### 2016-07-02 ms.tex
I put the base files under version control.

%%
%% Beginning of file 'sample.tex'
%%
%% Modified 2005 December 5
%%
%% This is a sample manuscript marked up using the
%% AASTeX v5.x LaTeX 2e macros.

%% The first piece of markup in an AASTeX v5.x document
%% is the \documentclass command. LaTeX will ignore
%% any data that comes before this command.

%% The command below calls the preprint style
%% which will produce a one-column, single-spaced document.
%% Examples of commands for other substyles follow. Use
%% whichever is most appropriate for your purposes.
%%
%%\documentclass[12pt,preprint]{aastex}

%% manuscript produces a one-column, double-spaced document:

%\documentclass{article}
\documentclass[twocolumn]{aastex6}
%\documentclass[iop]{emulateapj}

%% preprint2 produces a double-column, single-spaced document:
%\documentclass[preprint2]{aastex}

%% Sometimes a paper's abstract is too long to fit on the
%% title page in preprint2 mode. When that is the case,
%% use the longabstract style option.

%% \documentclass[preprint2,longabstract]{aastex}

%% If you want to create your own macros, you can do so
%% using \newcommand. Your macros should appear before
%% the \begin{document} command.
%%
%% If you are submitting to a journal that translates manuscripts
%% into SGML, you need to follow certain guidelines when preparing
%% your macros. See the AASTeX v5.x Author Guide
%% for information.

%Packages
%\usepackage[colorlinks=true,linkcolor=blue,citecolor=blue]{hyperref}

\usepackage{natbib}
\bibliographystyle{astroads}

\newcommand{\vdag}{(v)^\dagger}

%% You can insert a short comment on the title page using the command below.

%\slugcomment{DHS White Paper}

%% If you wish, you may supply running head information, although
%% this information may be modified by the editorial offices.
%% The left head contains a list of authors,
%% usually a maximum of three (otherwise use et al.).  The right
%% head is a modified title of up to roughly 44 characters.
%% Running heads will not print in the manuscript style.

\shorttitle{IRTF BD Spectro-photometry}
\shortauthors{BD team.}

%% This is the end of the preamble.  Indicate the beginning of the
%% paper itself with \begin{document}.

\begin{document}

%% LaTeX will automatically break titles if they run longer than
%% one line. However, you may use \\ to force a line break if
%% you desire.

\title{IRTF Spectro-Photometry of Rotating Brown Dwarfs}

%% Use \author, \affil, and the \and command to format
%% author and affiliation information.
%% Note that \email has replaced the old \authoremail command
%% from AASTeX v4.0. You can use \email to mark an email address
%% anywhere in the paper, not just in the front matter.
%% As in the title, use \\ to force line breaks.

\author{E. Schlawin, T. Karalidi?}
\affil{Steward Observatory, Tucson AZ 85721}
\email{eas342@email.arizona.edu}

\author{A. Burgasser, J. Teske, J. Gizis}
\affil{B}

%% Notice that each of these authors has alternate affiliations, which
%% are identified by the \altaffilmark after each name.  Specify alternate
%% affiliation information with \altaffiltext, with one command per each
%% affiliation.

%\altaffiltext{1}{Hubble Postdoctoral Fellow}

%% Mark off your abstract in the ``abstract'' environment. In the manuscript
%% style, abstract will output a Received/Accepted line after the
%% title and affiliation information. No date will appear since the author
%% does not have this information. The dates will be filled in by the
%% editorial office after submission.

\begin{abstract}
BD Science
\end{abstract}

%% Keywords should appear after the \end{abstract} command. The uncommented
%% example has been keyed in ApJ style. See the instructions to authors
%% for the journal to which you are submitting your paper to determine
%% what keyword punctuation is appropriate.

\keywords{Brown Dwarfs}

%% From the front matter, we move on to the body of the paper.
%% In the first two sections, notice the use of the natbib \citep
%% and \citet commands to identify citations.  The citations are
%% tied to the reference list via symbolic KEYs. The KEY corresponds
%% to the KEY in the \bibitem in the reference list below. We have
%% chosen the first three characters of the first author's name plus
%% the last two numeral of the year of publication as our KEY for
%% each reference.

%% Authors who wish to have the most important objects in their paper
%% linked in the electronic edition to a data center may do so by tagging
%% their objects with \objectname{} or \object{}.  Each macro takes the
%% object name as its required argument. The optional, square-bracket 
%% argument should be used in cases where the data center identification
%% differs from what is to be printed in the paper.  The text appearing 
%% in curly braces is what will appear in print in the published paper. 
%% If the object name is recognized by the data centers, it will be linked
%% in the electronic edition to the object data available at the data centers  
%%
%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
%% the brackets must be escaped with backslashes when used in the first
%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
%%  Otherwise, LaTeX will issue an error.

\section{Introduction}

\section{Light Curves}
\begin{figure}[!ht]
\centering
\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
\caption{Time Series.}\label{fig:DHSRes}
\end{figure}

\section{Conclusions}

\section{Acknowledgements}

%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

%% In a manner similar to \objectname authors can provide links to dataset
%% hosted at participating data centers via the \dataset{} command.  The
%% second curly bracket argument is printed in the text while the first
%% parentheses argument serves as the valid data set identifier.  Large
%% lists of data set are best provided in a table (see Table 3 for an example).
%% Valid data set identifiers should be obtained from the data center that
%% is currently hosting the data.
%%
%% Note that AASTeX interprets everything between the curly braces in the 
%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
%% compile your manuscript.  Special characters do not 
%% need to be escaped in the optional, square-bracket argument.

%% In this section, we use  the \subsection command to set off
%% a subsection.  \footnote is used to insert a footnote to the text.

%% Observe the use of the LaTeX \label
%% command after the \subsection to give a symbolic KEY to the
%% subsection for cross-referencing in a \ref command.
%% You can use LaTeX's \ref and \label commands to keep track of
%% cross-references to sections, equations, tables, and figures.
%% That way, if you change the order of any elements, LaTeX will
%% automatically renumber them.

%% This section also includes several of the displayed math environments
%% mentioned in the Author Guide.

%% The equation environment wil produce a numbered display equation.

%% The \notetoeditor{TEXT} command allows the author to communicate
%% information to the copy editor.  This information will appear as a
%% footnote on the printed copy for the manuscript style file.  Nothing will
%% appear on the printed copy if the preprint or
%% preprint2 style files are used.

%% The eqnarray environment produces multi-line display math. The end of
%% each line is marked with a \\. Lines will be numbered unless the \\
%% is preceded by a \nonumber command.
%% Alignment points are marked by ampersands (&). There should be two
%% ampersands (&) per line.

%% Putting eqnarrays or equations inside the mathletters environment groups
%% the enclosed equations by letter. For instance, the eqnarray below, instead
%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
%% LaTeX the paper and look at the output to see the results.

%% This section contains more display math examples, including unnumbered
%% equations (displaymath environment). The last paragraph includes some
%% examples of in-line math featuring a couple of the AASTeX symbol macros.

%% The displaymath environment will produce the same sort of equation as
%% the equation environment, except that the equation will not be numbered
%% by LaTeX.
%% If you wish to include an acknowledgments section in your paper,
%% separate it off from the body of the text using the \acknowledgments
%% command.

%% Included in this acknowledgments section are examples of the
%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
%% argument when you want to print the url directly in the text. Otherwise,
%% use either \url or \anchor, with the HREF as the first argument and the
%% text to be printed in the second.

\acknowledgments

%% To help institutions obtain information on the effectiveness of their
%% telescopes, the AAS Journals has created a group of keywords for telescope
%% facilities. A common set of keywords will make these types of searches
%% significantly easier and more accurate. In addition, they will also be
%% useful in linking papers together which utilize the same telescopes
%% within the framework of the National Virtual Observatory.
%% See the AASTeX Web site at http://aastex.aas.org/
%% for information on obtaining the facility keywords.

%% After the acknowledgments section, use the following syntax and the
%% \facility{} macro to list the keywords of facilities used in the research
%% for the paper.  Each keyword will be checked against the master list during
%% copy editing.  Individual instruments or configurations can be provided 
%% in parentheses, after the keyword, but they will not be verified.

%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.

%% Appendix material should be preceded with a single \appendix command.
%% There should be a \section command for each appendix. Mark appendix
%% subsections with the same markup you use in the main body of the paper.

%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
%% The equation counter will reset when it encounters the \appendix
%% command and will number appendix equations (A1), (A2), etc.

\appendix

%% The reference list follows the main body and any appendices.
%% Use LaTeX's thebibliography environment to mark up your reference list.
%% Note \begin{thebibliography} is followed by an empty set of
%% curly braces.  If you forget this, LaTeX will generate the error
%% "Perhaps a missing \item?".
%%
%% thebibliography produces citations in the text using \bibitem-\cite
%% cross-referencing. Each reference is preceded by a
%% \bibitem command that defines in curly braces the KEY that corresponds
%% to the KEY in the \cite commands (see the first section above).
%% Make sure that you provide a unique KEY for every \bibitem or else the
%% paper will not LaTeX. The square brackets should contain
%% the citation text that LaTeX will insert in
%% place of the \cite commands.

%% We have used macros to produce journal name abbreviations.
%% AASTeX provides a number of these for the more frequently-cited journals.
%% See the Author Guide for a list of them.

%% Note that the style of the \bibitem labels (in []) is slightly
%% different from previous examples.  The natbib system solves a host
%% of citation expression problems, but it is necessary to clearly
%% delimit the year from the author name used in the citation.
%% See the natbib documentation for more details and options.

\bibliographystyle{apj}
\bibliography{bd_biblio}

%\clearpage

%% Use the figure environment and \plotone or \plottwo to include
%% figures and captions in your electronic submission.
%% To embed the sample graphics in
%% the file, uncomment the \plotone, \plottwo, and
%% \includegraphics commands
%%
%% If you need a layout that cannot be achieved with \plotone or
%% \plottwo, you can invoke the graphicx package directly with the
%% \includegraphics command or use \plotfiddle. For more information,
%% please see the tutorial on "Using Electronic Art with AASTeX" in the
%% documentation section at the AASTeX Web site, http://aastex.aas.org/
%%
%% The examples below also include sample markup for submission of
%% supplemental electronic materials. As always, be sure to check
%% the instructions to authors for the journal you are submitting to
%% for specific submissions guidelines as they vary from
%% journal to journal.

%% This example uses \plotone to include an EPS file scaled to
%% 80% of its natural size with \epsscale. Its caption
%% has been written to indicate that additional figure parts will be
%% available in the electronic journal.

%\begin{figure}
%\epsscale{.80}
%\plotone{f1.eps}
%\caption{Derived spectra for 3C138 \citep[see][]{heiles03}. Plots for all sources are available
%in the electronic edition of {\it The Astrophysical Journal}.\label{fig1}}
%\end{figure}

%\clearpage

%% Here we use \plottwo to present two versions of the same figure,
%% one in black and white for print the other in RGB color
%% for online presentation. Note that the caption indicates
%% that a color version of the figure will be available online.
%%

%\begin{figure}
%\plottwo{f2.eps}{f2_color.eps}
%\caption{A panel taken from Figure 2 of \citet{rudnick03}. 
%See the electronic edition of the Journal for a color version 
%of this figure.\label{fig2}}
%\end{figure}

%% This figure uses \includegraphics to scale and rotate the still frame
%% for an mpeg animation.

%\begin{figure}
%\includegraphics[angle=90,scale=.50]{f3.eps}
%\caption{Animation still frame taken from \citet{kim03}.
%This figure is also available as an mpeg
%animation in the electronic edition of the
%{\it Astrophysical Journal}.}
%\end{figure}

%% If you are not including electonic art with your submission, you may
%% mark up your captions using the \figcaption command. See the
%% User Guide for details.
%%
%% No more than seven \figcaption commands are allowed per page,
%% so if you have more than seven captions, insert a \clearpage
%% after every seventh one.

%% Tables should be submitted one per page, so put a \clearpage before
%% each one.

%% Two options are available to the author for producing tables:  the
%% deluxetable environment provided by the AASTeX package or the LaTeX
%% table environment.  Use of deluxetable is preferred.
%%

%% Three table samples follow, two marked up in the deluxetable environment,
%% one marked up as a LaTeX table.

%% In this first example, note that the \tabletypesize{}
%% command has been used to reduce the font size of the table.
%% We also use the \rotate command to rotate the table to
%% landscape orientation since it is very wide even at the
%% reduced font size.
%%
%% Note also that the \label command needs to be placed
%% inside the \tablecaption.

%% This table also includes a table comment indicating that the full
%% version will be available in machine-readable format in the electronic
%% edition.

%% If you use the table environment, please indicate horizontal rules using
%% \tableline, not \hline.
%% Do not put multiple tabular environments within a single table.
%% The optional \label should appear inside the \caption command.

%% If the table is more than one page long, the width of the table can vary
%% from page to page when the default \tablewidth is used, as below.  The
%% individual table widths for each page will be written to the log file; a
%% maximum tablewidth for the table can be computed from these values.
%% The \tablewidth argument can then be reset and the file reprocessed, so
%% that the table is of uniform width throughout. Try getting the widths
%% from the log file and changing the \tablewidth parameter to see how
%% adjusting this value affects table formatting.

%% The \dataset{} macro has also been applied to a few of the objects to
%% show how many observations can be tagged in a table.

%% Tables may also be prepared as separate files. See the accompanying
%% sample file table.tex for an example of an external table file.
%% To include an external file in your main document, use the \input
%% command. Uncomment the line below to include table.tex in this
%% sample file. (Note that you will need to comment out the \documentclass,
%% \begin{document}, and \end{document} commands from table.tex if you want
%% to include it in this document.)

%% \input{table}

%% The following command ends your manuscript. LaTeX will ignore any text
%% that appears after it.

\end{document}

%%
%% End of file `sample.tex'.

### 2016-10-13 ms.tex
I added some stand-in affiliations and one example reference.
I added the discovery references for 2MASS J1821 and 2MASS J0835.

@@
 \usepackage{natbib}
-\bibliographystyle{astroads}
 
@@
 
-\author{E. Schlawin, T. Karalidi?}
-\affil{Steward Observatory, Tucson AZ 85721}
+\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi? }
+\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
 \email{eas342@email.arizona.edu}
-
-\author{A. Burgasser, J. Teske, J. Gizis}
-\affil{B}
 
@@
 \section{Introduction}
+\citep{burgaser2014irtf}.
+
+We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
+2MASS J1821+14010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
+2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
+2MASS J0835-019 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.
+
+\section{Observations}
 

### 2016-10-18 ms.tex
I added a few more tables and sentences about the observations.

@@
 \section{Introduction}
-\citep{burgaser2014irtf}.
+\citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
 
@@
 
+\input{bd_table.tex}
+
 \section{Observations}
+We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
+
+\input{observing_table.tex}
+
+We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
 
@@
 \section{Acknowledgements}
-
+%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
 %If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

### 2016-10-18 make_tables.py

@@ -1,0 +1,6 @@
+from astropy.io import ascii
+
+for oneTable in ['bd_table','observing_table']:
+    dat = ascii.read(oneTable+'.csv')
+    dat.write(oneTable+'.tex')
+    

### 2016-10-19 ms.tex
I added a tiny sentence about the reference star, but still haven't figured out which one.

@@
 We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
-2MASS J1821+14010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
+2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
@@
 We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
-
+For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, J=12.58, H=11.97, K=11.82  at a distance of 30.1\arcsec\ or was it 2MASS 18212622+1414064, J=11.25, H=10.91, K=10.85 at a distance of 19.1\arcsec)?
 \input{observing_table.tex}
@@
 We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
+
+For 2MASS J1821, we
 

### 2016-10-20 ms.tex
I finalized which source was used as the reference for 2MASS 1821.

@@
 
-\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi? }
+\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi }
 \affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
@@
 We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
-For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, J=12.58, H=11.97, K=11.82  at a distance of 30.1\arcsec\ or was it 2MASS 18212622+1414064, J=11.25, H=10.91, K=10.85 at a distance of 19.1\arcsec)?
+For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24 \arcsec. 
+%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
 \input{observing_table.tex}

### 2016-10-22 ms.tex
I added more info on the reference stars to the tables. Also, explained more about the dichroic and MORIS imager band choice.

@@
 \section{Introduction}
+
+Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
+
+The cloud layers may be studied from the direct spectroscopy and photometry of large populations of brown dwarf atmospheres.
+
+In addition to the direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
+
+The photometry brown dwarfs at the L/T transition is explained by (silicate?) clouds at a temperature of (?).
+
 \citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
@@
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J0835-019 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.
+2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.
 
-\input{bd_table.tex}
+\begin{table*}
+\begin{center}
+\begin{tabular}{cccc}
+Name & Rotation Period & Spectral Type & K magnitude \\
+-- & hr & -- & -- \\
+2MASS J1821+14010 & 4.2 & L5 & 11.14 \\
+2MASS J0835-019 & 9 & L5 & 11.65 \\
+\end{tabular}
+\end{center}
+\end{table*}
 
@@
 We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
-For 2MASS J1821, we observed a simultaneous reference - (I think it was 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24 \arcsec. 
+For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24 \arcsec.
+We were able to measure spectrophotometry over ? hours, which was greater than one full rotation period of the brown dwarf.
+Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
 %Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
-\input{observing_table.tex}
+For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
+%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px
+
+\begin{table*}
+\begin{center}
+\begin{tabular}{ccccc}
+Target & Observing Date & N$_{int}$ & t$_{exp}$ & Reference Star \\
+-- & UT Start & -- & (s) & -- \\
+\hline
+2MASS J1821 & 2015-12-31 & 363 & 45 & 2MASS 18212622+1414064 \\
+2MASS J0835 & 2016-06-25 & 352 & 60 & 2MASS 08354383-0819212 \\
+\end{tabular}
+\end{center}
+\end{table*}
 
 We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
-
-For 2MASS J1821, we
+We used a 0.9~$\mu$m dichoric to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
+For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
+For 2MASS J0835, we were unable to obtain photometry - why? due to the fainter source?
 

### 2016-10-22 make_tables.py

@@ -1,6 +1,16 @@
 from astropy.io import ascii
+import subprocess
+import pdb
 
 for oneTable in ['bd_table','observing_table']:
+    ## Cleanup CSV file for what MS Excel does
+    subprocess.call(['mac2unix',oneTable+'.csv'])
     dat = ascii.read(oneTable+'.csv')
-    dat.write(oneTable+'.tex')
+    ascii.write(dat,oneTable+'.tex',
+                Writer=ascii.Latex,latexdict={'tabletype':'table*'})
+    #dat.write(oneTable+'.tex',latexdict={'tabletype':'table*'},Writer=ascii.latex)
     
+    with open(oneTable+'.tex') as TableTex:
+        allLines = TableTex.readlines()
+        ## Add a horizontal line under headings
+        #pdb.set_trace()

### 2016-10-25 ms.tex
I added a dynamic spectrum image. But it's got the wrong reference and background star order.
I added the amplitude versus wavelength plot for 2MASS J1821.

@@
 \centering
+\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
+\caption{Top Panel: 2MASS 1821's median spectrum compared with the reference star.
+The reference star is a significantly higher temperature star.
+Bottom Panel: Dynamic spectrum of 2MASS J1821.}\label{fig:DHSRes}
+\end{figure}
+
+\begin{figure}[!ht]
+\centering
 \includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
-\caption{Time Series.}\label{fig:DHSRes}
+\caption{Time Series.}\label{fig:1821tser}
+\end{figure}
+
+\section{Light Curves}
+\begin{figure}[!ht]
+\centering
+\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
+\caption{Sine fit amplitude versus wavelength for 2MASS J1821.
+The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
 \end{figure}

### 2016-10-26 ms.tex
Relabled arcsec.
I found out the duration of the observations.

@@
 -- & hr & -- & -- \\
-2MASS J1821+14010 & 4.2 & L5 & 11.14 \\
+\hline \hline
+2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L5 & 11.14 \\
 2MASS J0835-019 & 9 & L5 & 11.65 \\
@@
 We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
-For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24 \arcsec.
-We were able to measure spectrophotometry over ? hours, which was greater than one full rotation period of the brown dwarf.
+For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
+We were able to measure spectrophotometry over 7.47 hours, which was 1.78 rotations at the rotation period.
 Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
@@
 
-\section{Light Curves}
 \begin{figure}[!ht]

### 2016-10-28 ms.tex
I added 2MASS J0835's specphot image side by side with 2MASS J0835 for comparison.

@@
 \usepackage{natbib}
-
+\usepackage[caption=false]{subfig}
 \newcommand{\vdag}{(v)^\dagger}
@@
 \section{Light Curves}
-\begin{figure}[!ht]
+
+\begin{figure*}[!t]
 \centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
+	\label{fig:specphot0835}
+	}
+\subfloat[2MASS J1821]{
 	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
-\caption{Top Panel: 2MASS 1821's median spectrum compared with the reference star.
-The reference star is a significantly higher temperature star.
-Bottom Panel: Dynamic spectrum of 2MASS J1821.}\label{fig:DHSRes}
-\end{figure}
+	\label{fig:specphot1821}
+	}
+	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star.
+The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption.
+The reference stars are significantly higher temperatures.
+Bottom Panels: Dynamic spectrum of 2MASS J1821.}
+	\label{fig:corner}
+\end{figure*}
 

### 2016-10-29 ms.tex
I also added a phase folded time series for 2MASS J0835 side by side with 2MASS J1821.
I put in a few references to early work on variability and models.
I added some more details about the observations, slit, calibration etc.

@@
 
+L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
+This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.
+
 \citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
@@
 \hline \hline
-2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L5 & 11.14 \\
+2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 & 11.14 \\
 2MASS J0835-019 & 9 & L5 & 11.65 \\
@@
 \section{Observations}
+
+For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
+
 We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
 For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
-We were able to measure spectrophotometry over 7.47 hours, which was 1.78 rotations at the rotation period.
+We were able to measure spectrophotometry over 7.47 hours, which was 1.8 rotations at the 4.2 rotation period from \citet{metchev2015weatherII}.
+
+As visible in Figure \ref{fig:specphot1821}, the light curves repeat the same fluctuations after one rotation period.
 Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
 %Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
-For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
+
 %Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px
+
+We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
+We used a 0.9~$\mu$m dichoric to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
+For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
+For 2MASS J0835, we were unable to obtain photometry - why? due to the fainter source?
 
@@
 \begin{center}
+\caption{Observing Parameters}\label{tab:obsParam}
 \begin{tabular}{ccccc}
@@
 \end{center}
+\tablenotetext{}{}
 \end{table*}
 
-We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
-We used a 0.9~$\mu$m dichoric to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
-For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
-For 2MASS J0835, we were unable to obtain photometry - why? due to the fainter source?
+We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
+Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.
+
+Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp.
+We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
 
@@
 Bottom Panels: Dynamic spectrum of 2MASS J1821.}
-	\label{fig:corner}
+	\label{fig:specphot}
 \end{figure*}
 
-\begin{figure}[!ht]
+\begin{figure*}[!t]
 \centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
+	\label{fig:tserPhase0835}
+	}
+\subfloat[2MASS J1821]{
 	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
-\caption{Time Series.}\label{fig:1821tser}
-\end{figure}
+	\label{fig:tserPhase1821}
+	}
+	\caption{Phase folded time series for both systems.}
+	\label{fig:tserPfold}
+\end{figure*}
 

### 2016-10-29 ms.tex
I added more details about the flat fielding and background subtraction.

@@
 For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
+We obtained spectrophotometry over 4.65 hours, covering about half of a rotation period for 2MASS J0835.
 
@@
 We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
+
+For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
+Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
+All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
+We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.
+For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
+
+As in \citep{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
+We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
 

### 2016-10-30 ms.tex
I added more details to the 2MASS J1821 flat fielding - without using sky frames.

@@
 
-As visible in Figure \ref{fig:specphot1821}, the light curves repeat the same fluctuations after one rotation period.
+As visible in Figure \ref{fig:specphot1821}, the light curves for 2MASS J1821 repeat the same fluctuations after one rotation period.
 Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
@@
 We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.
+
 For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
+Here, we fit the flat field structure with low order polynomials in the incandescent flat field to describe the spatial structure and use the residual image as a pixel-to-pixel flat.
+As in 2MASS J0835, we cross-correlate the spatial structure image to find a shift and then multiply it by the pixel-to-pixel flat to create a custom flat field for every image.
+In both 2MASS J0835 and 2MASS J1821 we remove all spectral structure from the flat fields to make ``response'' images that do not include the spectral structure of the lamp or dramatically alter the flux levels that would affect SNR calculations from the number of photo-electrons in a given pixel.
 

### 2016-11-01 ms.tex
I added some more references to brown dwarf L/T work and added a crude spectrum for 2MASS J0835.

@@
 Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
+Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds.
 
-The cloud layers may be studied from the direct spectroscopy and photometry of large populations of brown dwarf atmospheres.
-
-In addition to the direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
+The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
+In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
+In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.
 
@@
 This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.
+Virtually all L dwarfs and most T dwarfs likely have photospheric heterogeneities that cause flux variations larger than 0.2\% in the near infrared \citep{metchev2015weatherII}
 
-\citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
+\citet{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
+\citet{burgaser2014irtf} observed the binary system Luhman 16 AB and used the more stable Luhman 16A as a simultaneous reference to measure spectral variability in Luhman 16B.
 
@@
 
-\begin{figure}[!ht]
+\begin{figure*}[!]
 \centering
+\subfloat[2MASS J0835 - \colorbox{red}{fit needs more work} ]{
+	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
+	\label{fig:ampspec0835}
+	}
+\subfloat[2MASS J1821]{
 	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
-\caption{Sine fit amplitude versus wavelength for 2MASS J1821.
+	\label{fig:ampspec1821}
+	}
+	\caption{Sine fit amplitude versus wavelength for each brown dwarf.
+The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}
+	\label{fig:ampSpect}
+\end{figure*}
+
+%    \begin{figure}[!ht]
+%    \centering
+%    \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
+%    \caption{Sine fit amplitude versus wavelength for 2MASS J1821.
 The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
-\end{figure}
+%    \end{figure}
 

### 2016-11-02 ms.tex
I added some more notes about the sinusoidal model fitting.

@@
 We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
+We use optimal extraction \citep{horne1986optimalE} to maximize the signal to noise.
+The spatial profiles are fit with low order polynomials with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
 
@@
 
+Figure \ref{fig:specphot} shows the dynamic spectra for both brown dwarfs with the individual spectra of the target and reference stars on the upper panels.
+At the few percent level, 2MASS j0835 shows no variations or systematics.
+2MASS J1821 on the other hand, shows a periodic signal that is strongest at the short wavelength and gradually gets smaller toward longer wavelengths.
+2MASS J1821 also exhibits systematic trends near strong slopes in the raw spectra due to telluric absorption bands.
+
 \begin{figure*}[!t]
@@
 
+2MASS J0835 exhibits no periodic behavior whereas 2MASS 1821 shows large varations when phasing the dynamic spectra at the known rotation periods of the two brown dwarfs, shown in Figure \ref{fig:tserPfold}.
+For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.
+
+We fit the time series of each brown dwarf in 25 spectral bins each to assess the wavelength-dependent nature of their variations.
+The simple model can be described as 
+\begin{equation}
+F(t) = A * \sin(2 \pi (t - t_0)/\tau) + B t + C
+\end{equation}
+where $F$ is the flux as a function of time ($t$), A is the amplitude of the variations, $t_0$ is the time offset of the variations and $\tau$ is the and B and C are linear terms describing the baseline trend.
+For the fits, we include a 4 free parameters: $A$, $t_0$, $B$ and $C$.
+We fixed the sinusoidal period $\tau$ at the literature value of periodicity because there are also variations due to variable telluric variation that are not relevant to the brown dwarf system.
+We imposed a prior that $A$ >= 0 so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
+
 \begin{figure*}[!]
@@
 The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}
-	\label{fig:ampSpect}
+	\label{fig:ampSpec}
 \end{figure*}
+
+Figure \ref{fig:ampSpec} shows the best fit amplitudes as a function of wavelength.
+We use the standard deviation of points near minimum to estimate the noise in the flux time series.
+The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
+The amplitude spectrum of 2MASS J0835 shown in Figure \ref{fig:ampspec0835} shows random fluctuations as a function of wavelength.
+2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
+This was also observed in the shorter wavelength range of 1.1~$\mu$m to 1.7~$\mu$m in \citet{yang2016exStormsBD}.
 

### 2016-11-02 ms.tex
Updates from ShareLaTeX

--- 2016-10-30 ms.tex
@@
 \usepackage{natbib}
-\usepackage[caption=false]{subfig}
+
 \newcommand{\vdag}{(v)^\dagger}
@@
 
-\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi }
+\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi? }
 \affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
 \email{eas342@email.arizona.edu}
+
+%This is a test by Gizis
 
@@
 \section{Introduction}
-
-Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
-
-The cloud layers may be studied from the direct spectroscopy and photometry of large populations of brown dwarf atmospheres.
-
-In addition to the direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
-
-The photometry brown dwarfs at the L/T transition is explained by (silicate?) clouds at a temperature of (?).
-
-L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
-This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.
-
-\citep{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
-
-We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
-2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
-2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.
-
-\begin{table*}
-\begin{center}
-\begin{tabular}{cccc}
-Name & Rotation Period & Spectral Type & K magnitude \\
--- & hr & -- & -- \\
-\hline \hline
-2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 & 11.14 \\
-2MASS J0835-019 & 9 & L5 & 11.65 \\
-\end{tabular}
-\end{center}
-\end{table*}
-
-\section{Observations}
-
-For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
-We obtained spectrophotometry over 4.65 hours, covering about half of a rotation period for 2MASS J0835.
-
-We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
-For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
-We were able to measure spectrophotometry over 7.47 hours, which was 1.8 rotations at the 4.2 rotation period from \citet{metchev2015weatherII}.
-
-As visible in Figure \ref{fig:specphot1821}, the light curves for 2MASS J1821 repeat the same fluctuations after one rotation period.
-Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
-%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
-
-%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px
-
-We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
-We used a 0.9~$\mu$m dichoric to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
-For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
-For 2MASS J0835, we were unable to obtain photometry - why? due to the fainter source?
-
-\begin{table*}
-\begin{center}
-\caption{Observing Parameters}\label{tab:obsParam}
-\begin{tabular}{ccccc}
-Target & Observing Date & N$_{int}$ & t$_{exp}$ & Reference Star \\
--- & UT Start & -- & (s) & -- \\
-\hline
-2MASS J1821 & 2015-12-31 & 363 & 45 & 2MASS 18212622+1414064 \\
-2MASS J0835 & 2016-06-25 & 352 & 60 & 2MASS 08354383-0819212 \\
-\end{tabular}
-\end{center}
-\tablenotetext{}{}
-\end{table*}
-
-We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
-Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.
-
-Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp.
-We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
-
-For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
-Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
-All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
-We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.
-
-For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
-Here, we fit the flat field structure with low order polynomials in the incandescent flat field to describe the spatial structure and use the residual image as a pixel-to-pixel flat.
-As in 2MASS J0835, we cross-correlate the spatial structure image to find a shift and then multiply it by the pixel-to-pixel flat to create a custom flat field for every image.
-In both 2MASS J0835 and 2MASS J1821 we remove all spectral structure from the flat fields to make ``response'' images that do not include the spectral structure of the lamp or dramatically alter the flux levels that would affect SNR calculations from the number of photo-electrons in a given pixel.
-
-As in \citep{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
-We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
+\citep{burgaser2014irtf}.
 
 \section{Light Curves}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
-	\label{fig:specphot0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
-	\label{fig:specphot1821}
-	}
-	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star.
-The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption.
-The reference stars are significantly higher temperatures.
-Bottom Panels: Dynamic spectrum of 2MASS J1821.}
-	\label{fig:specphot}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
-	\label{fig:tserPhase0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
-	\label{fig:tserPhase1821}
-	}
-	\caption{Phase folded time series for both systems.}
-	\label{fig:tserPfold}
-\end{figure*}
-
 \begin{figure}[!ht]
 \centering
-\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
-\caption{Sine fit amplitude versus wavelength for 2MASS J1821.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
+\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
+\caption{Time Series.}\label{fig:DHSRes}
 \end{figure}
@@
 \section{Acknowledgements}
-%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
+
 %If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.

### 2016-11-04 ms.tex
I added a quick figure of simple Mie scattering curve fits.
I added some explanations of the Mie fits.

--- 2016-11-02 ms.tex
@@
 
+%This is a test by Gizis
+
 %% Notice that each of these authors has alternate affiliations, which
@@
 \begin{abstract}
-BD Science
+L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres.
+We present a high precision ground-based study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010.
+2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m.
+2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m.
+We interpret the spectral variability in 2MASS J1821 as being due to clouds with sub-micron-sized particles.
 \end{abstract}
@@
 	\label{fig:specphot}
+	\vspace{0.1in}
 \end{figure*}
@@
 
+\section{Simple Model Fits}
+
+We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
+In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
+We model the extinction coefficient from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
+We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains.
+For the particle size distribution we assume a log-normal distribution around a characteristic size with a distribution $\sigma$ of 0.5.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
+\caption{Sine fit amplitude versus wavelength with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
+\end{centering}
+\end{figure}
+
+Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
+In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
 \section{Conclusions}

### 2016-11-04 ms.tex
I a few tweaks to wording throughout on the Mie scattering fits and a reference to Yang et al. 2015.

@@
 \shorttitle{IRTF BD Spectro-photometry}
-\shortauthors{BD team.}
+\shortauthors{Schlawin et al.}
 
@@
 L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres.
-We present a high precision ground-based study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010.
+We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010.
 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m.
-2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m.
-We interpret the spectral variability in 2MASS J1821 as being due to clouds with sub-micron-sized particles.
+2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
 \end{abstract}
@@
 The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
-In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time.
+In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
 In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.
 
-The photometry brown dwarfs at the L/T transition is explained by (silicate?) clouds at a temperature of (?).
+The photometry brown dwarfs at the L/T transition is explained by (silicate and sulfide?) clouds at a temperature of (?).
 
@@
 \hline \hline
-2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 & 11.14 \\
+2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 - L5 & 11.14 \\
 2MASS J0835-019 & 9 & L5 & 11.65 \\
@@
 \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
-\caption{Sine fit amplitude versus wavelength with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
+\caption{Sine fit amplitude versus wavelength excluding the regions contaminated by telluric absorption.
+with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
 \end{centering}
@@
 In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
+
+\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821.
+
 \section{Conclusions}

### 2016-11-04 ms.tex
I added a longer description of the WFC3 spectrum I grabbed from the Yang et al. 2015 paper.

@@
 We fixed the sinusoidal period $\tau$ at the literature value of periodicity because there are also variations due to variable telluric variation that are not relevant to the brown dwarf system.
-We imposed a prior that $A$ >= 0 so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
+We imposed a prior that $A \geq 0$ so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
 
@@
 	\caption{Sine fit amplitude versus wavelength for each brown dwarf.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}
+The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}
 	\label{fig:ampSpec}
@@
 
-\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821.
+\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
+Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
+\begin{equation}
+A  = \frac{f_R - 1}{f_R + 1}
+\end{equation}
+where $f_R$ is the flux ratio of the maximum over minimum flux.
+
+The WFC3 amplitude spectrum is shown with the data in Figure \ref{fig:ampspec1821mie}.
+There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
+The WFC3 spectrum is not affected by the telluric absorption the way the SpeX data is.
+\citet{yang2015hstRotBD} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821, consistent with our Mie scattering fit.
 

### 2016-11-06 ms.tex
I added a sentence about 2MASS WISE 1906.
I added a reference to Gagne et al. 2015 on 2MASS J1821.
I corrected the refrence from Banyan 5 to Banyan 7 and added the derived spectral types and effective temperatures.

@@
 2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
+The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
@@
 \begin{center}
-\begin{tabular}{cccc}
-Name & Rotation Period & Spectral Type & K magnitude \\
--- & hr & -- & -- \\
+\begin{tabular}{ccccr}
+Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ \\
+-- & (hr) & -- & -- & (K) \\
 \hline \hline
-2MASS J1821+14010 & 4.2\footnote{\citet{metchev2015weatherII}} & L4.5 - L5 & 11.14 \\
-2MASS J0835-019 & 9 & L5 & 11.65 \\
+2MASS J1821+14010 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} \\
+2MASS J0835-019 & 9 & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} \\
 \end{tabular}
 \end{center}
+\tablenotetext{a}{\citet{metchev2015weatherII}.}
+\tablenotetext{b}{\citet{gagne2015banyan7}.}
+\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}
+
 \end{table*}
@@
 We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
+The program also included WISE J1906+4011, but weather prevented successful observations of this brown dwarf.
 Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.
@@
 
-\section{Simple Model Fits}
+\section{Sinusoidal Model Fits}
 

### 2016-11-07 ms.tex
I added a simple temperature difference model.

@@
 L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres.
-We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010.
+We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5.
 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m.
@@
 
+\section{Sinusoidal Model Fits}
+
 We fit the time series of each brown dwarf in 25 spectral bins each to assess the wavelength-dependent nature of their variations.
@@
 
-\section{Sinusoidal Model Fits}
+\subsection{Mie Scattering Fit}
 
@@
 \caption{Sine fit amplitude versus wavelength excluding the regions contaminated by telluric absorption.
-with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m}\label{fig:ampspec1821mie}
+with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
+Also shown in the figure is the WFC3 amplitude from \citet{yang2015hstRotBD}.
+The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
 \end{centering}
@@
 \citet{yang2015hstRotBD} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821, consistent with our Mie scattering fit.
+
+\subsection{Spot Model Fit}
+
+Another simple model we attempt is a spot model - that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars.
+In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
+This time we model the data with two layers in local thermodynamic equilibrium (LTE) so that the flux is a ratio of two Planck functions.
+We include a multiplicative constant to account for the geometric area ratio of the two temperature layers.
+The two-layer model best-fits the data with a reduced chi-squared of 4.0, which is significantly disfavored as compared to the Mie scattering mode.
+Furthermore, the 400 K temperature variation in the model is significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
+\caption{The same data as in Figure \ref{fig:ampspec1821mie}.
+We fit the data as a temperature differential between the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
+\end{centering}
+\end{figure}
 

### 2016-11-08 ms.tex
I added some discussion/references of condensates and corrected the rotation period for 2MASS 0835.

@@
 Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
-Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds.
+Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds including H$_2$O, MgSiO$_3$, Mg$_2$SiO$_4$ and Fe \citep{marley2015rev}.
 
 The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
-In addition to these direct spectroscopy and photometry, brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
+Brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
 In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.
@@
 
-We observed the three brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
+We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
 2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
@@
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable.
+2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable with a period of 9 hr.
+
+Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$ \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.
 
@@
 \begin{center}
-\begin{tabular}{ccccr}
-Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ \\
--- & (hr) & -- & -- & (K) \\
+\caption{Brown Dwarf Properties}\label{tab:bdProp}
+\begin{tabular}{ccccrr}
+Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
+-- & (hr) & -- & -- & (K) & (km/s) \\
 \hline \hline
-2MASS J1821+14010 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} \\
-2MASS J0835-019 & 9 & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} \\
+2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
+2MASS 0835 & 3.1\tablenotemark{d} & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
 \end{tabular}
@@
 \tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}
-
+\tablenotetext{d}{\citet{blake2010nirspecVS}}
+\tablenotetext{e}{\citet{koen2004ibandBD}}
 \end{table*}
@@
 \section{Conclusions}
+
+We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
+These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
+We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems.
+After fitting sinusoids to both of the time series, we find that the
 

### 2016-11-10 ms.tex
I wrote out the equations for the 2 temperature model.

@@
 \newcommand{\vdag}{(v)^\dagger}
+\newcommand{\degree}{$^\circ$}
 
@@
 A  = \frac{f_R - 1}{f_R + 1}
-\end{equation}
+\end{equation}\label{eq:ampFromRatio}
 where $f_R$ is the flux ratio of the maximum over minimum flux.
@@
 \begin{centering}
+\includegraphics[width=0.4\textwidth]{temperature_drawing.pdf}
+\caption{A simple two layer model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
 \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
@@
 \end{figure}
+
+I should change the spot model fit to the following model
+\begin{equation}
+f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
+\end{equation}
+where $\alpha_1$ and $\alpha_2$ are the areal fractions of the two temperature layers limited to [0,1], $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.
+
+Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
+\begin{equation}
+A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
+\end{equation}
+If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
 

### 2016-11-11 ms.tex
I put in different temperature and alpha constraints on the spot model.

@@
 \usepackage[caption=false]{subfig}
+\usepackage{amsmath,amssymb}
 \newcommand{\vdag}{(v)^\dagger}
@@
 \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
-\caption{Sine fit amplitude versus wavelength excluding the regions contaminated by telluric absorption.
+\caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption.
 with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
@@
 
-Another simple model we attempt is a spot model - that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars.
-In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
-This time we model the data with two layers in local thermodynamic equilibrium (LTE) so that the flux is a ratio of two Planck functions.
-We include a multiplicative constant to account for the geometric area ratio of the two temperature layers.
-The two-layer model best-fits the data with a reduced chi-squared of 4.0, which is significantly disfavored as compared to the Mie scattering mode.
-Furthermore, the 400 K temperature variation in the model is significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
-
 \begin{figure}
@@
 \includegraphics[width=0.4\textwidth]{temperature_drawing.pdf}
-\caption{A simple two layer model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
+\caption{A simple two region model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
 \end{centering}
 \end{figure}
+
+Another simple model we attempt is a spot model - that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
+In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
+This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem} with two opposite longitudes of the planet at the brightness minimum and maximum.
+We assume that are each in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
+The flux ratio between maximum and minimum flux is then
+\begin{equation}
+f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
+\end{equation}
+where $\alpha_1$ and $\alpha_2$ are the areal fractions of the two temperature layers limited to [0,1], $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.
+Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
+\begin{equation}
+A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
+\end{equation}
+If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
+If we ignore projection effects for small area coverage, the effective temperature is 
+\begin{equation}
+\sigma T_{eff}^4 \approx (\alpha_1 + \alpha_2) \sigma T_1^4 + (2 - \alpha_1 - \alpha_2) \sigma T_2^4
+\end{equation}
+where $\sigma$ is the Stephan-Boltzmann constant.
+
+Our model best-fits the data with $\alpha_i$ << 1 and also with much lower temperatures than equilibrium, shown in Figure \ref{fig:ampspec1821tdiff}.
+This model has a reduced chi-squared of 1.3, consistent with the data, but not with the effective temperature.
+If we restrict the model to be a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures, the best-fit is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a $\bar{\chi}^2$ = 15.
+Finally, we attempt a model where we restrict the temperature limits to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{citet{gagne2015banyan7}}.
+The best fit model has $T_{eff} \approx $1590 K, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
+This model fits with $\bar{\chi}^2$ = 2.1.
+However, the temperature contrasts in these models are significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
 
@@
 \caption{The same data as in Figure \ref{fig:ampspec1821mie}.
-We fit the data as a temperature differential between the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
+We fit the data with a two region model that assumes the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
 \end{centering}
 \end{figure}
-
-I should change the spot model fit to the following model
-\begin{equation}
-f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
-\end{equation}
-where $\alpha_1$ and $\alpha_2$ are the areal fractions of the two temperature layers limited to [0,1], $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.
-
-Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
-\begin{equation}
-A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
-\end{equation}
-If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
+% Command used:
+% plot_rad_vs_wavl,/amp,/shadetell,custxrange=[0.8,2.5],custyrange=[-0.1,1.9],/showYang,/twoTreg
 

### 2016-11-11 ms.tex
Some text updates throughout and I added a few acknowledgements.

@@
 
-\title{IRTF Spectro-Photometry of Rotating Brown Dwarfs}
+\title{IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010}
 
@@
 L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres.
-We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5.
+We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5 using the Infrared Telescope Facility (IRTF).
 2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m.
 2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
+It can also be fit by a hot spots on the brown dwarf surface, but they require implausible temperature variations, so we prefer the Mie scattering model.
 \end{abstract}
@@
 In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
-We model the extinction coefficient from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
-We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains.
+We model the extinction coefficient, $Q_{ext}$ from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
+We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains (MgSiO$_3$).
 For the particle size distribution we assume a log-normal distribution around a characteristic size with a distribution $\sigma$ of 0.5.
@@
 
-Our model best-fits the data with $\alpha_i$ << 1 and also with much lower temperatures than equilibrium, shown in Figure \ref{fig:ampspec1821tdiff}.
+Our model best-fits the data with $\alpha_i << $1 and also with much lower temperatures than equilibrium, shown in Figure \ref{fig:ampspec1821tdiff}.
 This model has a reduced chi-squared of 1.3, consistent with the data, but not with the effective temperature.
 If we restrict the model to be a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures, the best-fit is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a $\bar{\chi}^2$ = 15.
-Finally, we attempt a model where we restrict the temperature limits to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{citet{gagne2015banyan7}}.
+Finally, we attempt a model where we restrict the temperature limits to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
 The best fit model has $T_{eff} \approx $1590 K, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
-This model fits with $\bar{\chi}^2$ = 2.1.
-However, the temperature contrasts in these models are significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
+The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
+Therefore, we suspect that hot or cold spots on the surface a are a less likely scenario to explain the variability of 2MASS 1821.
 
@@
 These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
-We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems.
-After fitting sinusoids to both of the time series, we find that the
+We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
+After fitting sinusoids to both of the time series, we find that 2MASS 0835 is not variable to within measurement precision.
 
 \section{Acknowledgements}
+Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.
+Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
+This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2016-11-11 ms.tex
I added a few sentences to the conclusions.

@@
 \centering
-\subfloat[2MASS J0835 - \colorbox{red}{fit needs more work} ]{
+\subfloat[2MASS J0835 - \colorbox{red}{fit might need more work} ]{
 	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
@@
 We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
-After fitting sinusoids to both of the time series, we find that 2MASS 0835 is not variable to within measurement precision.
+After fitting sinusoids to both of the time series, we find that 2MASS 0835 has low levels of variability and not wavelength dependence.
+
+2MASS J1821 shows significant variability up to the 1.1\% amplitude at short wavelengths (0.8$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
+This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{yang2016exStormsBD} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
+The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.
+
+We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with Mg-rich pyroxene grains with sub-micron sized particles.
+A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.
+We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
+The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperatures and temperature differences.
+Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.
 

### 2016-11-15 ms.tex
I mainly touched up the intro and added a reference to Ben Lew's paper.

@@
 Brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
-In the case where the targets are bright enough, Doppler imaging can be used to map out the cloud structures on brown dwarfs as in \citet{crossfield2014dopplerimg}.
-
-The photometry brown dwarfs at the L/T transition is explained by (silicate and sulfide?) clouds at a temperature of (?).
+In the case where the targets are bright enough for high resolution spectroscopy, Doppler imaging can be used to map out the cloud structures on brown dwarfs \citep{crossfield2014dopplerimg}.
 
@@
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L5 brown dwarf known to be variable with a period of 9 hr.
+2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a period of 9 hr.
+The basic properties of each system are listed in Table \ref{tab:bdProp}.
 
-Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$ \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.
+Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ (enstatite) and Mg$_2$SiO$_4$ (forsterite) \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.
 
@@
 \caption{Brown Dwarf Properties}\label{tab:bdProp}
-\begin{tabular}{ccccrr}
-Name & Rotation Period & Spectral Type & K magnitude  & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
--- & (hr) & -- & -- & (K) & (km/s) \\
+\begin{tabular}{cccccrr}
+Name & Rotation Period & Spectral Type & K magnitude  & $J$ - $K$ & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
+-- & (hr) & -- & -- & -- & (K) & (km/s) \\
 \hline \hline
-2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
-2MASS 0835 & 3.1\tablenotemark{d} & L4 Pec\tablenotemark{b} - L5 & 11.65 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
+2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1.78 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
+2MASS 0835 & 3.1\tablenotemark{e} & L4 Pec\tablenotemark{b} - L5\tablenotemark{f} & 11.65 & 2.03 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
 \end{tabular}
@@
 \tablenotetext{d}{\citet{blake2010nirspecVS}}
-\tablenotetext{e}{\citet{koen2004ibandBD}}
+\tablenotetext{e}{Tentative period from \citet{koen2004ibandBD}}
+\tablenotetext{f}{\citet{cruz2003coolNeighbors}}
 \end{table*}
@@
 For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
-We obtained spectrophotometry over 4.65 hours, covering about half of a rotation period for 2MASS J0835.
+We obtained spectrophotometry over 4.65 hours, covering 1.5 rotation periods for 2MASS J0835.
 
@@
 This was also observed in the shorter wavelength range of 1.1~$\mu$m to 1.7~$\mu$m in \citet{yang2016exStormsBD}.
+
+This type of wavelength trend was also recently observed for WISEP J004701.06+680352.1 \citep{lew2016w0047}, which has a much $J-K$ 2.55 spectrum.
+In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains.
 

### 2016-11-18 ms.tex
I added the updated intro and a color magnitude diagram. I don't think I actually committed the intro updates last time.

@@
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a period of 9 hr.
+2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a period of 3 hr.
 The basic properties of each system are listed in Table \ref{tab:bdProp}.
@@
 
-\section{Observations}
+In this paper, we describe time series observations of both 2MASS J1821 and 2MASS J0835 over one rotation period with spectral coverage from 0.8 to 2.4 $\mu$m.
+In Section \ref{sec:obs}, we describe our observations with the Infrared Telescope Facility (IRTF).
+In Section \ref{sec:ModelFits}, we describe how we fit the data with sinusoidal models to create an amplitude spectrum.
+We fit the amplitude spectra with two different physical models.
+We conclude in Section \ref{sec:conclusions}.
+
+\section{Observations}\label{sec:obs}
 
@@
 We obtained spectrophotometry over 4.65 hours, covering 1.5 rotation periods for 2MASS J0835.
+%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
 
@@
 We were able to measure spectrophotometry over 7.47 hours, which was 1.8 rotations at the 4.2 rotation period from \citet{metchev2015weatherII}.
+%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px
 
@@
 Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
-%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
 
-%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px
+We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
+The program also included WISE J1906+4011, but weather prevented successful observations of this brown dwarf.
+Table \ref{tab:obsParam} shows the observing parameters for each of the two observed targets including the integration time, number of integrations and reference star.
 
 We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
-We used a 0.9~$\mu$m dichoric to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
+We used a 0.9~$\mu$m dichroic to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
 For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
-For 2MASS J0835, we were unable to obtain photometry - why? due to the fainter source?
+For 2MASS J0835, the source was too faint for photometry in $i$ band.
 
@@
 
-We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
-The program also included WISE J1906+4011, but weather prevented successful observations of this brown dwarf.
-Table \ref{tab:obsParam} shows the observing parameters for each target including the integration time, number of integrations and reference star.
-
-Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp.
+Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp while science data was taken with a 3$\times$60\arcsec\ slit to minimized slit losses.
 We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
@@
 
-As in \citep{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
+As in \citet{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
 We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
@@
 
-\section{Light Curves}
+\subsection{Light Curves}
 
@@
 The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption.
-The reference stars are significantly higher temperatures.
-Bottom Panels: Dynamic spectrum of 2MASS J1821.}
+The reference stars have significantly bluer spectra than the brown dwarfs.
+Bottom Panels: Dynamic spectra of each brown dwarf system.}
 	\label{fig:specphot}
@@
 Figure \ref{fig:specphot} shows the dynamic spectra for both brown dwarfs with the individual spectra of the target and reference stars on the upper panels.
-At the few percent level, 2MASS j0835 shows no variations or systematics.
+At the $\lesssim 1$\% level, 2MASS J0835 shows no variations or systematics.
 2MASS J1821 on the other hand, shows a periodic signal that is strongest at the short wavelength and gradually gets smaller toward longer wavelengths.
@@
 
-\section{Sinusoidal Model Fits}
+\section{Sinusoidal Model Fits}\label{sec:ModelFits}
 
@@
 
-\section{Conclusions}
+\section{Conclusions}\label{sec:conclusions}
 
@@
 This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
+
+\appendix
+
+\section{Color-Magnitude Diagram}
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{color_mag.pdf}
+\caption{Color-Magnitude diagram from Dupuy and Liu.}\label{fig:CMD}
+\end{centering}
+\end{figure}
 

### 2016-11-19 ms.tex
I added a 2MASS J1821 label and an updated reference to the color magnitude diagram.
I turned off the rasterization of the image and added an acknowledgement to astropy.
I updated the time series plots to be in JD instead of saying orbital phase.

@@
 	}
-	\caption{Phase folded time series for both systems.}
+	\caption{Time series for each system. Alternating colors are used to distinguished the light curves with offsets.}
 	\label{fig:tserPfold}
@@
 This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
+This research made use of the \texttt{astropy} package \citep{astropy2013}.
 
@@
 \includegraphics[width=0.5\textwidth]{color_mag.pdf}
-\caption{Color-Magnitude diagram from Dupuy and Liu.}\label{fig:CMD}
+\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}.}\label{fig:CMD}
 \end{centering}

### 2016-11-20 ms.tex
I touched up some of the intro and description of the time series.

@@
 
-We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres.
+We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres with the techniques of \citet{schlawin2014} to achieve high precision spectro-photometry.
 2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
@@
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a period of 3 hr.
+2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a tentative period of 3 hr \citep{koen2004ibandBD}, which also permitted multiple rotation periods.
 The basic properties of each system are listed in Table \ref{tab:bdProp}.
@@
 2MASS J1821 on the other hand, shows a periodic signal that is strongest at the short wavelength and gradually gets smaller toward longer wavelengths.
-2MASS J1821 also exhibits systematic trends near strong slopes in the raw spectra due to telluric absorption bands.
+2MASS J1821 also exhibits systematic trends near strong slopes in the raw spectra due to telluric absorption bands at 1.4 and 1.8~$\mu$m.
 
@@
 	}
-	\caption{Time series for each system. Alternating colors are used to distinguished the light curves with offsets.}
+	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
 	\label{fig:tserPfold}
@@
 
-2MASS J0835 exhibits no periodic behavior whereas 2MASS 1821 shows large varations when phasing the dynamic spectra at the known rotation periods of the two brown dwarfs, shown in Figure \ref{fig:tserPfold}.
+2MASS J0835 exhibits very little variability over our 4.8 hr whereas 2MASS 1821 shows large varations when phasing the dynamic spectra at the known rotation periods of the two brown dwarfs, shown in Figure \ref{fig:tserPfold}.
 For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.

### 2016-11-20 ms.tex
I went through and updated the section on the amplitude spectrum fits.

@@
 For the fits, we include a 4 free parameters: $A$, $t_0$, $B$ and $C$.
-We fixed the sinusoidal period $\tau$ at the literature value of periodicity because there are also variations due to variable telluric variation that are not relevant to the brown dwarf system.
+We fixed the sinusoidal period $\tau$ at the literature value of rotation period (Table \ref{tab:bdProp}) because are trends (with a period of $\sim$24 hr) due to uncorrected telluric variations that that are not relevant to the brown dwarf system.
 We imposed a prior that $A \geq 0$ so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
@@
 	\caption{Sine fit amplitude versus wavelength for each brown dwarf.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}
+The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.
+2MASS J0835 shows no clear trend in wavelength, while 2MASS J1821 has a strong slope indicative of Mie-scattering particles.}
 	\label{fig:ampSpec}
@@
 The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
-The amplitude spectrum of 2MASS J0835 shown in Figure \ref{fig:ampspec0835} shows random fluctuations as a function of wavelength.
+The amplitude spectrum of 2MASS J0835 shown in Figure \ref{fig:ampspec0835} shows small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
 2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
-This was also observed in the shorter wavelength range of 1.1~$\mu$m to 1.7~$\mu$m in \citet{yang2016exStormsBD}.
-
-This type of wavelength trend was also recently observed for WISEP J004701.06+680352.1 \citep{lew2016w0047}, which has a much $J-K$ 2.55 spectrum.
-In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains.
+This was is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
 
@@
 We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains (MgSiO$_3$).
-For the particle size distribution we assume a log-normal distribution around a characteristic size with a distribution $\sigma$ of 0.5.
+For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
 
@@
 The WFC3 spectrum is not affected by the telluric absorption the way the SpeX data is.
-\citet{yang2015hstRotBD} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821, consistent with our Mie scattering fit.
+\citet{yang2015hstRotBD} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and consistent with our Mie scattering fit.
+
+A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{lew2016w0047}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
+In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains, similar to our characteristic particle size.
 
@@
 \end{equation}
-where $\alpha_1$ and $\alpha_2$ are the areal fractions of the two temperature layers limited to [0,1], $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.
+where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first ($T_1$ and second ($T_2$) regions respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.
+$\alpha_1$ and $\alpha_2$ are limited to [0,1].
 Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
@@
 
-Our model best-fits the data with $\alpha_i << $1 and also with much lower temperatures than equilibrium, shown in Figure \ref{fig:ampspec1821tdiff}.
-This model has a reduced chi-squared of 1.3, consistent with the data, but not with the effective temperature.
-If we restrict the model to be a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures, the best-fit is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a $\bar{\chi}^2$ = 15.
-Finally, we attempt a model where we restrict the temperature limits to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
-The best fit model has $T_{eff} \approx $1590 K, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
-The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly more than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
+We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
+To be close to the effective temperature of the brown dwarf, we fix $T_1$ to be 1600 K and only vary $T_2$.
+This model is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a reduced chi-squared, $\bar{\chi}^2$ = 15.
+Next, we attempt a model where we allow $\alpha_1$ and $\alpha_2$ to be free parameters and restrict the temperature limits of the two regions to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
+The best fit model has $T_{eff} \approx $1590 K and $\bar{\chi}^2$=2.1, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
+Finally, we consider a model where all four parameters, $\alpha_1$, $\alpha_2$, $T_1$ and $T_2$ are all free.
+With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
+THe $\alpha$ values are much smaller indicating that the model is like dark patch.
+
+The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly larger than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
 Therefore, we suspect that hot or cold spots on the surface a are a less likely scenario to explain the variability of 2MASS 1821.
@@
 We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
-After fitting sinusoids to both of the time series, we find that 2MASS 0835 has low levels of variability and not wavelength dependence.
+After fitting sinusoids to both of the time series, we find that 2MASS 0835 has low levels of variability and no significant wavelength dependence.
 

### 2016-11-21 ms.tex
Some word touch-ups in the sinusoidal fit section.

@@
 \end{equation}
-where $F$ is the flux as a function of time ($t$), A is the amplitude of the variations, $t_0$ is the time offset of the variations and $\tau$ is the and B and C are linear terms describing the baseline trend.
-For the fits, we include a 4 free parameters: $A$, $t_0$, $B$ and $C$.
-We fixed the sinusoidal period $\tau$ at the literature value of rotation period (Table \ref{tab:bdProp}) because are trends (with a period of $\sim$24 hr) due to uncorrected telluric variations that that are not relevant to the brown dwarf system.
+where $F$ is the flux as a function of time ($t$), A is the amplitude of the variations, $t_0$ is the time offset of the variations, $\tau$ is period of the variations and B and C are linear terms describing the baseline trend.
+For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters.
+We fixed the sinusoidal period $\tau$ at the literature value of rotation period (Table \ref{tab:bdProp}) because there are trends (with a period of $\sim$24 hr) due to uncorrected telluric variations that that are not relevant to the brown dwarf system.
 We imposed a prior that $A \geq 0$ so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
@@
 The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
-The amplitude spectrum of 2MASS J0835 shown in Figure \ref{fig:ampspec0835} shows small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
+The amplitude spectrum ($A$ as a function of wavelength) of 2MASS J0835, (Figure \ref{fig:ampspec0835}), shows small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
 2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
 This was is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
+We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.
 

### 2016-11-22 ms.tex
I fixed typos and re-worded throughput.

@@
 \begin{abstract}
-L and T brown dwarfs show variability associated with the rotation of non-uniform atmospheres.
+L and T brown dwarfs show variability associated with the rotation of heterogeneous atmospheres.
 We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5 using the Infrared Telescope Facility (IRTF).
-2MASS J0835 shows relatively little spectral variability from 0.8~$\mu$m to 2.4~$\mu$m.
-2MASS J1821 by contrast shows a strong variability in the shorter wavelengths that falls off toward 2.4~$\mu$m, that can be fit by Mie extinction of sub-micron dust particles.
+2MASS J0835 shows low level ($\lesssim 0.4\%$) spectral variability with no wavelength dependence from 0.8~$\mu$m to 2.4~$\mu$m.
+2MASS J1821, by contrast, shows $\sim$2\%  variability in the shorter wavelengths that falls off toward 2.4~$\mu$m.
+The variability amplitude spectrum can be fit by Mie extinction of sub-micron dust particles.
 It can also be fit by a hot spots on the brown dwarf surface, but they require implausible temperature variations, so we prefer the Mie scattering model.
@@
 The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
-Brown dwarfs may be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
+Brown dwarfs can also be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
 In the case where the targets are bright enough for high resolution spectroscopy, Doppler imaging can be used to map out the cloud structures on brown dwarfs \citep{crossfield2014dopplerimg}.
@@
 
-\citet{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) was a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
+\citet{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) is a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
 \citet{burgaser2014irtf} observed the binary system Luhman 16 AB and used the more stable Luhman 16A as a simultaneous reference to measure spectral variability in Luhman 16B.
 
-We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres with the techniques of \citet{schlawin2014} to achieve high precision spectro-photometry.
+We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres with the exoplanet techniques of \citet{schlawin2014} to achieve high precision spectro-photometry.
 2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
@@
 2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a tentative period of 3 hr \citep{koen2004ibandBD}, which also permitted multiple rotation periods.
+2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a tentative period of 3.1 hr \citep{koen2004ibandBD}, which also permitted about 1.5 rotation periods.
 The basic properties of each system are listed in Table \ref{tab:bdProp}.
@@
 In Section \ref{sec:ModelFits}, we describe how we fit the data with sinusoidal models to create an amplitude spectrum.
-We fit the amplitude spectra with two different physical models.
+We fit the variability amplitude spectra with two different physical models - Mie scattering from clouds and a heterogenous temperature distribution.
 We conclude in Section \ref{sec:conclusions}.
@@
 
-We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry.
+We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry which employs a large 3\arcsec $\times$ 60\arcsec\ slit.
 We used a 0.9~$\mu$m dichroic to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
-For guiding, we use the MORIS imager in the SDSS $i$ band and 60 second long exposures in order to obtain simultaneous photometry on 2MASS J1821.
-For 2MASS J0835, the source was too faint for photometry in $i$ band.
+For guiding, we use the MORIS imager in the SDSS $i$ band.
+For 2MASS J0835, we used short (<15 sec) integrations as is standard for guiding, so the source was too faint for photometry in $i$ band.
+For 2MASS J1821, we extended the integration time to 60 seconds in order to obtain simultaneous $i$ band photometry.
 
@@
 \caption{Observing Parameters}\label{tab:obsParam}
-\begin{tabular}{ccccc}
-Target & Observing Date & N$_{int}$ & t$_{exp}$ & Reference Star \\
--- & UT Start & -- & (s) & -- \\
+\begin{tabular}{cccccc}
+Target & Observing Date & N$_{int}$ & t$_{int}$ & Duration & Reference Star \\
+-- & UT Start & -- & (s) & (hr) &  -- \\
 \hline
-2MASS J1821 & 2015-12-31 & 363 & 45 & 2MASS 18212622+1414064 \\
-2MASS J0835 & 2016-06-25 & 352 & 60 & 2MASS 08354383-0819212 \\
+2MASS J1821 & 2015-12-31 & 363 & 45 & 4.65 &  2MASS 18212622+1414064 \\
+2MASS J0835 & 2016-06-25 & 352 & 60 & 7.47 &  2MASS 08354383-0819212 \\
 \end{tabular}
 \end{center}
-\tablenotetext{}{}
+\tablenotetext{}{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp.
+The duration is the total time from start to end of the observations including the reset times and overheads.}
 \end{table*}
@@
 The spatial profiles are fit with low order polynomials with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
+These spatial profiles are then used to calculate a weighted sum spectrum.
 
@@
 
-2MASS J0835 exhibits very little variability over our 4.8 hr whereas 2MASS 1821 shows large varations when phasing the dynamic spectra at the known rotation periods of the two brown dwarfs, shown in Figure \ref{fig:tserPfold}.
+2MASS J0835 exhibits very little variability over our 4.7 hr whereas 2MASS 1821 shows large variability at the 4.2 hr rotation period, shown in Figure \ref{fig:tserPfold}.
 For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.
@@
 With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
-THe $\alpha$ values are much smaller indicating that the model is like dark patch.
+The $\alpha$ values,  $\alpha_i <<$ 1 indicating that the model fits with dark patches on a small fraction of the surface.
 
 The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly larger than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
-Therefore, we suspect that hot or cold spots on the surface a are a less likely scenario to explain the variability of 2MASS 1821.
+Therefore, we suspect that hot or cold spots on the surface are a less plausible explanation of the variability of 2MASS 1821 than a heterogenous temperature distribution.
 
@@
 We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
-The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperatures and temperature differences.
+The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperature differences.
 Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.

### 2016-12-04 ms_v2.tex
Adam's suggested changes in v2

--- 2016-11-22 ms.tex
@@
-%%
-%% Beginning of file 'sample.tex'
-%%
-%% Modified 2005 December 5
-%%
-%% This is a sample manuscript marked up using the
-%% AASTeX v5.x LaTeX 2e macros.
-
-%% The first piece of markup in an AASTeX v5.x document
-%% is the \documentclass command. LaTeX will ignore
-%% any data that comes before this command.
-
-%% The command below calls the preprint style
-%% which will produce a one-column, single-spaced document.
-%% Examples of commands for other substyles follow. Use
-%% whichever is most appropriate for your purposes.
-%%
-%%\documentclass[12pt,preprint]{aastex}
-
-%% manuscript produces a one-column, double-spaced document:
-
-%\documentclass{article}
+% manuscript produces a one-column, double-spaced document:
+%\documentclass[12pt,preprint]{aastex}
 \documentclass[twocolumn]{aastex6}
@@
 
-%% preprint2 produces a double-column, single-spaced document:
+% preprint2 produces a double-column, single-spaced document:
 %\documentclass[preprint2]{aastex}
-
-%% Sometimes a paper's abstract is too long to fit on the
-%% title page in preprint2 mode. When that is the case,
-%% use the longabstract style option.
-
-%% \documentclass[preprint2,longabstract]{aastex}
-
-%% If you want to create your own macros, you can do so
-%% using \newcommand. Your macros should appear before
-%% the \begin{document} command.
-%%
-%% If you are submitting to a journal that translates manuscripts
-%% into SGML, you need to follow certain guidelines when preparing
-%% your macros. See the AASTeX v5.x Author Guide
-%% for information.
 
@@
 \newcommand{\degree}{$^\circ$}
+\newcommand{\vtan}{$V_{tan}$}
+\newcommand{\kms}{km~s$^{-1}$}
+\newcommand{\msun}{M$_{\sun}$}
+\newcommand{\rjup}{R$_{Jup}$}
+\newcommand{\ldl}{$\lambda/{\Delta}{\lambda}$}
+\newcommand{\lsun}{L$_{\sun}$}
+\newcommand{\lbol}{$\log_{10}{L_{bol}/L_{\sun}}$}
+\newcommand{\teff}{T$_{eff}$}
+\newcommand{\logg}{$\log{g}$}
+\newcommand{\fsed}{$f_{sed}$}
+\newcommand{\kzz}{$K_{zz}$}
+\newcommand{\meth}{CH$_4$}
+\newcommand{\wat}{H$_2$O}
+\newcommand{\sha}{2MASS~J0835$-$0819}
+\newcommand{\shb}{2MASS~J1812+1414}
 
-%% You can insert a short comment on the title page using the command below.
+\slugcomment{To be submitted to ApJ/AJ}
 
-%\slugcomment{DHS White Paper}
-
-%% If you wish, you may supply running head information, although
-%% this information may be modified by the editorial offices.
-%% The left head contains a list of authors,
-%% usually a maximum of three (otherwise use et al.).  The right
-%% head is a modified title of up to roughly 44 characters.
-%% Running heads will not print in the manuscript style.
-
-\shorttitle{IRTF BD Spectro-photometry}
+\shorttitle{Spectral Variability of L Dwarfs}
 \shortauthors{Schlawin et al.}
-
-%% This is the end of the preamble.  Indicate the beginning of the
-%% paper itself with \begin{document}.
 
@@
 
-%% LaTeX will automatically break titles if they run longer than
-%% one line. However, you may use \\ to force a line break if
-%% you desire.
-
-\title{IRTF Spectro-Photometry of Two Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010}
+\title{Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010}
 
@@
 
-\author{E. Schlawin, A. Burgasser, J. Teske, J. Gizis, T. Karalidi }
-\affil{Steward Observatory, Tucson AZ 85721, UCSD, DTM, University of Delaware}
-\email{eas342@email.arizona.edu}
+\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J. Teske\altaffilmark{4}, J. Gizis\altaffilmark{5} \and T. Karalidi\altaffilmark{1}}
 
-%This is a test by Gizis
-
-%% Notice that each of these authors has alternate affiliations, which
-%% are identified by the \altaffilmark after each name.  Specify alternate
-%% affiliation information with \altaffiltext, with one command per each
-%% affiliation.
-
-%\altaffiltext{1}{Hubble Postdoctoral Fellow}
-
-%% Mark off your abstract in the ``abstract'' environment. In the manuscript
-%% style, abstract will output a Received/Accepted line after the
-%% title and affiliation information. No date will appear since the author
-%% does not have this information. The dates will be filled in by the
-%% editorial office after submission.
+\altaffiltext{1}{Steward Observatory, Tucson AZ 85721 \email{eas342@email.arizona.edu}}
+\altaffiltext{2}{Visiting Astronomer at the Infrared Telescope Facility, which is operated by the University of Hawaii under contract NNH14CK55B with the National Aeronautics and Space Administration}
+\altaffiltext{3}{Center for Astrophysics and Space Science, University of California San Diego, La Jolla, CA 92093, USA}
+\altaffiltext{4}{Carnegie DTM, 5241 Broad Branch Road, NV, Washington, DC 20015, USA}
+\altaffiltext{5}{Department of Physics and Astronomy, University of Delaware, Newark, DE 19716, USA}
 
 \begin{abstract}
-L and T brown dwarfs show variability associated with the rotation of heterogeneous atmospheres.
-We present a high precision ground-based time series study of 2 brown dwarfs - 2MASS J08354256-0819237 and 2MASS J18212815+1414010, both of spectral type L4-L5 using the Infrared Telescope Facility (IRTF).
-2MASS J0835 shows low level ($\lesssim 0.4\%$) spectral variability with no wavelength dependence from 0.8~$\mu$m to 2.4~$\mu$m.
-2MASS J1821, by contrast, shows $\sim$2\%  variability in the shorter wavelengths that falls off toward 2.4~$\mu$m.
-The variability amplitude spectrum can be fit by Mie extinction of sub-micron dust particles.
-It can also be fit by a hot spots on the brown dwarf surface, but they require implausible temperature variations, so we prefer the Mie scattering model.
+Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
+The spectral character of these variations yield insight into the composition and vertical structure of the clouds.
+Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
+By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m band.
+We find that 2MASS~J0835$-$0819 exhibits low-level ($\lesssim$ 0.4\% per band) variability with no spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m and declines toward longer wavelengths.
+The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414 over 1.1--1.6~$\mu$m.
+We reproduce the variability amplitude spectrum of 2MASS~J1821+1414 with Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths.
+An alternate model based on surface hot spots more accurately reproduces the variability amplitude spectrum, but requires implausibly large temperature variations.
+{\bf [phase variation?
+differences between 0835 and 1821?]}
 \end{abstract}
 
-%% Keywords should appear after the \end{abstract} command. The uncommented
-%% example has been keyed in ApJ style. See the instructions to authors
-%% for the journal to which you are submitting your paper to determine
-%% what keyword punctuation is appropriate.
-
-\keywords{Brown Dwarfs}
-
-%% From the front matter, we move on to the body of the paper.
-%% In the first two sections, notice the use of the natbib \citep
-%% and \citet commands to identify citations.  The citations are
-%% tied to the reference list via symbolic KEYs. The KEY corresponds
-%% to the KEY in the \bibitem in the reference list below. We have
-%% chosen the first three characters of the first author's name plus
-%% the last two numeral of the year of publication as our KEY for
-%% each reference.
-
-%% Authors who wish to have the most important objects in their paper
-%% linked in the electronic edition to a data center may do so by tagging
-%% their objects with \objectname{} or \object{}.  Each macro takes the
-%% object name as its required argument. The optional, square-bracket 
-%% argument should be used in cases where the data center identification
-%% differs from what is to be printed in the paper.  The text appearing 
-%% in curly braces is what will appear in print in the published paper. 
-%% If the object name is recognized by the data centers, it will be linked
-%% in the electronic edition to the object data available at the data centers  
-%%
-%% Note that for sources with brackets in their names, e.g. [WEG2004] 14h-090,
-%% the brackets must be escaped with backslashes when used in the first
-%% square-bracket argument, for instance, \object[\[WEG2004\] 14h-090]{90}).
-%%  Otherwise, LaTeX will issue an error.
+\keywords{techniques: spectroscopic -- stars: atmospheres -- stars: brown dwarfs -- stars: individual (\objectname{2MASS J08354256-0819237}, \objectname{2MASS J18212815+1414010}) -- stars: late-type -- stars: variables: general}
 
@@
 
-Brown dwarfs atmospheres are an intriguing environment to explore cloud composition, particle size and formation that also complement studies of exoplanet atmospheres.
-Their temperatures are cool enough that they span condensation points of many cloud-producing  compounds including H$_2$O, MgSiO$_3$, Mg$_2$SiO$_4$ and Fe \citep{marley2015rev}.
+The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
+In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}
+whose surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
+Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have photospheric heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
+Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
 
-The cloud layers may be studied from the direct spectroscopy of a populations of brown dwarf atmospheres \citep[e.g.][]{burgasser2006ltTrans,liu2006}.
-Brown dwarfs can also be observed over their rotation periods to understand the spatial cloud structure and composition, that can change rapidly with time \citep[e.g.][]{yang2016exStormsBD}.
-In the case where the targets are bright enough for high resolution spectroscopy, Doppler imaging can be used to map out the cloud structures on brown dwarfs \citep{crossfield2014dopplerimg}.
+Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure, as grey grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
+The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been show to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
+Wavelength-dependent phase variance in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
+Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.
 
-L dwarfs are found to be variable with periods of 1-100 hours \citep{bailer-jones1999bdvar,bailer-jones1999varevo}.
-This variability is explained by a patchy clouds at the L/T transition \citep{marley2010patchyc}.
-Virtually all L dwarfs and most T dwarfs likely have photospheric heterogeneities that cause flux variations larger than 0.2\% in the near infrared \citep{metchev2015weatherII}
+Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
+Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
+In contrast, the stability of space-based platforms $Hubble$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
+However, these facilities are not suited, for building up robust statistical samples to assess the physical bases of surface heterogeneity or different variability modes.
 
-\citet{burgaser2014irtf} first demonstrated that the Infrared Telescope Facility (IRTF) is a useful tool for characterizing brown dwarf variability and that a simultaneous reference can be used to correct for common-mode variability, such as telluric transmission variations.
-\citet{burgaser2014irtf} observed the binary system Luhman 16 AB and used the more stable Luhman 16A as a simultaneous reference to measure spectral variability in Luhman 16B.
+High-precision, spectro-photometric monitoring from the ground has been demonstrated in a few specific cases.
+\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
+This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy.
+A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
+In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion.
+Both studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
 
-We observed the two brown dwarfs as part of a pilot program to assess the efficacy of IRTF for measuring spectral variability in brown dwarf atmospheres with the exoplanet techniques of \citet{schlawin2014} to achieve high precision spectro-photometry.
-2MASS J18212815+1414010 is an L5 brown dwarf showing a triangular H-band spectrum \citep{looper2008peculiarLdwarfs}.
-The spectral type is peculiar and has also been designated as L4 \citep{gagne2015banyan7}.
-2MASS J1821's short rotation period (4.2 hr) allows for time series spectroscopy for all longitudes in a single ground based observation night.
-2MASS J08354256-0819237 \citep{cruz2003coolNeighbors} is also an L4-L5 brown dwarf known to be variable with a tentative period of 3.1 hr \citep{koen2004ibandBD}, which also permitted about 1.5 rotation periods.
-The basic properties of each system are listed in Table \ref{tab:bdProp}.
+This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions.
+We describe the target identification strategy and pilot targets in Section~\ref{sec:targets}.
+In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
+In Section~\ref{sec:ModelFits}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
+We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
+We summarize our results in Section~\ref{sec:conclusions}.
 
-Both brown dwarfs' effective temperatures in Table \ref{tab:bdProp} are near the condensation temperatures of MgSiO$_3$ (enstatite) and Mg$_2$SiO$_4$ (forsterite) \citep{marley2015rev} so these are viable candidates for clouds in their atmospheres.
+\section{Target Selection}\label{sec:targets}
 
-\begin{table*}
-\begin{center}
-\caption{Brown Dwarf Properties}\label{tab:bdProp}
-\begin{tabular}{cccccrr}
-Name & Rotation Period & Spectral Type & K magnitude  & $J$ - $K$ & T$_\mathrm{eff}$ &  $v$ sin($i$) \\
--- & (hr) & -- & -- & -- & (K) & (km/s) \\
-\hline \hline
-2MASS 1821 & 4.2\tablenotemark{a} & L4 Pec\tablenotemark{b} - L5 Pec\tablenotemark{c} & 11.14 & 1.78 & 1600 $\pm$ 100\tablenotemark{b} & 28.85 $\pm$ 0.16\tablenotemark{d}\\
-2MASS 0835 & 3.1\tablenotemark{e} & L4 Pec\tablenotemark{b} - L5\tablenotemark{f} & 11.65 & 2.03 & 1800 $\pm$ 100\tablenotemark{b} & 14.18 $\pm$ 0.43\tablenotemark{d} \\
-\end{tabular}
-\end{center}
-\tablenotetext{a}{\citet{metchev2015weatherII}.}
-\tablenotetext{b}{\citet{gagne2015banyan7}.}
-\tablenotetext{c}{\citet{looper2008peculiarLdwarfs}}
-\tablenotetext{d}{\citet{blake2010nirspecVS}}
-\tablenotetext{e}{Tentative period from \citet{koen2004ibandBD}}
-\tablenotetext{f}{\citet{cruz2003coolNeighbors}}
-\end{table*}
+We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}.
+The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$.
+We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
+Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been observed to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
+Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming radius R = 1~{\rjup}.
+There is an $H$ = 12.3 star (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}.
+This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
+\citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
+There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.
 
-In this paper, we describe time series observations of both 2MASS J1821 and 2MASS J0835 over one rotation period with spectral coverage from 0.8 to 2.4 $\mu$m.
-In Section \ref{sec:obs}, we describe our observations with the Infrared Telescope Facility (IRTF).
-In Section \ref{sec:ModelFits}, we describe how we fit the data with sinusoidal models to create an amplitude spectrum.
-We fit the variability amplitude spectra with two different physical models - Mie scattering from clouds and a heterogenous temperature distribution.
-We conclude in Section \ref{sec:conclusions}.
+\begin{deluxetable*}{llcccccccl}
+\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
+\tablewidth{0pt}
+\tablehead{
+\colhead{Name} & 
+\colhead{SpT} & 
+\colhead{$d$} & 
+\colhead{2MASS $H$} & 
+\colhead{$J-K_s$} & 
+\colhead{\teff} & 
+\colhead{P$_{rot}$} &
+\colhead{$v\sin{i}$} & 
+\colhead{$i$\tablenotemark{a}} & 
+\colhead{Refs} \\
+ &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($degree$)} \\
+ }
+\startdata
+{\sha} & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
+{\shb} & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
+\enddata
+\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
+A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
+\tablenotetext{b}{Tentative period.}
+\tablerefs{(1) \citet{2003AJ....126.2421C};
+(2) \citet{2012ApJ...752...56F}; 
+(3) \citet{2015ApJ...810..158F};
+(4) \citet{2004MNRAS.354..378K};
+(5) \citet{2010ApJ...723..684B};
+(6) \citet{2008ApJ...686..528L}; 
+(7) \citet{2016MNRAS.455..357S};
+(8) \citet{2015ApJ...798...73G};
+(9) \citet{2015ApJ...799..154M}
+(10) \citet{2015ApJ...798L..13Y}; 
+}
+\end{deluxetable*}
+
+\begin{figure*}
+\centering
+	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
+	\label{fig:image1821}
+	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right).
+Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left.
+The comparison stars referred to in the text appear as blue sources in these images.
+}
+	\label{fig:images}
+	\vspace{0.1in}
+\end{figure*}
 
@@
 
-For 2MASS J0835, we observed a simultaneous reference - 2MASS 08354383-0819212, $J$=12.74, $H$=12.28, $K_S$=12.19 at a distance of 28 arcsec.
-We obtained spectrophotometry over 4.65 hours, covering 1.5 rotation periods for 2MASS J0835.
-%Using MORIS image for distance and plate scale in header of 0.1143 arcsec/px
+We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
+{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
+Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion.
+The short-wavelength limit was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
+For {\sha} our exposures were 15~sec, which was sufficient for guiding but not precision photometry.
+For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
 
-We observed 2MASS J1821 and 2MASS J0835 for one night each with the IRTF.
-For 2MASS J1821, we observed a simultaneous reference - 2MASS 18212622+1414064, $J$=12.58, $H$=11.97, $K_S$=11.82  at a distance of 24\arcsec.
-We were able to measure spectrophotometry over 7.47 hours, which was 1.8 rotations at the 4.2 rotation period from \citet{metchev2015weatherII}.
-%Using SpeX Guider image for distance of 241px  and plate scale in header of 0.116 arcsec/px
+\begin{deluxetable*}{lcccccccll}
+\tablecaption{Observations}\label{tab:obsParam}
+\tablewidth{0pt}
+\tablehead{
+ & \multicolumn{3}{c}{Observation Epoch (UT)} \\
+ \cline{2-4}
+\colhead{Target} & 
+\colhead{Date} & 
+\colhead{Start} & 
+\colhead{End} & 
+\colhead{$N_{int}$} & 
+\colhead{$t_{int}$} & 
+\colhead{Duration} & 
+\colhead{Airmass} & 
+\colhead{Reference Star} & 
+\colhead{Conditions} \\
+ & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Range} }
+\startdata
+{\sha} & 2016-06-25 & XXX & XXX & 352 & 60 & 7.47 & XXX-XXX & J08354383-0819212 & XXX \\
+{\shb} & 2015-12-31 & XXX & XXX & 363 & 45 & 4.65 & XXX-XXX & J18212622+1414064 & XXX \\
+\enddata
+\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp.
+The duration is the total time from start to end of the observations including the reset times and overheads.}
+\end{deluxetable*}
 
-As visible in Figure \ref{fig:specphot1821}, the light curves for 2MASS J1821 repeat the same fluctuations after one rotation period.
-Assuming the brown dwarfs cloud structure was relatively unchanged in one rotation, this enabled confirmation that the signal was astrophysical as opposed to the systematics affecting the same instrument telescope for observations of the  KIC 12557548 system \citep{schlawin2016kic1255}.
+Wavelength calibrations were performed using observations of ThAr  emission lamps with the 0.3$\times$60$\arcsec$.
+We also obtained calibration sequences of ThAr and flat-field lamps with the 3$\times$60$\arcsec$ slit  before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
 
-We observed 2MASS J1821 and J0835 each for one night as part of a pilot program to explore a variety of brown dwarfs with different variability levels and atmospheric temperatures.
-The program also included WISE J1906+4011, but weather prevented successful observations of this brown dwarf.
-Table \ref{tab:obsParam} shows the observing parameters for each of the two observed targets including the integration time, number of integrations and reference star.
-
-We use the same method as \citet{schlawin2014} to obtain high precision spectrophotometry which employs a large 3\arcsec $\times$ 60\arcsec\ slit.
-We used a 0.9~$\mu$m dichroic to split the optical wavelengths to the MORIS imager \citep{Gulbis2011}.
-For guiding, we use the MORIS imager in the SDSS $i$ band.
-For 2MASS J0835, we used short (<15 sec) integrations as is standard for guiding, so the source was too faint for photometry in $i$ band.
-For 2MASS J1821, we extended the integration time to 60 seconds in order to obtain simultaneous $i$ band photometry.
-
-\begin{table*}
-\begin{center}
-\caption{Observing Parameters}\label{tab:obsParam}
-\begin{tabular}{cccccc}
-Target & Observing Date & N$_{int}$ & t$_{int}$ & Duration & Reference Star \\
--- & UT Start & -- & (s) & (hr) &  -- \\
-\hline
-2MASS J1821 & 2015-12-31 & 363 & 45 & 4.65 &  2MASS 18212622+1414064 \\
-2MASS J0835 & 2016-06-25 & 352 & 60 & 7.47 &  2MASS 08354383-0819212 \\
-\end{tabular}
-\end{center}
-\tablenotetext{}{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp.
-The duration is the total time from start to end of the observations including the reset times and overheads.}
-\end{table*}
-
-Wavelength calibrations were performed with a 0.3$\times$60\arcsec\ slit and an argon emission lamp while science data was taken with a 3$\times$60\arcsec\ slit to minimized slit losses.
-We performed calibrations sequences of argon emission lamp spectra and flat fielding with the 3$\times$60\arcsec\ slit both before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
+[ADAM STOPPED HERE]
 
@@
 	}
-	\caption{Top Panels: The target stars' median raw spectrum compared with the reference star.
-The areas near 1.4 and 1.8 $\mu$m are contaminated by telluric water absorption.
+	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).
+These spectra have not been corrected for telluric absorption or instrumental spectral response.
 The reference stars have significantly bluer spectra than the brown dwarfs.
-Bottom Panels: Dynamic spectra of each brown dwarf system.}
+Bottom Panels: Dynamic spectra of each brown dwarf system.
+[MORE DESCRIPTION] {\bf [y-axis in hours not days, change top normalization or y-range so full spectrum is visible, and remove labels]}}
 	\label{fig:specphot}
@@
 
-Figure \ref{fig:specphot} shows the dynamic spectra for both brown dwarfs with the individual spectra of the target and reference stars on the upper panels.
-At the $\lesssim 1$\% level, 2MASS J0835 shows no variations or systematics.
-2MASS J1821 on the other hand, shows a periodic signal that is strongest at the short wavelength and gradually gets smaller toward longer wavelengths.
-2MASS J1821 also exhibits systematic trends near strong slopes in the raw spectra due to telluric absorption bands at 1.4 and 1.8~$\mu$m.
+Figure \ref{fig:specphot} shows the dynamic spectra of both targets, as well as the median spectra of the target and reference stars.
+{\sha} shows no variations or systematics at the $\lesssim1$\% level, while {\shb} shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
+The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than arising from systematic effects (see \citealt{2016ApJ...826..156S}).
+{\shb} does exhibits some systematic features near the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by slight wavelength drifts and lower signals-to-noise.
 
@@
 	}
-	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
+	\caption{Time series for each system with an offset added for clarity.
+Each wavelength bin is labeled on the right side.
+Alternating colors are used to distinguished the light curves with offsets.
+{\bf [increased vertical scale so fluctuations are visible; replace diamonds with vertical bars (unc) or smaller symbols]}}
 	\label{fig:tserPfold}
@@
 
-2MASS J0835 exhibits very little variability over our 4.7 hr whereas 2MASS 1821 shows large variability at the 4.2 hr rotation period, shown in Figure \ref{fig:tserPfold}.
-For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.
-
 \section{Sinusoidal Model Fits}\label{sec:ModelFits}
 
-We fit the time series of each brown dwarf in 25 spectral bins each to assess the wavelength-dependent nature of their variations.
-The simple model can be described as 
+We extracted separate lightcurves for each target in 25 spectral bins of width XXX~$\mu$m, as shown in Figure~\ref{fig:tserPfold}.
+Each of these were fit to a simple sinusoidal model {\bf [NOTE: CHANGE TO COSINE FOR SIMPLER INTERPRETATION OF TO]:
 \begin{equation}
-F(t) = A * \sin(2 \pi (t - t_0)/\tau) + B t + C
+F(t) = A * \cos(2 \pi (t - t_0)/\tau) + B t + C
 \end{equation}
-where $F$ is the flux as a function of time ($t$), A is the amplitude of the variations, $t_0$ is the time offset of the variations, $\tau$ is period of the variations and B and C are linear terms describing the baseline trend.
-For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters.
-We fixed the sinusoidal period $\tau$ at the literature value of rotation period (Table \ref{tab:bdProp}) because there are trends (with a period of $\sim$24 hr) due to uncorrected telluric variations that that are not relevant to the brown dwarf system.
-We imposed a prior that $A \geq 0$ so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
+Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
+For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
+We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.
 
@@
 2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
-This was is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
+This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
 We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.
@@
 \includegraphics[width=0.5\textwidth]{color_mag.pdf}
-\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}.}\label{fig:CMD}
+\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 and 2MASS J0835 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
 \end{centering}

### 2016-12-04 ms.tex
I added a clarification to the color-magnitude diagram.
I made Adam's edits the main ms.tex version.

@@
 
-2MASS J0835 exhibits very little variability over our 4.7 hr whereas 2MASS 1821 shows large variability at the 4.2 hr rotation period, shown in Figure \ref{fig:tserPfold}.
-For 2MASS 1821, the variations are mostly sinusoidal and repeat over multiple rotations of the brown dwarf - the exception is wavelengths near telluric features, such as 1.43~$\mu$m and 1.79~$\mu$m.
-
 \section{Sinusoidal Model Fits}\label{sec:ModelFits}
 
-We fit the time series of each brown dwarf in 25 spectral bins each to assess the wavelength-dependent nature of their variations.
-The simple model can be described as 
+We extracted separate lightcurves for each target in 25 spectral bins of width XXX~$\mu$m, as shown in Figure~\ref{fig:tserPfold}.
+Each of these were fit to a simple sinusoidal model {\bf [NOTE: CHANGE TO COSINE FOR SIMPLER INTERPRETATION OF TO]}:
 \begin{equation}
-F(t) = A * \sin(2 \pi (t - t_0)/\tau) + B t + C
+F(t) = A * \cos(2 \pi (t - t_0)/\tau) + B t + C
 \end{equation}
-where $F$ is the flux as a function of time ($t$), A is the amplitude of the variations, $t_0$ is the time offset of the variations, $\tau$ is period of the variations and B and C are linear terms describing the baseline trend.
-For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters.
-We fixed the sinusoidal period $\tau$ at the literature value of rotation period (Table \ref{tab:bdProp}) because there are trends (with a period of $\sim$24 hr) due to uncorrected telluric variations that that are not relevant to the brown dwarf system.
-We imposed a prior that $A \geq 0$ so that a solution with a $\pi$ phase offset and negative amplitude isn't found.
+Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
+For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
+We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.
 

### 2016-12-04 ms.tex
I updated the airmass, UT start and FWHM. I had to correct the dates of the observations.

@@
 \colhead{Reference Star} & 
-\colhead{Conditions} \\
- & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Range} }
+\colhead{FWHM} \\
+ & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
 \startdata
-{\sha} & 2016-06-25 & XXX & XXX & 352 & 60 & 7.47 & XXX-XXX & J08354383-0819212 & XXX \\
-{\shb} & 2015-12-31 & XXX & XXX & 363 & 45 & 4.65 & XXX-XXX & J18212622+1414064 & XXX \\
+{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
+{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
 \enddata
 \tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp.
-The duration is the total time from start to end of the observations including the reset times and overheads.}
+The duration is the total time from start to end of the observations including the reset times and overheads.
+The FWHM is the measured median value of the time series around 1.6$\mu$m.}
 \end{deluxetable*}

### 2016-12-04 ms.tex
I got rid of duplicate references.

@@
 Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
-The spectral character of these variations yield insight into the composition and vertical structure of the clouds.
+The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds.
 Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
-By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m band.
+By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
 We find that 2MASS~J0835$-$0819 exhibits low-level ($\lesssim$ 0.4\% per band) variability with no spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m and declines toward longer wavelengths.
@@
 
-Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure, as grey grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
+Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
 The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been show to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
@@
 
-As in \citet{schlawin2016kic1255}, we perform background subtraction over the entire slit with polynomial fit.
+As in \citet{2016ApJ...826..156S}, we perform background subtraction over the entire slit with polynomial fit.
 We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
@@
 2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
-This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{yang2016exStormsBD}.
+This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}.
 We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.
@@
 with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
-Also shown in the figure is the WFC3 amplitude from \citet{yang2015hstRotBD}.
+Also shown in the figure is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}.
 The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
@@
 
-\citet{yang2015hstRotBD} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
+\citet{2015ApJ...798L..13Y} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
 Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
@@
 The WFC3 spectrum is not affected by the telluric absorption the way the SpeX data is.
-\citet{yang2015hstRotBD} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and consistent with our Mie scattering fit.
+\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and consistent with our Mie scattering fit.
 
-A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{lew2016w0047}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
+A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
 In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains, similar to our characteristic particle size.
@@
 2MASS J1821 shows significant variability up to the 1.1\% amplitude at short wavelengths (0.8$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
-This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{yang2016exStormsBD} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
+This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
 The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.

### 2016-12-04 ms.tex
I put in a few ground-based exoplanet MOS observations as evidence for ground-based high precision obs.

@@
 
-High-precision, spectro-photometric monitoring from the ground has been demonstrated in a few specific cases.
+High-precision, spectro-photometric monitoring from the ground has been demonstrated for transiting exoplanet observations \citep[e.g.][]{bean10,stevenson2016hatp26} and brown dwarf variability measurements.
 \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
@@
 In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion.
-Both studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
+These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
 

### 2016-12-07 ms.tex
I cleaned up the references to MOS methods for spectro-photometry.

--- 2016-12-04 ms.tex
@@
 Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
-Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
-In contrast, the stability of space-based platforms $Hubble$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
+Some ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) have been limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
+In contrast, the stability of space-based platforms $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
 However, these facilities are not suited, for building up robust statistical samples to assess the physical bases of surface heterogeneity or different variability modes.
 
-High-precision, spectro-photometric monitoring from the ground has been demonstrated in a few specific cases.
+Multi-Object Spectroscopy (MOS) which uses references stars to correct for telluric effects with a multi-object spectrograph or long slit \citep[e.g.][]{bean10,bean2013,gibson13clouds,stevenson2016hatp26} has significantly improved the precision of ground-based spectro-photometry.
 \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
@@
 In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion.
-Both studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
+These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground and with IRTF from 1-2.5~$\mu$m.
 

### 2016-12-07 ms.tex
I updated the wavelength bin size and the cosine fit formula.

@@
 
-We extracted separate lightcurves for each target in 25 spectral bins of width XXX~$\mu$m, as shown in Figure~\ref{fig:tserPfold}.
-Each of these were fit to a simple sinusoidal model {\bf [NOTE: CHANGE TO COSINE FOR SIMPLER INTERPRETATION OF TO]}:
+We extracted separate light curves for each target in 25 spectral bins of width 0.060~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model:
 \begin{equation}
-F(t) = A * \cos(2 \pi (t - t_0)/\tau) + B t + C
+F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
 \end{equation}

### 2016-12-09 ms.tex
I updated the dynamic spectra to show the time in hours and also to adjust the ranges and plot labels to see what's doing on with the raw spectra.
I adjusted the time series for 0835 and 1821 so the plot symbols are smaller and the time is expressed in hours.

@@
 Bottom Panels: Dynamic spectra of each brown dwarf system.
-[MORE DESCRIPTION] {\bf [y-axis in hours not days, change top normalization or y-range so full spectrum is visible, and remove labels]}}
+[MORE DESCRIPTION]}
 	\label{fig:specphot}
@@
 	}
-	\caption{Time series for each system with an offset added for clarity.
-Each wavelength bin is labeled on the right side.
-Alternating colors are used to distinguished the light curves with offsets.
-{\bf [increased vertical scale so fluctuations are visible; replace diamonds with vertical bars (unc) or smaller symbols]}}
+	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
 	\label{fig:tserPfold}

### 2016-12-11 ms.tex
I deleted an empty figure position specifier.
I added an acknowledgement to emcee since I started using it.

@@
 
-\begin{figure*}[!]
+\begin{figure*}
 \centering
@@
 \section{Acknowledgements}
+CHIMERA retrieval makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
 Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.

### 2016-12-14 ms.tex
I added an example corner plot of posterior distributions to the cosine fit.
I forced the appendex to be a page farther back and adjusted the number of significant digits in the corner plot.
I added some plots showing an example with a term cosine fit.

@@
 We extracted separate light curves for each target in 25 spectral bins of width 0.060~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model:
-\begin{equation}
+\begin{equation}\label{eq:cosfit}
 F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
@@
 \appendix
+\clearpage
+\pagebreak
 
@@
 \caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 and 2MASS J0835 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
+\end{centering}
+\end{figure}
+
+\section{Example Posterior Distributions}
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{corner_example.pdf}
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:postCosfit}
+\end{centering}
+\end{figure}
+
+We also explore a 2 term sinusoidal fit:
+
+\begin{equation}\label{eq:cosfit2term}
+F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C
+\end{equation}
+
+The 2 term fit works better on the light curves that show the variations at a high signal to noise ratio
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
+\caption{Best fit model to time series at 1.08~$\mu$m using Equation \ref{eq:cosfit2term}.}\label{fig:model2Cosfit}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{corner_example.pdf}
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
 \end{centering}

### 2016-12-15 ms.tex
I added some more descriptions of the two parameter and one parameter MCMC runs I did.

@@
 \section{Color-Magnitude Diagram}
+
+Figure \ref{fig:CMD} shows the color magnitude diagram from the sample of brown dwarfs in \citet{dupuy2012ltparallax}, which includes 2MASS J0835-0819 but not 2MASS J1812+1414.
+We highlight these two brown dwarfs to be contrasted with the rest of the population.
+
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{color_mag.pdf}
-\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 and 2MASS J0835 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
+\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821-0819 and 2MASS J0835+1414 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
 \end{centering}
@@
 \section{Example Posterior Distributions}
+
+In Figure \ref{fig:postCosfit}, we show the posterior distributions of a sinusoidal model (Equation \ref{eq:cosfit}) fit to the data using \texttt{emcee} \citep{foreman-mackey2013emcee} for an example wavelength bin of 1.08~$\mu$m.
+This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
+We impose priors on the amplitude $A_1$ so that it would be positive, $t_1$ would be less than the observation windows (to avoid multiple periodic solutions) and that the period $\tau$ would be between 0 and the observation window length.
+The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.
+
 \begin{figure}
@@
 
-We also explore a 2 term sinusoidal fit:
-
+We also explore a 2 term sinusoidal fit with a second cosine function at twice the frequency:
 \begin{equation}\label{eq:cosfit2term}
@@
 \end{equation}
+Now there are two amplitude parameters $A_1$ and $A_2$ and two time offset parameters $t_1$ and $t_2$.
+Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for this 2 term sinusoidal fit.
+We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
+The two term model appears visually to fit the data well.
+The $\chi^2$ per degree of freedom is still 7.9, so it is not the expected 1.0.
+However, the error bars are likely underestimated when using photon and read noise limits.
 
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_example.pdf}
+\includegraphics[width=0.5\textwidth]{corner_fit_2term.pdf}
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}

### 2016-12-18 ms.tex
I added an equation for the re-parameterized two temperature model.
I put in a plot with the MCMC posteriors for a 2 temperature model.

@@
 
+In the model fitting, we found a strong correlation between $\alpha_1$ and $\alpha_2$.
+There-fore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
+\begin{equation}\label{eq:2tempAdiff}
+A_\lambda = \frac{\beta \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(2 \alpha_1 - \beta \right) B_\lambda(T_1) + \left(2 - 2 \alpha_1 + \beta \right) B_\lambda(T_2)}.
+\end{equation}
+
 We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
@@
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{corner_fit_2temp.pdf}
+\caption{Example posterior distributions for an MCMC fit to the spectra using Equation \ref{eq:2tempAdiff}.}\label{fig:post2Tempfit}
 \end{centering}

### 2016-12-19 ms.tex
I added a best-fit model fit plot to the spectrum. Also, for the 2 term fit to the time series, I show a comparison between using 1 cosine term and 2 cosine terms.

@@
 
+\pagebreak
 \section{Example Posterior Distributions}
 
+\subsection{Time Series}
 In Figure \ref{fig:postCosfit}, we show the posterior distributions of a sinusoidal model (Equation \ref{eq:cosfit}) fit to the data using \texttt{emcee} \citep{foreman-mackey2013emcee} for an example wavelength bin of 1.08~$\mu$m.
@@
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
+\end{centering}
+\end{figure}
+
+\clearpage
+\pagebreak
+\subsection{Amplitude Spectrum}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
+\caption{Maximum likelihood spectrum using an MCMC fit to the amplitude spectrum of 2MASS 1821.}\label{fig:ML2Tempfit}
 \end{centering}

### 2016-12-24 ms.tex
I updated the descriptions of the figures in the appendix.

@@
 The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly larger than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
-Therefore, we suspect that hot or cold spots on the surface are a less plausible explanation of the variability of 2MASS 1821 than a heterogenous temperature distribution.
+Therefore, we suspect that hot or cold spots on the surface are a less plausible explanation of the variability of 2MASS J1821 than a heterogenous temperature distribution.
 
@@
 
-Figure \ref{fig:CMD} shows the color magnitude diagram from the sample of brown dwarfs in \citet{dupuy2012ltparallax}, which includes 2MASS J0835-0819 but not 2MASS J1812+1414.
+Figure \ref{fig:CMD} shows the color magnitude diagram from the sample of brown dwarfs in \citet{dupuy2012ltparallax}, which includes 2MASS J0835 but not 2MASS J1821.
 We highlight these two brown dwarfs to be contrasted with the rest of the population.
@@
 \includegraphics[width=0.5\textwidth]{color_mag.pdf}
-\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821-0819 and 2MASS J0835+1414 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
+\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J0835 and 2MASS J1821 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
 \end{centering}
@@
 
-We also explore a 2 term sinusoidal fit with a second cosine function at twice the frequency:
+Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also fit a two term cosine model.
+In the two term model, we add a second cosine function at twice the frequency:
 \begin{equation}\label{eq:cosfit2term}
-F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C
+F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C.
 \end{equation}
@@
 
-The 2 term fit works better on the light curves that show the variations at a high signal to noise ratio
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
-\caption{Best fit model to time series at 1.08~$\mu$m using Equation \ref{eq:cosfit2term}.}\label{fig:model2Cosfit}
+\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m.
+Error bars are shown for photon and read noise.
+We show two best-fit models using a single cosine term (green) and a 2 cosine term fit (red) which is a better match to the data.}\label{fig:model2Cosfit}
 \end{centering}
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_fit_2term.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:post2Cosfit}
+\includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term} }\label{fig:post2Cosfit}
 \end{centering}
@@
 
+We also use \texttt{emcee} to fit the amplitude spectrum of 2MASS J1821 using the two temperature surface model
+
 \begin{figure}
@@
 \includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
-\caption{Maximum likelihood spectrum using an MCMC fit to the amplitude spectrum of 2MASS 1821.}\label{fig:ML2Tempfit}
+\caption{Maximum likelihood spectrum using an MCMC fit to the amplitude spectrum of 2MASS J1821.}\label{fig:ML2Tempfit}
 \end{centering}

### 2016-12-26 ms.tex
I added a few tiny notes on the best fits

@@
 This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
-We impose priors on the amplitude $A_1$ so that it would be positive, $t_1$ would be less than the observation windows (to avoid multiple periodic solutions) and that the period $\tau$ would be between 0 and the observation window length.
+We impose priors on the amplitude $A_1 > 0$, $|t_t| < 6 hr$ (to avoid multiple periodic solutions) and that the period $0 < \tau < 6 hr$ so that the periodicity is shorter than the observation window length.
 The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.
+The maximum likelihood solution is shown in Figure \ref{fig:model2Cosfit} and has a $\chi^2$ per degree of freedom of 12.1
 

### 2016-12-28 ms.tex
I added a few notes on the parameters' units for the posteriors of the sinusoidal fit.

@@
 This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
+In this example, we input photon noise only.
 We impose priors on the amplitude $A_1 > 0$, $|t_t| < 6 hr$ (to avoid multiple periodic solutions) and that the period $0 < \tau < 6 hr$ so that the periodicity is shorter than the observation window length.
@@
 \includegraphics[width=0.5\textwidth]{corner_example.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.}\label{fig:postCosfit}
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.
+Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of percent per hour and C is the offset constant in fraction (not percent).
+}\label{fig:postCosfit}
 \end{centering}

### 2017-01-02 ms.tex
I added a residual time series for the two term time series and do a comparison to the photon noise.
I added more description to the text and captions of the appendix.

@@
 
-\subsection{Spot Model Fit}
+\subsection{Spot Model Fit}\label{sec:spotModel}
 
@@
 Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
-\begin{equation}
+\begin{equation}\label{eq:twoTempAmpAlphas}
 A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
@@
 There-fore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
-\begin{equation}\label{eq:2tempAdiff}
+\begin{equation}\label{eq:twoTempAmp}
 A_\lambda = \frac{\beta \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(2 \alpha_1 - \beta \right) B_\lambda(T_1) + \left(2 - 2 \alpha_1 + \beta \right) B_\lambda(T_2)}.
@@
 \includegraphics[width=0.5\textwidth]{color_mag.pdf}
-\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J0835 and 2MASS J1821 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
+\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
 \end{centering}
@@
 The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.
-The maximum likelihood solution is shown in Figure \ref{fig:model2Cosfit} and has a $\chi^2$ per degree of freedom of 12.1
+The maximum likelihood solution is shown in Figure \ref{fig:model2Cosfit} and has a chi-squared per degree of freedom ($\bar{\chi^2}$) of 12.1
 
@@
 Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of percent per hour and C is the offset constant in fraction (not percent).
+We only input photon counting and read noise statistics for the errors.
+This is likely and underestimate for the uncertainty in the time series.
 }\label{fig:postCosfit}
@@
 The two term model appears visually to fit the data well.
-The $\chi^2$ per degree of freedom is still 7.9, so it is not the expected 1.0.
-However, the error bars are likely underestimated when using photon and read noise limits.
+The $\bar{\chi^2}$ is still 7.9, so it is not the expected 1.0.
+However, the error bars are underestimated when only including photon and read noise components.
+With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors.
+With the brown dwarf rotation light curves, there is not flat baseline over which to measure error levels.
 
@@
 Error bars are shown for photon and read noise.
-We show two best-fit models using a single cosine term (green) and a 2 cosine term fit (red) which is a better match to the data.}\label{fig:model2Cosfit}
+We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$) which is a better match to the data.}\label{fig:model2Cosfit}
 \end{centering}
@@
 \includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term} }\label{fig:post2Cosfit}
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term}.
+Again, there is little correlation between the posteriors for the different parameters.
+The offset parameter for second time offset $t_1$, has multiple solutions at a period of 1.95 hours.}\label{fig:post2Cosfit}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{residual_ML.pdf}
+\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfit2term} from the data.
+The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
 \end{centering}
@@
 
-We also use \texttt{emcee} to fit the amplitude spectrum of 2MASS J1821 using the two temperature surface model
+We also use \texttt{emcee} to fit the amplitude spectrum of 2MASS J1821 using the two temperature surface model in Section \label{sec:spotModel} with Equation \ref{eq:twoTempAmp}.
 
@@
 \includegraphics[width=0.5\textwidth]{corner_fit_2temp.pdf}
-\caption{Example posterior distributions for an MCMC fit to the spectra using Equation \ref{eq:2tempAdiff}.}\label{fig:post2Tempfit}
+\caption{Example posterior distributions for an MCMC fit to the spectra using Equation \ref{eq:twoTempAmp}.}\label{fig:post2Tempfit}
 \end{centering}

### 2017-01-04 ms.tex
I replaced the PDF files of the time series wiht PNGs since the file sizes were way too big.

@@
 \subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
+	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.png}
 	\label{fig:tserPhase0835}
@@
 \subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
+	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.png}
 	\label{fig:tserPhase1821}
@@
 Error bars are shown for photon and read noise.
-We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$) which is a better match to the data.}\label{fig:model2Cosfit}
+We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$ =7.9) which is a better match to the data.}\label{fig:model2Cosfit}
 \end{centering}

### 2017-01-06 ms.tex
I added a plot to show the histogram of residuals.
I added a new plot for the two term posterior distribution. This time I restricted the priors so that we didn't unnecessarily fit multiple periodic solutions.

@@
 We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
+For the time offsets, we 
 The two term model appears visually to fit the data well.
@@
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term}.
-Again, there is little correlation between the posteriors for the different parameters.
-The offset parameter for second time offset $t_1$, has multiple solutions at a period of 1.95 hours.}\label{fig:post2Cosfit}
+Again, there is little correlation between the posteriors for the different parameters.}\label{fig:post2Cosfit}
 \end{centering}
@@
 The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
+\end{centering}
+\end{figure}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{histo_resids.pdf}
+\caption{Histogram of residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfit2term} from the data.}\label{fig:histoResid2Cosfit}
 \end{centering}

### 2017-01-06 ms.tex
I now show a best-fit light curve at 1.08um with 1, 2, and 3 cosine terms and chi-squared values.

@@
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.
-Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of percent per hour and C is the offset constant in fraction (not percent).
+Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of fraction of flux per hour and C is the offset constant in fraction (not percent).
 We only input photon counting and read noise statistics for the errors.
@@
 
-Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also fit a two term cosine model.
-In the two term model, we add a second cosine function at twice the frequency:
-\begin{equation}\label{eq:cosfit2term}
-F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C.
+Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also explore models with additional sinusoidal frequencies.
+In the multiple term model, we add cosine functions at $n$ times the frequency:
+\begin{equation}\label{eq:cosfitMultiTerm}
+F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/(\tau)) +  ...
 \end{equation}
-Now there are two amplitude parameters $A_1$ and $A_2$ and two time offset parameters $t_1$ and $t_2$.
-Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for this 2 term sinusoidal fit.
-We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
-For the time offsets, we 
-The two term model appears visually to fit the data well.
-The $\bar{\chi^2}$ is still 7.9, so it is not the expected 1.0.
+Now there are $n$ amplitude parameters $A_n$ and $n$ time offset parameters $t_n$.
+Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for 2 term and 3 term sinusoidal fits.
+We assume the same priors as the 1 term sinusoidal fit with  $A_n > 0$.
+For the time offsets, we restrict the range to be $\pm$ 4 hr / $n$.
+The multiple term model appear visually to fit the data well.
+However, the $\bar{\chi^2}$ are still 7.9 and 7.4, so it is not the expected 1.0.
 However, the error bars are underestimated when only including photon and read noise components.
 With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors.
-With the brown dwarf rotation light curves, there is not flat baseline over which to measure error levels.
+With the brown dwarf rotation light curves, there is no flat baseline over which to measure error levels.
 
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
+\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
 \caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m.
 Error bars are shown for photon and read noise.
-We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$ =7.9) which is a better match to the data.}\label{fig:model2Cosfit}
+We a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1).
+Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
 \end{centering}
@@
 \includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term}.
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfitMultiTerm} for 2 terms.
 Again, there is little correlation between the posteriors for the different parameters.}\label{fig:post2Cosfit}
@@
 \includegraphics[width=0.5\textwidth]{residual_ML.pdf}
-\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfit2term} from the data.
+\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data.
 The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
@@
 \includegraphics[width=0.5\textwidth]{histo_resids.pdf}
-\caption{Histogram of residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfit2term} from the data.}\label{fig:histoResid2Cosfit}
+\caption{Histogram of residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data with 2 terms.}\label{fig:histoResid2Cosfit}
 \end{centering}

### 2017-01-06 ms.tex
I added another plot for the residuals using the 3 term model.

@@
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfitMultiTerm} for 2 terms.
-Again, there is little correlation between the posteriors for the different parameters.}\label{fig:post2Cosfit}
+Again, there is little correlation between the posteriors for the different parameters. {\it Right} Same figure, but with 3 cosine terms.}\label{fig:post2Cosfit}
 \end{centering}
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{residual_ML.pdf}
-\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data.
+\includegraphics[width=0.48\textwidth]{residual_2term_1080nm.pdf}
+\includegraphics[width=0.48\textwidth]{residual_3term_1080nm.pdf}
+\caption{{\it Left:} Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data.
 The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}

### 2017-01-10 ms.tex
I fixed up some text and descriptions in the appendices.

@@
 \begin{equation}\label{eq:cosfitMultiTerm}
-F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/(\tau)) +  ...
+F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/\tau) +  ...
 \end{equation}
@@
 Error bars are shown for photon and read noise.
-We a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1).
+We plot a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1).
 Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
@@
 \includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
-\caption{Maximum likelihood spectrum using an MCMC fit to the amplitude spectrum of 2MASS J1821.}\label{fig:ML2Tempfit}
+\caption{We repeat the amplitude spectrum of 2MASS J1821 from Figure \ref{fig:ampspec1821tdiff}, which excludes the wavelengths contaminated by telluric absorption.
+We show a maximum likelihood model spectrum, which has a $\chi^2$ per degree of freedom of 1.16.}\label{fig:ML2Tempfit}
 \end{centering}

### 2017-01-10 ms_v161019_ajb.tex

--- 2017-01-06 ms.tex
@@
 
-\title{Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS J08354256-0819237 and 2MASS J18212815+1414010}
+\title{Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010}
 
@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits low-level ($\lesssim$ 0.4\% per band) variability with no spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m and declines toward longer wavelengths.
-The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414 over 1.1--1.6~$\mu$m.
-We reproduce the variability amplitude spectrum of 2MASS~J1821+1414 with Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths.
-An alternate model based on surface hot spots more accurately reproduces the variability amplitude spectrum, but requires implausibly large temperature variations.
-{\bf [phase variation?
-differences between 0835 and 1821?]}
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m, the variability amplitude declining toward longer wavelengths.
+{\bf [PHASE VARIATION]}.
+The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths.
+An alternate model based on surface hot spots requires implausibly large temperature variations.
+The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
 \end{abstract}
@@
 whose surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
-Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have photospheric heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
+Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
 Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
 
-Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
-The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been show to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
+Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
+The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
 Wavelength-dependent phase variance in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
@@
 Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
-Some ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) have been limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
-In contrast, the stability of space-based platforms $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
-However, these facilities are not suited, for building up robust statistical samples to assess the physical bases of surface heterogeneity or different variability modes.
+Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
+In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
+However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity, or evolution in variability modes.
 
-Multi-Object Spectroscopy (MOS) which uses references stars to correct for telluric effects with a multi-object spectrograph or long slit \citep[e.g.][]{bean10,bean2013,gibson13clouds,stevenson2016hatp26} has significantly improved the precision of ground-based spectro-photometry.
+Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects  (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}) can significantly improve the precision of ground-based spectro-photometry.
 \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
@@
 In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion.
-These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground and with IRTF from 1-2.5~$\mu$m.
+These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
 
 This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions.
-We describe the target identification strategy and pilot targets in Section~\ref{sec:targets}.
+We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
 In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
@@
 
-\section{Target Selection}\label{sec:targets}
+\section{Target Selection and Characterization}\label{sec:targets}
 
@@
 Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been observed to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
-Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming radius R = 1~{\rjup}.
-There is an $H$ = 12.3 star (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
+Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
+There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
 2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}.
@@
 \startdata
-{\sha} & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
-{\shb} & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
+2MASS~J08354256$-$0819237 & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
+2MASS~J18212815+14140101 & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
 \enddata
@@
 
+To characterize the atmospheric regions probed by our observations, we computed the brightness temperature spectra of our sources using previously obtained IRFT/SpeX data \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
+The brightness temperature:
+\begin{equation}
+T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{I_{\lambda,surf}\lambda^5}\right)\right]^{-1}
+\end{equation}
+can be inferred from the surface flux density
+\begin{equation}
+I_{\lambda,surf} = {\pi}B_{\lambda} = I_{\lambda,obs}\left(\frac{d}{R}\right)^2 = I_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
+\end{equation}
+where $I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.
+For both sources, we first normalized the observed spectrum to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}, then adopted radii from the evolutionary models of \citet{2001RvMP...73..719B} assuming effective temperatures ({\teff}s) computed by \citet{2015ApJ...810..158F} based on bolometric luminosity measurements.
+Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\teff} and radius were propagated by Monte Carlo simulation.
+\citet{2016ApJ...833...96L} have recently reported {\sha} to be both overluminous and exhibiting signatures of moderately low surface gravity; we therefore considered two cases for this source: an age of 200--500~Myr uniformly sampled, for which the evolutionary models predict radii of 0.115~R$_{\odot}$ to 0.101~R$_{\odot}$; and an equal-mass binary with the same age range ($I_{\lambda,int}$ = $\frac{1}{2}I_{\lambda,obs}$).
+For {\shb}, we assumed a uniform age range of 1--5~Gyr, for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.082~R$_{\odot}$.
+Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.
+The spectral peaks for {\shb} span 1950--2100~K, slightly warmer at short wavelengths.
+For {\sha}, the young single model predicts a peak brightness temperature that increases with wavelength, reaching 2450~K at $K$-band.
+Assuming this source is a binary brings the brightness temperature spectrum into qualitative (roughly flat) and quantitative (2100--2250~K) agreement with {\shb}.
+{\bf [I'M WORRIED I HAVE A FACTOR OF 2 ERROR HERE]}.
+
+\begin{figure*}
+\centering
+	\plottwo{tbright0835.pdf}{tbright1821.pdf}
+	\caption{Calculated brightness temperature of {\sha} (left) and {\shb} (right) as a function of wavelength.
+The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations.
+For {\sha}, we calculate separately for young single (black) and binary (blue) models, the latter scaling the observed absolute fluxes by a factor of two.
+}
+	\label{fig:tbright}
+	\vspace{0.1in}
+\end{figure*}
+
 \section{Observations}\label{sec:obs}
@@
 Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
-The short-wavelength limit was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
-For {\sha} our exposures were 15~sec, which was sufficient for guiding but not precision photometry.
+Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis.
+This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction.
+The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
+Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively.
+The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
+For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
 For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
 
-\begin{deluxetable*}{lcccccccll}
+\begin{deluxetable*}{lccccccccc}
 \tablecaption{Observations}\label{tab:obsParam}
@@
 \colhead{Reference Star} & 
-\colhead{FWHM} \\
+\colhead{FWHM \@ $H$} \\
  & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
@@
 
-Wavelength calibrations were performed using observations of ThAr  emission lamps with the 0.3$\times$60$\arcsec$.
-We also obtained calibration sequences of ThAr and flat-field lamps with the 3$\times$60$\arcsec$ slit  before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
+Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
+We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
+% to measure pixel response and assess flexure in the instrument with telescope orientation.
+For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response.
+To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure spatial shifts {\bf [WHAT ORDER OF SHIFT DID YOU FIND]}.
+These shifts were used to apply a custom flat field for every image.
+For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis. {\bf [IS THIS TRUE FOR 1821?]}
 
-[ADAM STOPPED HERE]
+As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fitto points more than 30 pixels away from the center of the source dispersion traces.
+Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials {\bf [REALLY?
+NOT A MEDIAN PROFILE?
+OR A MODIFIED GAUSSIAN?
+LOW ORDER POLY WOULDN'T CAPTURE PSF SHAPE I THINK]} with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
+These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 
+Typical signals-to-noise of the extracted spectra were {\bf [WHAT?]}. 
+Relative spectra (source/reference) were then computed for each exposure.
+{\bf [DID YOU HAVE TO TAKE INTO ACCOUNT RELATIVE WAVELENGTH SHIFTS BETWEEN SOURCE AND REFERENCE STAR?
+I DON'T THINK DISPERSION IS STRICTLY ALIGNED WITH PIXEL AXES AND MAY HAVE SOME CURVATURE]}.
 
-For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
-Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
-All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
-We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.
+{\bf [MORIS REDUCTION FOR 1821?]}
 
-For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
-Here, we fit the flat field structure with low order polynomials in the incandescent flat field to describe the spatial structure and use the residual image as a pixel-to-pixel flat.
-As in 2MASS J0835, we cross-correlate the spatial structure image to find a shift and then multiply it by the pixel-to-pixel flat to create a custom flat field for every image.
-In both 2MASS J0835 and 2MASS J1821 we remove all spectral structure from the flat fields to make ``response'' images that do not include the spectral structure of the lamp or dramatically alter the flux levels that would affect SNR calculations from the number of photo-electrons in a given pixel.
-
-As in \citet{2016ApJ...826..156S}, we perform background subtraction over the entire slit with polynomial fit.
-We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
-We use optimal extraction \citep{horne1986optimalE} to maximize the signal to noise.
-The spatial profiles are fit with low order polynomials with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
-These spatial profiles are then used to calculate a weighted sum spectrum.
+\section{Analysis}
 
@@
 
-Figure \ref{fig:specphot} shows the dynamic spectra of both targets, as well as the median spectra of the target and reference stars.
-{\sha} shows no variations or systematics at the $\lesssim1$\% level, while {\shb} shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
-The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than arising from systematic effects (see \citealt{2016ApJ...826..156S}).
-{\shb} does exhibits some systematic features near the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by slight wavelength drifts and lower signals-to-noise.
+Figure \ref{fig:specphot} shows the dynamic spectra (relative source brightness as a function of wavelength and time) for both targets, as well as the median spectra of the target and reference stars.
+{\sha} shows a relative flat response with shows no obvious variations at the $\lesssim1$\% level.
+{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
+The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
+Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.
+
+{\bf [MORIS ANALYSIS FOR 1821?]}
 
@@
 \subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.png}
+	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.pdf}
 	\label{fig:tserPhase0835}
@@
 \subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.png}
+	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.pdf}
 	\label{fig:tserPhase1821}
@@
 
-\section{Sinusoidal Model Fits}\label{sec:ModelFits}
+Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
+The uncertainties in these curves are {\bf [WHAT?
+HOW DETERMINED?]}.
+Again, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.
+These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr.
+In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
+As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
+{\bf [WE SHOULD VERIFY THIS]}
 
-We extracted separate light curves for each target in 25 spectral bins of width 0.060~$\mu$m, as shown in Figure~\ref{fig:tserPfold}. Each of these were fit to a simple sinusoidal model:
+Each of the light curves were fit to a simple sinusoidal model:
 \begin{equation}\label{eq:cosfit}
@@
 \end{equation}
-Here, $F(t)$ is the flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
-For the fits, we let $A$, $t_0$, $B$ and $C$ be free parameters, but fixed $\tau$ at the literature value of rotation period due to systematic trends (with a period of $\sim$24 hr) caused by uncorrected telluric variations.
+where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
+For our initial fits, we allowed $A$, $t_0$, $B$ and $C$ to be free parameters, but fixed $\tau$ at the literature value of rotation period to mitigate systematic biases (e.g., convergence on a period of $\sim$24 hr).
+{\bf [IS THIS A PROBLEM IF YOU IGNORE TELLURIC BANDS?
+COULD YOU CONSTRAIN THE ALLOWED PERIOD RANGE (I.E., PRIOR).
+SHOULD DO A FIT WITH PERIOD FREE TO VARY TO GET A MEASURE OF THIS QUANTITY]}
 We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.
+{\bf [THIS IS LIKELY LEADING TO OUR "DETECTION" OF 0835; NEED ANOTHER WAY TO DO THIS]}.
+We use the standard deviation of points near minimum to estimate the noise in the flux time series.
+The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
 
@@
 
-Figure \ref{fig:ampSpec} shows the best fit amplitudes as a function of wavelength.
-We use the standard deviation of points near minimum to estimate the noise in the flux time series.
-The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
-The amplitude spectrum ($A$ as a function of wavelength) of 2MASS J0835, (Figure \ref{fig:ampspec0835}), shows small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
+STOPPED HERE
+
+Figure \ref{fig:ampSpec} shows the best fit periodic amplitudes as a function of wavelength.
+For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
 2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
@@
 \caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.
-Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of fraction of flux per hour and C is the offset constant in fraction (not percent).
+Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of percent per hour and C is the offset constant in fraction (not percent).
 We only input photon counting and read noise statistics for the errors.
@@
 
-Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also explore models with additional sinusoidal frequencies.
-In the multiple term model, we add cosine functions at $n$ times the frequency:
-\begin{equation}\label{eq:cosfitMultiTerm}
-F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/(\tau)) +  ...
+Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also fit a two term cosine model.
+In the two term model, we add a second cosine function at twice the frequency:
+\begin{equation}\label{eq:cosfit2term}
+F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) +  B t + C.
 \end{equation}
-Now there are $n$ amplitude parameters $A_n$ and $n$ time offset parameters $t_n$.
-Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for 2 term and 3 term sinusoidal fits.
-We assume the same priors as the 1 term sinusoidal fit with  $A_n > 0$.
-For the time offsets, we restrict the range to be $\pm$ 4 hr / $n$.
-The multiple term model appear visually to fit the data well.
-However, the $\bar{\chi^2}$ are still 7.9 and 7.4, so it is not the expected 1.0.
+Now there are two amplitude parameters $A_1$ and $A_2$ and two time offset parameters $t_1$ and $t_2$.
+Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for this 2 term sinusoidal fit.
+We assume the same priors as the 1 term sinusoidal fit with both $A_1$ and $A_2 > 0$.
+The two term model appears visually to fit the data well.
+The $\bar{\chi^2}$ is still 7.9, so it is not the expected 1.0.
 However, the error bars are underestimated when only including photon and read noise components.
 With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors.
-With the brown dwarf rotation light curves, there is no flat baseline over which to measure error levels.
+With the brown dwarf rotation light curves, there is not flat baseline over which to measure error levels.
 
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
+\includegraphics[width=0.5\textwidth]{best_fit_2term.pdf}
 \caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m.
 Error bars are shown for photon and read noise.
-We a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1).
-Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
+We show two best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1) and a 2 cosine term fit (red, $\bar{\chi^2}$) which is a better match to the data.}\label{fig:model2Cosfit}
 \end{centering}
@@
 \includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfitMultiTerm} for 2 terms.
-Again, there is little correlation between the posteriors for the different parameters.}\label{fig:post2Cosfit}
+\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit2term}.
+Again, there is little correlation between the posteriors for the different parameters.
+The offset parameter for second time offset $t_1$, has multiple solutions at a period of 1.95 hours.}\label{fig:post2Cosfit}
 \end{centering}
@@
 \includegraphics[width=0.5\textwidth]{residual_ML.pdf}
-\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data.
+\caption{Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfit2term} from the data.
 The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{histo_resids.pdf}
-\caption{Histogram of residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data with 2 terms.}\label{fig:histoResid2Cosfit}
 \end{centering}

### 2017-01-11 ms.tex
I merged all of Adam's edits into the main ms.tex file.

@@
 Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been observed to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
-Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming radius R = 1~{\rjup}.
-There is an $H$ = 12.3 star (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
+Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
+There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
 2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}.
@@
 
-Wavelength calibrations were performed using observations of ThAr  emission lamps with the 0.3$\times$60$\arcsec$.
-We also obtained calibration sequences of ThAr and flat-field lamps with the 3$\times$60$\arcsec$ slit  before and after the brown dwarf time series to obtain information on the flat field and any flexure in the instrument with telescope orientation.
+Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
+We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
+% to measure pixel response and assess flexure in the instrument with telescope orientation.
+For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response.
+To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure spatial shifts {\bf [WHAT ORDER OF SHIFT DID YOU FIND]}.
+These shifts were used to apply a custom flat field for every image.
+For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis. {\bf [IS THIS TRUE FOR 1821?]}
 
-[ADAM STOPPED HERE]
+As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit to points more than 30 pixels away from the center of the source dispersion traces.
+Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials {\bf [REALLY?
+NOT A MEDIAN PROFILE?
+OR A MODIFIED GAUSSIAN?
+LOW ORDER POLY WOULDN'T CAPTURE PSF SHAPE I THINK]} with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
+These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 
+Typical signals-to-noise of the extracted spectra were {\bf [WHAT?]}. 
+Relative spectra (source/reference) were then computed for each exposure.
+{\bf [DID YOU HAVE TO TAKE INTO ACCOUNT RELATIVE WAVELENGTH SHIFTS BETWEEN SOURCE AND REFERENCE STAR?
+I DON'T THINK DISPERSION IS STRICTLY ALIGNED WITH PIXEL AXES AND MAY HAVE SOME CURVATURE]}.
 
-For 2MASS J0835, we use a combination of an incandescent lamp and a sky frame to construct a flat.
-Due to flexure and motion with thin the system, we use a sky frame to get the structure of the background with low order polynomials fits in the horizontal direction.
-All of the (large $\gtrsim$ 30 px) structure is removed from the lamp frame with low order polynomials, and this residual flat is used to correct the pixel-to-pixel variations while the sky frame is used to measure the larger structures.
-We cross-correlate the sky frame with each image to account for any spatial shifts and apply the pixel-to-pixel flat to construct a custom flat field for every image.
+{\bf [MORIS REDUCTION FOR 1821?]}
 
-For 2MASS J1821, we did not have sufficient sky frames for sky flats so we use an incandescent lamp for flat fielding.
-Here, we fit the flat field structure with low order polynomials in the incandescent flat field to describe the spatial structure and use the residual image as a pixel-to-pixel flat.
-As in 2MASS J0835, we cross-correlate the spatial structure image to find a shift and then multiply it by the pixel-to-pixel flat to create a custom flat field for every image.
-In both 2MASS J0835 and 2MASS J1821 we remove all spectral structure from the flat fields to make ``response'' images that do not include the spectral structure of the lamp or dramatically alter the flux levels that would affect SNR calculations from the number of photo-electrons in a given pixel.
-
-As in \citet{2016ApJ...826..156S}, we perform background subtraction over the entire slit with polynomial fit.
-We use a 4th order polynomial through all points outside +/-30 pixels of each aperture for the background subtraction.
-We use optimal extraction \citep{horne1986optimalE} to maximize the signal to noise.
-The spatial profiles are fit with low order polynomials with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
-These spatial profiles are then used to calculate a weighted sum spectrum.
+\section{Analysis}
 

### 2017-01-11 ms.tex
I corrected the reference to the analysis section.

@@
 In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
-In Section~\ref{sec:ModelFits}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
+In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
 We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
@@
 
-\section{Analysis}
+\section{Analysis}\label{sec:analysis}
 

### 2017-01-12 ms.tex
I added a few details from Adam's comments.

@@
 \centering
-	\plottwo{tbright0835.pdf}{tbright1821.pdf}
+	\plottwo{tbright0835.png}{tbright1821.png}
 	\caption{Calculated brightness temperature of {\sha} (left) and {\shb} (right) as a function of wavelength.
@@
 For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response.
-To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure spatial shifts {\bf [WHAT ORDER OF SHIFT DID YOU FIND]}.
+To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
 These shifts were used to apply a custom flat field for every image.
-For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis. {\bf [IS THIS TRUE FOR 1821?]}
+
+For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.
+{\bf [IS THIS TRUE FOR 1821?- \color{red}{YES, there were only 5 good sky frames at the end and 3 at the beginning.}]}
 
 As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit to points more than 30 pixels away from the center of the source dispersion traces.
-Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials {\bf [REALLY?
-NOT A MEDIAN PROFILE?
-OR A MODIFIED GAUSSIAN?
-LOW ORDER POLY WOULDN'T CAPTURE PSF SHAPE I THINK]} with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
+Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials along the spectral direction one row at a time with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
 These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 

### 2017-01-12 ms.tex
I described the wavelength solution methodology in more detail.

@@
 Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
+The images were rectified by shifting each row to match a center row in between the two sources.
+This was achieved by cross correlating the reference row with all other detector rows (which have the same background spectrum) and fitting a smooth function over the sources as in \citealt{2016ApJ...826..156S}.
 We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
@@
 These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 
-Typical signals-to-noise of the extracted spectra were {\bf [WHAT?]}. 
+Typical signals-to-noise of the extracted spectra were 40 - 100 per spectral pixel (unbinned).
 Relative spectra (source/reference) were then computed for each exposure.
-{\bf [DID YOU HAVE TO TAKE INTO ACCOUNT RELATIVE WAVELENGTH SHIFTS BETWEEN SOURCE AND REFERENCE STAR?
-I DON'T THINK DISPERSION IS STRICTLY ALIGNED WITH PIXEL AXES AND MAY HAVE SOME CURVATURE]}.
+Our image rectification process described above ensures that the wavelength solution is the same for each row if the image.
+However, there are small additional shifts of the sources within the slit so another cross-correlation is performed between the sources to ensure they match before dividing the two spectra.
 

### 2017-01-15 ms_v170114_ajb.tex
Updates from ShareLaTeX

--- 2017-01-10 ms_v161019_ajb.tex
@@
 Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
+This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
 Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
 There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
-2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}.
+2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
 This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
@@
 
-\begin{deluxetable*}{llcccccccl}
+\begin{deluxetable*}{lllcccccccl}[t]
 \tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
@@
 \tablehead{
+ & \multicolumn{2}{c}{Spectral Type} \\
 \colhead{Name} & 
-\colhead{SpT} & 
+\colhead{Opt} & 
+\colhead{NIR} & 
 \colhead{$d$} & 
@@
 \colhead{Refs} \\
- &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($degree$)} \\
+ &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
  }
 \startdata
-2MASS~J08354256$-$0819237 & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
-2MASS~J18212815+14140101 & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
+2MASS~J08354256$-$0819237 & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
+2MASS~J18212815+14140101 & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
 \enddata
@@
 \tablenotetext{b}{Tentative period.}
+\tablenotetext{c}{Estimated from the \citet{2015ApJ...810..158F} {\teff}/spectral type relation.}
 \tablerefs{(1) \citet{2003AJ....126.2421C};
@@
 
-To characterize the atmospheric regions probed by our observations, we computed the brightness temperature spectra of our sources using previously obtained IRFT/SpeX data \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
-The brightness temperature:
+To characterize the atmospheric regions probed by our observations, we analyzed previously 
+obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
+Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicate near-infrared
+classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}).
+The former is considerably later than the L5 optical classification previously reported by \citet{2003AJ....126.2421C}.
+We confirm the intermediate low surface gravity classification (INT-G) reported by \citet{2016ApJ...833...96L} based on the indices of \citet{2013ApJ...772...79A} using an L7 classification.
+The discrepancy between the optical and near-infrared classifications of this source is likely related to surface gravity effects.
+{\shb}, on the other hand, is a good match to the L5 spectral standard and has a field dwarf gravity classification.
+
+We computed brightness temperature spectra from these data as
 \begin{equation}
@@
 \end{equation}
-can be inferred from the surface flux density
+where the surface flux density $I_{\lambda,surf}$ is computed as
 \begin{equation}
@@
 \end{equation}
-where $I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.
-For both sources, we first normalized the observed spectrum to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}, then adopted radii from the evolutionary models of \citet{2001RvMP...73..719B} assuming effective temperatures ({\teff}s) computed by \citet{2015ApJ...810..158F} based on bolometric luminosity measurements.
+$I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.
+Both spectra were normalized to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}.
+We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming effective temperatures ({\teff}s) from \citet{2015ApJ...810..158F} based on these sources' bolometric luminosity measurements (Table~\ref{tab:bdProp}).
 Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\teff} and radius were propagated by Monte Carlo simulation.
-\citet{2016ApJ...833...96L} have recently reported {\sha} to be both overluminous and exhibiting signatures of moderately low surface gravity; we therefore considered two cases for this source: an age of 200--500~Myr uniformly sampled, for which the evolutionary models predict radii of 0.115~R$_{\odot}$ to 0.101~R$_{\odot}$; and an equal-mass binary with the same age range ($I_{\lambda,int}$ = $\frac{1}{2}I_{\lambda,obs}$).
-For {\shb}, we assumed a uniform age range of 1--5~Gyr, for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.082~R$_{\odot}$.
+For {\sha} we considered two cases: radii corresponding to an age of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}, for which the evolutionary models predict radii of 0.147~R$_{\odot}$ to 0.115~R$_{\odot}$; and an age range of 1--5~Gyr for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.084~R$_{\odot}$.
+For {\shb}, we assumed a lower age limit of 200~Myr based on its FLD-G classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S} range of 1--5~Gyr; evolutionary models predict radii of 0.120~R$_{\odot}$ to 0.097~R$_{\odot}$ for these ages.
+
 Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.
-The spectral peaks for {\shb} span 1950--2100~K, slightly warmer at short wavelengths.
-For {\sha}, the young single model predicts a peak brightness temperature that increases with wavelength, reaching 2450~K at $K$-band.
-Assuming this source is a binary brings the brightness temperature spectrum into qualitative (roughly flat) and quantitative (2100--2250~K) agreement with {\shb}.
-{\bf [I'M WORRIED I HAVE A FACTOR OF 2 ERROR HERE]}.
+The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
+Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here.
+For {\shb},
+brightness temperatures range from 1880$\pm$30~K at the $J$-band peak to 1700$\pm$40~K at the $K$-band peak.
+These values are notably warmer than the {\teff} = 1614$\pm$100~K estimated from \citet{2015ApJ...810..158F} {\teff}/spectral type relation, but relatively consistent this source's earlier spectral type as compared to {\sha}.
+We conjecture that the Filippazzo et al.\ relation underestimates the {\teff} of this source due to its unusually dusty spectral energy distribution.
 
@@
 \centering
+	\plottwo{classify0835.pdf}{classify1821.pdf}
 	\plottwo{tbright0835.pdf}{tbright1821.pdf}
-	\caption{Calculated brightness temperature of {\sha} (left) and {\shb} (right) as a function of wavelength.
+	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
+(Bottom) Calculated brightness temperature spectra of {\sha} (left) and {\shb} (right).
 The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations.
-For {\sha}, we calculate separately for young single (black) and binary (blue) models, the latter scaling the observed absolute fluxes by a factor of two.
+For {\sha}, we calculate separate brightness temperatures assuming radii consistent with a low surface gravity (50--200 Myr; blue) and field surface gravity (1--5~Gyr; black).
 }
@@
 The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
-For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
+%For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
 For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
@@
 
-{\bf [MORIS REDUCTION FOR 1821?]}
+%{\bf [MORIS REDUCTION FOR 1821?]}
 

### 2017-01-15 make_tables.py
I removed old unused images and outdated table files.

@@ -1,16 +1,0 @@
-from astropy.io import ascii
-import subprocess
-import pdb
-
-for oneTable in ['bd_table','observing_table']:
-    ## Cleanup CSV file for what MS Excel does
-    subprocess.call(['mac2unix',oneTable+'.csv'])
-    dat = ascii.read(oneTable+'.csv')
-    ascii.write(dat,oneTable+'.tex',
-                Writer=ascii.Latex,latexdict={'tabletype':'table*'})
-    #dat.write(oneTable+'.tex',latexdict={'tabletype':'table*'},Writer=ascii.latex)
-    
-    with open(oneTable+'.tex') as TableTex:
-        allLines = TableTex.readlines()
-        ## Add a horizontal line under headings
-        #pdb.set_trace()

### 2017-01-21 ms.tex
I added a tiny note about 2MASS 1821 MORIS reduction.
Made a table fit inside the page better and added an explanatory sentence to a figure caption.

@@
 
-\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J. Teske\altaffilmark{4}, J. Gizis\altaffilmark{5} \and T. Karalidi\altaffilmark{1}}
+\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J. Gizis\altaffilmark{4}, T. Karalidi\altaffilmark{1}, \and J. Teske\altaffilmark{5}}
 
@@
 \altaffiltext{3}{Center for Astrophysics and Space Science, University of California San Diego, La Jolla, CA 92093, USA}
-\altaffiltext{4}{Carnegie DTM, 5241 Broad Branch Road, NV, Washington, DC 20015, USA}
-\altaffiltext{5}{Department of Physics and Astronomy, University of Delaware, Newark, DE 19716, USA}
+\altaffiltext{4}{Department of Physics and Astronomy, University of Delaware, Newark, DE 19716, USA}
+\altaffiltext{5}{Carnegie Observatories, 813 Santa Barbara Street, Pasadena, CA 91101, USA}
 
@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m, the variability amplitude declining toward longer wavelengths.
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 {\bf [PHASE VARIATION]}.
@@
 Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
+
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
+This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
 Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
 There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
-2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G}.
+2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
 This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
@@
 \colhead{Refs} \\
- &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($degree$)} \\
+ &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
  }
 \startdata
-2MASS~J08354256$-$0819237 & L5 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
-2MASS~J18212815+14140101 & L4.5pec & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1600$\pm$100 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
+\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
+\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
 \enddata
@@
 	\label{fig:image1821}
+	\vspace{-.9in}
 	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right).
@@
 	\label{fig:images}
-	\vspace{0.1in}
+	\vspace{0.17in}
 \end{figure*}
 
-To characterize the atmospheric regions probed by our observations, we computed the brightness temperature spectra of our sources using previously obtained IRFT/SpeX data \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
-The brightness temperature:
+To characterize the atmospheric regions probed by our observations, we analyzed previously 
+obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
+Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicate near-infrared
+classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}).
+The former is considerably later than the L5 optical classification previously reported by \citet{2003AJ....126.2421C}.
+We confirm the intermediate low surface gravity classification (INT-G) reported by \citet{2016ApJ...833...96L} based on the indices of \citet{2013ApJ...772...79A} using an L7 classification.
+The discrepancy between the optical and near-infrared classifications of this source is likely related to surface gravity effects.
+{\shb}, on the other hand, is a good match to the L5 spectral standard and has a field dwarf gravity classification.
+
+We computed brightness temperature spectra from these data as
 \begin{equation}
@@
 \centering
-	\plottwo{tbright0835.png}{tbright1821.png}
-	\caption{Calculated brightness temperature of {\sha} (left) and {\shb} (right) as a function of wavelength.
+	\plottwo{classify0835.pdf}{classify1821.pdf}
+	\plottwo{tbright0835.pdf}{tbright1821.pdf}
+	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
+(Bottom) Calculated brightness temperature spectra of {\sha} (left) and {\shb} (right).
 The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations.
-For {\sha}, we calculate separately for young single (black) and binary (blue) models, the latter scaling the observed absolute fluxes by a factor of two.
+For {\sha}, we calculate separate brightness temperatures assuming radii consistent with a low surface gravity (50--200 Myr; blue) and field surface gravity (1--5~Gyr; black).
 }
@@
 The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
-For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
+
+%For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
 For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
@@
 Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
+
 The images were rectified by shifting each row to match a center row in between the two sources.
@@
 
+For MORIS reduction, we used the raw files and performed aperture photometry with the IDL \texttt{aper} procedure using an aperture size of 6 pixels and a sky annulus of 8-11 pixels.
 {\bf [MORIS REDUCTION FOR 1821?]}
@@
 Bottom Panels: Dynamic spectra of each brown dwarf system.
-[MORE DESCRIPTION]}
+The dynamic spectrum for \sha\ shows no significant variability whereas there is a periodic modulation for \shb\ that decrease toward longer wavelengths.
+[MORE DESCRIPTION -- How should the reader interpret these dynamic spectra?]}
 	\label{fig:specphot}
@@
 Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
-The uncertainties in these curves are {\bf [WHAT?
-HOW DETERMINED?]}.
-Again, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.
+The uncertainties in these curves are 0.2\% in high throughput regions of the spectrum and 0.6\% per exposure.
+The lower values are areas of high throughput and flux whereas the low values are near telluric absorption features or the edges of the spectrum.
+We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
+In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
+We attribute this to correlated errors between wavelengths. {\bf [WHAT? HOW DETERMINED?]}
+
+As seen in Figure~\ref{fig:tserPfold}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.
 These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr.
@@
 \caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption.
-with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
+[SOMETHING HERE?
+like, The data are fit] with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
 Also shown in the figure is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}.
@@
 There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
-The WFC3 spectrum is not affected by the telluric absorption the way the SpeX data is.
-\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and consistent with our Mie scattering fit.
+The WFC3 spectrum is not affected by the telluric absorption, unlike the SpeX data.
+\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our Mie scattering fit.
 
 A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
-In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains, similar to our characteristic particle size.
+In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains [WHY DO WE USE PYROXENE INSTEAD OF FORSTERITE?], similar to our characteristic particle size.
 
@@
 
-Another simple model we attempt is a spot model - that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
+Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
 In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
-This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem} with two opposite longitudes of the planet at the brightness minimum and maximum.
+This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
 We assume that are each in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
@@
 \end{equation}
-where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first ($T_1$ and second ($T_2$) regions respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two levels.
+where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first ($T_1$ and second ($T_2$) regions respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
 $\alpha_1$ and $\alpha_2$ are limited to [0,1].
@@
 In the model fitting, we found a strong correlation between $\alpha_1$ and $\alpha_2$.
-There-fore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
+Therefore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
 \begin{equation}\label{eq:twoTempAmp}
@@
 With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
-The $\alpha$ values,  $\alpha_i <<$ 1 indicating that the model fits with dark patches on a small fraction of the surface.
+The $\alpha$ values are both $<<1$, indicating that the model fits with dark patches on a small fraction of the surface.
+[I MODIFIED THIS SENTENCE; IS IT CORRECT?
+I'm a little confused about how both $\alpha$ values can be $<<1$; if one is small doesn't the other have to be large?]
 
@@
 This research made use of the \texttt{astropy} package \citep{astropy2013}.
+The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.
+We are most fortunate to have the opportunity to conduct observations from this mountain.
 
@@
 \section{Example Posterior Distributions}
-
+[DO WE NEED MORE TEXT IN THIS SECTION EXPLAINING EACH FIGURE?]
 \subsection{Time Series}
@@
 
+\clearpage
+\pagebreak
+\subsection{Manual Shifting}
+
+The trends near 1.4 $\mu$m and 1.8 $\mu$m in \shb\ could probably be reduced by better wavelength shifting.
+I wrote a GUI that let me control the shifts for each spectrum and plot the ratio spectrum.
+I minimized the residuals and ran a test case for \sha.
+As seen in Figure \ref{fig:manualVsAutoShift0835}, the manual shifting dramatically reduces the systematic linear trends in the dynamic spectra.
+In contrast to Figure \ref{fig:specphot}, not linear de-trending has been applied to columns so the systematic linear trends are visible in both cases.
+The automatic shifting finds the peak in the cross correlation.
+It does this by cross-correlating a portion of the spectrum (excluding the endpoints) and zeroed on the wings. 
+The automatic method then fits the cross-correlation pattern with a parabola to find the peak.
+The manual method is where we use keystrokes to shift one spectrum by 0.333 px back in forth until the ratio of another spectrum has the smallest residuals.
+Two iterations were used in the manuals shifting: (1) minimizing the residuals of the target divided by reference and (2) minimizing the residuals of the target divided by the target middle spectrum.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835- Automatic Shifting]{
+	\includegraphics[width=0.5\textwidth]{specphot_0835_auto_noremovel.pdf}
+	\label{fig:specphot0835autoS}
+	}
+\subfloat[2MASS J0835 - Manual shifting ]{
+	\includegraphics[width=0.5\textwidth]{specphot_0835_manual_noremovel.pdf}
+	\label{fig:specphot0835manualS}
+	}
+	\caption{Dynamic spectra of {\sha} using automatic cross correlation wavelength shifting (left) and manual wavelength shifting(right).
+	The manual method shows dramatically better systematics in these dynamic spectra which have no fits along columns to remove trends.}
+	\label{fig:manualVsAutoShift0835}
+	\vspace{0.1in}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J1821- Automatic Shifting]{
+	\includegraphics[width=0.5\textwidth]{specphot_1821_auto_noremovel.pdf}
+	\label{fig:specphot1821autoS}
+	}
+\subfloat[2MASS J1821 - Manual shifting ]{
+	\includegraphics[width=0.5\textwidth]{specphot_1821_manual_noremovel.pdf}
+	\label{fig:specphot1821manualS}
+	}
+	\caption{Dynamic spectra of {\shb} using automatic cross correlation wavelength shifting (left) and manual wavelength shifting(right).
+	The manual method shows better systematics but higher frequency noise.}
+	\label{fig:manualVsAutoShift1821}
+	\vspace{0.1in}
+\end{figure*} 
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-01-22 ms.tex
I added an early MCMC fit to the time series to generate a whole spectrum for 2MASS 0835.

@@
 \end{figure*}
+
+\clearpage
+\pagebreak
+\subsection{MCMC Time Series Fits}
+
+Fitting all light curves to \sha\ with MCMC methods and without the A$_1$ > 0 prior results in more non-detections, but an unusual pattern to the spectra.
+As with other MCMC fits, error bars are from photon and read noise, so they're likely under-estimated.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_0835.pdf}
+\caption{Spectrum of \sha\ using all MCMC fits with 1 cosine term .}\label{fig:mcmcSpec0835}
+\end{centering}
+\end{figure}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-01-24 ms.tex
I added an MCMC fit to 2MASS 1821 in addition to the one yesterday for 2MASS 0835.
I plotted the results of an experiment where I scaled all the error bars up by a factor of 4X.

@@
 
-\begin{figure}
-\begin{centering}
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835 - Manual Shifting]{
 	\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_0835.pdf}
-\caption{Spectrum of \sha\ using all MCMC fits with 1 cosine term .}\label{fig:mcmcSpec0835}
-\end{centering}
-\end{figure}
+	\label{fig:ampSpec0835ManualS}
+	}
+\subfloat[2MASS J1821 - Manual shifting ]{
+	\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_1821.pdf}
+	\label{fig:ampSpec1821ManualS}
+	}
+	\caption{Amplitude spectrum of {\sha} (left)  and {\shb} (right) using manual wavelength shifting, 1 cosine term fit and MCMC fitting with error bars from photon and read noise.}
+	\label{fig:ampSpecManualS}
+	\vspace{0.1in}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835 - 4$\times \sigma$]{
+	\includegraphics[width=0.5\textwidth]{mcmc_2mass_0835_spectrum_0400perc_err.pdf}
+	\label{fig:ampSpec0835fourTimesErr}
+	}
+\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
+	\includegraphics[width=0.5\textwidth]{mcmc_2mass_1821_spectrum_0400perc_err.pdf}
+	\label{fig:ampSpec1821fourTimesErr}
+	}
+	\caption{As an experiment, I remade the amplitude spectra of Figure \ref{fig:ampSpecManualS} but scaled all error bars up by a factor of 4 for all points to account for some systematic errors.
+IE, Amplitude spectrum of {\sha} (left)  and {\shb} (right) using manual wavelength shifting, 1 cosine term fit and MCMC fitting with error bars from 4$\times$ photon and read noise.}
+	\label{fig:ampSpecManualSfourTimesErr}
+	\vspace{0.1in}
+\end{figure*}
 

### 2017-01-25 ms.tex
I put in a section describing the amplitude spectra I get if I put in a gith prior on the rotation period.

@@
 \pagebreak
-\subsection{MCMC Time Series Fits}
+\subsection{MCMC Time Series Fits - first try}
 
-Fitting all light curves to \sha\ with MCMC methods and without the A$_1$ > 0 prior results in more non-detections, but an unusual pattern to the spectra.
+Fitting all light curves to \sha\ with MCMC methods and without the A$_1 >$ 0 prior results in more non-detections, but an unusual pattern to the spectra.
 As with other MCMC fits, error bars are from photon and read noise, so they're likely under-estimated.
@@
 	\label{fig:ampSpecManualSfourTimesErr}
+	\vspace{0.1in}
+\end{figure*}
+
+\clearpage
+\pagebreak
+\subsection{MCMC Time Series Fits - second try}
+
+As with my \texttt{IDL} code, I found that I had to impose a tight prior on the rotation period (I actually fixed it at the literature value of 4.1 hr) in order to avoid fitting the systematics at the telluric wavelengths.
+When I do this, the MCMC code produces a very smooth amplitude spectrum for 2MASS 1821, as visible in Figure \ref{fig:ampSpecManualSTauRestrict}.
+I experimented with the restriction that $3.8 < \tau < 4.0$ based on the multi-term Fourier series fits.
+I used two different error scalings - 2.5 $\sigma$ and 4 $\sigma$.
+2.5 $\sigma$ give the expected $\bar{\chi^2} \approx 1$, whereas 4 $\sigma$ gives around 0.4.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
+	\label{fig:ampSpec0835times2p5ErrTauRest}
+	}
+\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
+	\label{fig:ampSpec1821fourTimesErr}
+	}
+	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit.
+In this case, there were MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
+	\label{fig:ampSpecManualSTauRestrict}
 	\vspace{0.1in}
@@
 
-\appendix
+%\appendix
 

### 2017-01-27 ms.tex
I fixed the 2MASS 1821 coordinates because they read 2MASS 1812 by accident.
I updated the explanation of the residuals plots.

@@
 \newcommand{\sha}{2MASS~J0835$-$0819}
-\newcommand{\shb}{2MASS~J1812+1414}
+\newcommand{\shb}{2MASS~J1821+1414}
 
@@
 \includegraphics[width=0.48\textwidth]{residual_3term_1080nm.pdf}
-\caption{{\it Left:} Residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data.
+\caption{Residuals after subtracting the maximum likelihood two-term model from Equation \ref{eq:cosfitMultiTerm} from the data.
+We show the residuals when using a 2 term model (left) and a 3 term model (right).
 The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}

### 2017-01-27 ms.tex
I added a new amplitude spectrum for 2MASS 0835 this time where I let A be +/- and impose a prior on the rotation period.

@@
 \subfloat[2MASS J1821 - 2.5$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
+	\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0250perc_err_taurestric.pdf}
 	\label{fig:ampSpec0835times2p5ErrTauRest}
@@
 \end{figure*}
+
+As with \shb\ I imposed a tight prior on $\tau$ such that $3.0 < \tau < 3.2$ for \sha. This now gives an average amplitude of zero -- see Figure \ref{fig:amp2mass08352p5ErrTauRest}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0250perc_err_taurestric.pdf}
+\caption{Amplitude spectrum for \sha\ with error bars scaled by 2.5$\sigma$. The average amplitude is zero.}\label{fig:amp2mass08352p5ErrTauRest}
+\end{centering}
+\end{figure}
 

### 2017-01-27 ms.tex
I added the 2MASS 0835 amplitude spectrum where I have scaled all error bars by a factor of 4.

--- 2017-01-27 ms.tex
@@
 	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
-	\label{fig:ampSpec0835times2p5ErrTauRest}
+	\label{fig:ampSpec1821times2p5ErrTauRest}
 	}
@@
 	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
-	\label{fig:ampSpec1821fourTimesErr}
+	\label{fig:ampSpec1821fourTimesErrTauRest}
 	}
@@
 	\label{fig:ampSpecManualSTauRestrict}
+	\vspace{0.1in}
+\end{figure*}
+
+As with \shb\ I imposed a tight prior on $\tau$ such that $3.0 < \tau < 3.2$ for \sha. This now gives an average amplitude of zero -- see Figure \ref{fig:ampSpec0835TauRestrict}.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
+	\label{fig:ampSpec1821times2p5ErrTauRest}
+	}
+\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
+	\label{fig:ampSpec1821fourTimesErrTauRest}
+	}
+	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit.
+In this case, there were two MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
+	\label{fig:ampSpec1821TauRestrict}
+	\vspace{0.1in}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835 - 2.5$\times \sigma$]{
+	\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0250perc_err_taurestrict.pdf}
+	\label{fig:ampSpec0835times2p5ErrTauRest}
+	}
+\subfloat[2MASS J0835 - 4$\times \sigma$ ]{
+	\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0400perc_err_taurestrict.pdf}
+	\label{fig:ampSpec0835fourTimesErrTauRest}
+	}
+	\caption{Restricting the $\tau$ parameter to, $3.0 < \tau < 3.2$ results in a spectrum that is on average near 0\% amplitude for \sha.
+We show the amplitude spectra for error bars scaled by 2.5$\sigma$ and 4.0$\sigma$.}
+	\label{fig:ampSpec0835TauRestrict}
 	\vspace{0.1in}

### 2017-01-29 ms.tex
I switched the T brightness plots to PNGs so it's easier to scroll and zoom.
I started reading through from the beginning and making small edits to the text to make sure it was consistent with the latest analysis and plots.

@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$2\% at 1~$\mu$m, with the variability amplitude declining toward longer wavelengths.
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 {\bf [PHASE VARIATION]}.
@@
 
-\begin{deluxetable*}{lllcccccccl}[t]
+\begin{deluxetable*}{lllcccccccl}
 \tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
@@
 The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
+{\bf [Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
 Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here.
@@
 	\plottwo{classify0835.pdf}{classify1821.pdf}
-	\plottwo{tbright0835.pdf}{tbright1821.pdf}
+	\plottwo{tbright0835.png}{tbright1821.png}
 	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.

### 2017-01-31 ms.tex
I added plots showing the time offset parameter as a function of wavelength.

@@
 \centering
-\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
-	\label{fig:ampSpec1821times2p5ErrTauRest}
-	}
-\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
-	\label{fig:ampSpec1821fourTimesErrTauRest}
-	}
-	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit.
-In this case, there were two MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
-	\label{fig:ampSpec1821TauRestrict}
-	\vspace{0.1in}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
 \subfloat[2MASS J0835 - 2.5$\times \sigma$]{
@@
 	}
-	\caption{Restricting the $\tau$ parameter to, $3.0 < \tau < 3.2$ results in a spectrum that is on average near 0\% amplitude for \sha.
+	\caption{Restricting the $\tau$ parameter to $3.0 < \tau < 3.2$ results in a spectrum that is on average near 0\% amplitude for \sha.
 We show the amplitude spectra for error bars scaled by 2.5$\sigma$ and 4.0$\sigma$.}
+	\label{fig:ampSpec0835TauRestrict}
+	\vspace{0.1in}
+\end{figure*}
+
+One thing to check is the time offset parameter as a function of wavelength.
+AB noticed a trend in this $t_1$ parameter, but didn't have error bars fully incorporated.
+I'm finding the trend is marginal when using 4$\sigma$ noise scaling.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835 - 4$\times \sigma$]{
+	\includegraphics[width=0.5\textwidth]{2mass_0835_t_1_spectrum_0400perc_err_taurestrict.pdf}
+	\label{fig:t1Spec0835TauRest}
+	}
+\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_t_1_spectrum_0400perc_err_taurestrict.pdf}
+	\label{fig:t1Spec1821TauRest}
+	}
+	\caption{Searching for trends in the $t_1$ parameter as a function of wavelength.
+The possible upward trend is marginal for \shb\ when using the 4$\sigma$ scaling of error bars.
+In these cases, we have restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
 	\label{fig:ampSpec0835TauRestrict}

### 2017-02-01 ms.tex
I added a figure showing that the IDL and python Mie scattering are in excellent agreement.

@@
 
+\clearpage
+\pagebreak
+\subsection{Mie scattering}
+
+My old Mie scattering code was in IDL and would be more work to incorporate into MCMC fitting, so I found python package \texttt{miescatter} and did a comparison with my IDL code.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{python_vs_IDL_example.pdf}
+\caption{Example Mie scattering extinction cross sections $Q_{ext}$ for a spherical particle with a radius of 0.5~$\mu$m and a complex index of refraction of n=1.825 - 0.001 $i$.
+The IDL and python code's are in excellent agreement.}\label{fig:IDLvsPython}
+\end{centering}
+\end{figure}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-02-03 ms.tex
I described some initial MCMC fits to the amplitude spectrum when using a single particle size.

@@
 
+I did an initial MCMC fit where I plugged in these same index of refraction (n=1.825 - 0.001 $i$ for all wavelengths) and fit the spectrum that I found in IDL.
+The best fit matches the data well with a $\bar{\chi^2}$ of 1.3, visible in Figure \ref{fig:mcmcMieBest1particle}.
+However, there are many solutions at different resonances in the Mie extinction curve visible in Figure \ref{fig:mcmcMieCorner1particle}.
+A better way to handle this is a log-normal distribution of particles as in \citet{schlawin2016}.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[Single Particle Best fit for \shb]{
+	\includegraphics[width=0.5\textwidth]{best_fit_single_particle_mie.pdf}
+	\label{fig:mcmcMieBest1particle}
+	}
+\subfloat[Single Particle Histograms for \shb]{
+	\includegraphics[width=0.5\textwidth]{corner_single_particle_mie.pdf}
+	\label{fig:mcmcMieCorner1particle}
+	}
+	\caption{An initial fit to the amplitude spectrum when using a single particle.
+	The best fit nicely matches the data but has multiple solutions at the Mie scattering resonances.}
+	\label{fig:mcmcMieCorner1particle}s
+	\vspace{0.1in}
+\end{figure*}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-02-07 ms.tex
I removed an extra s after a figure caption.
I added some example runs with a Log-Normal particle size distribution.

@@
 However, there are many solutions at different resonances in the Mie extinction curve visible in Figure \ref{fig:mcmcMieCorner1particle}.
-A better way to handle this is a log-normal distribution of particles as in \citet{schlawin2016}.
+A better way to handle this is a log-normal distribution of particles as in \citet{2016ApJ...826..156S}.
 
@@
 	}
-\subfloat[Single Particle Histograms for \shb]{
+\subfloat[Single Particle Posterios for \shb]{
 	\includegraphics[width=0.5\textwidth]{corner_single_particle_mie.pdf}
@@
 	The best fit nicely matches the data but has multiple solutions at the Mie scattering resonances.}
-	\label{fig:mcmcMieCorner1particle}s
+	\label{fig:mcmcMieCorner1particle}
+	\vspace{0.1in}
+\end{figure*}
+
+I manually created a log-normal distribution of particles in Python and added up their cross sections weighted by number of particles.
+This process is slow, so I calculated it once and found  a 15th order polynomial fit to $Q_{ext}$ and evaluated this in the model.
+The resulting MCMC distribution is shown in Figure \ref{fig:mcmcMieCornerLogNorm}.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[Log-Normal Best fit for \shb]{
+	\includegraphics[width=0.5\textwidth]{best_fit_lognormal_mie.pdf}
+	\label{fig:mcmcMieBestLogNorm}
+	}
+\subfloat[Log-Normal Posteriors for \shb]{
+	\includegraphics[width=0.5\textwidth]{corner_lognormal_mie.pdf}
+	\label{fig:mcmcMieCornerLogNorm}
+	}
+	\caption{An initial fit to the amplitude spectrum when using a log-normal size distribution with a $\sigma=0.5$.
+	Again, there are a few ``walkers'' that stay at large radii.}
+	\label{fig:mcmcMieCornerLogNorm}
 	\vspace{0.1in}

### 2017-02-10 ms.tex
I added a few figures to describe why there was a local min for very large particle radii and how I excluded local min.

@@
 
+On closer inspection, I see that there is a local minimum for large particle radii where the $\chi^2$ begins to increase from 3~$\mu$m to 2$\mu$m.
+This is illustrated in Figure \ref{fig:localMinLargeRadii}.
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{local_min_illustration.pdf}
+\caption{A set of example Mie scattering models for example parameters for the Amplitude offset and median particle radius written as [A,r].
+The model at 2~$\mu$m is slightly worse than at 3~$\mu$m, so it traps a few walkers in the MCMC run.}\label{fig:localMinLargeRadii}
+\end{centering}
+\end{figure}
+
+When I discard walkers with very low likelihood, as done in CHIMERA, the local minima are not included since their so low probability.
+The resulting MCMC run is shown in Figure \ref{fig:localMinExcludeCorner}.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{corner_lognormal_mie_no_lmin.pdf}
+\caption{MCMC fit when discarding points with a $\chi^2$ more than 5 times the minimum to exclude walkers that were trapped at local minima.}\label{fig:localMinExcludeCorner}
+\end{centering}
+\end{figure}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-02-11 ms.tex
I added a weighted average in the phase with wavelength study and also did a phase vs Amplitude.

@@
 In these cases, we have restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
-	\label{fig:ampSpec0835TauRestrict}
+	\label{fig:t1SpecTauRestrict}
+	\vspace{0.1in}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835 - 4$\times \sigma$]{
+	\includegraphics[width=0.5\textwidth]{2mass_0835_t1_vs_A1_0400perc_err_taurestrict.pdf}
+	\label{fig:t1vsA1Spec0835}
+	}
+\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_t1_vs_A1_0400perc_err_taurestrict.pdf}
+	\label{fig:t1vsA1Spec1821}
+	}
+	\caption{Searching for trends in the $t_1$ parameter as a function of Amplitude ($A_1$).
+No clear trend arises in these correlation plots.
+As with Figure \ref{fig:t1SpecTauRestrict}, we have used 4$\sigma$ scaling of error bars and restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
+	\label{fig:t1vsA1SpecTest}
 	\vspace{0.1in}

### 2017-02-13 ms.tex
I showed what the MORIS photometry time series looks like and how it affects the spectrum.

@@
 \pagebreak
-\subsection{Mie scattering}
+\subsection{Mie scattering MCMC}
 
@@
 \end{figure}
+
+\clearpage
+\pagebreak
+\subsection{MORIS Data}
+
+I made a time series of my photometry to see if it would help with the spectrum fit.
+
+The SNR is so low that's it hard to see any clear pattern.
+The photometry adds very little to the spectrum, as seen in Figure \ref{fig:morisPhotometryAndSpec}.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[MORIS $i$ Band Photometry for \shb]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_moris_tser_best_fit.pdf}
+	\label{fig:morisTSerBestFit}
+	}
+\subfloat[Amplitude spectrum for \shb\ when adding MORIS photometry]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_a1_spec_w_moris.pdf}
+	\label{fig:spectrum1821WMoris}
+	}
+	\caption{MORIS photometry does not significantly improve the constraints on the spectrum.}
+	\label{fig:morisPhotometryAndSpec}
+\end{figure*}
 

### 2017-02-13 ms.tex
I discovered that the MORIS photometry was having the SpeX error bar scaling but should not. Now I think it adds a potentially useful upper limit to the short wavelength part of the spectrum.

@@
 
-I made a time series of my photometry to see if it would help with the spectrum fit.
-
+I made a time series of the MORIS $i$ band photometry to see if it would help with the spectrum fit.
 The SNR is so low that's it hard to see any clear pattern.
-The photometry adds very little to the spectrum, as seen in Figure \ref{fig:morisPhotometryAndSpec}.
+However, the photometry can put upper limits to the spectrum, as seen in Figure \ref{fig:spectrum1821WMoris}.
 
@@
 	}
-	\caption{MORIS photometry does not significantly improve the constraints on the spectrum.}
+	\caption{MORIS photometry can put an upper limit on the short wavelength end of the spectrum spectrum.}
 	\label{fig:morisPhotometryAndSpec}

### 2017-02-14 supplement.tex
This now creates the document supplement by reverting the revert.
This reverts commit c797583931de84fb6d22da6ee3a0e1c5e1da3c74.

--- 2017-02-13 ms.tex
@@
 %\documentclass[12pt,preprint]{aastex}
-\documentclass[twocolumn]{aastex6}
+\documentclass[manuscript]{aastex6}
 %\documentclass[iop]{emulateapj}
@@
 
-\title{Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010}
+\title{Supplement to Spectral Variability of Two Rapidly Rotating Brown Dwarfs: \\2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010}
 
@@
 \begin{abstract}
-Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
-The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds.
-Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
-By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
-{\bf [PHASE VARIATION]}.
-The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths.
-An alternate model based on surface hot spots requires implausibly large temperature variations.
-The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
+Supplementary Information
 \end{abstract}
@@
 \keywords{techniques: spectroscopic -- stars: atmospheres -- stars: brown dwarfs -- stars: individual (\objectname{2MASS J08354256-0819237}, \objectname{2MASS J18212815+1414010}) -- stars: late-type -- stars: variables: general}
-
-\section{Introduction}
-
-The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
-In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}
-whose surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
-Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
-Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
-
-Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
-The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
-Wavelength-dependent phase variance in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
-Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.
-
-Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
-Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
-In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
-However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity, or evolution in variability modes.
-
-Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects  (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}) can significantly improve the precision of ground-based spectro-photometry.
-\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
-This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy.
-A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
-In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion.
-These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
-
-This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions.
-We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
-In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
-In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
-We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
-We summarize our results in Section~\ref{sec:conclusions}.
-
-\section{Target Selection and Characterization}\label{sec:targets}
-
-We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}.
-The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$.
-We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
-Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
-
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
-This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
-Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
-There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
-2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
-This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
-\citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
-There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.
-
-\begin{deluxetable*}{lllcccccccl}
-\tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
-\tablewidth{0pt}
-\tablehead{
- & \multicolumn{2}{c}{Spectral Type} \\
-\colhead{Name} & 
-\colhead{Opt} & 
-\colhead{NIR} & 
-\colhead{$d$} & 
-\colhead{2MASS $H$} & 
-\colhead{$J-K_s$} & 
-\colhead{\teff} & 
-\colhead{P$_{rot}$} &
-\colhead{$v\sin{i}$} & 
-\colhead{$i$\tablenotemark{a}} & 
-\colhead{Refs} \\
- &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
- }
-\startdata
-\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
-\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
-\enddata
-\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
-A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
-\tablenotetext{b}{Tentative period.}
-\tablenotetext{c}{Estimated from the \citet{2015ApJ...810..158F} {\teff}/spectral type relation.}
-\tablerefs{(1) \citet{2003AJ....126.2421C};
-(2) \citet{2012ApJ...752...56F}; 
-(3) \citet{2015ApJ...810..158F};
-(4) \citet{2004MNRAS.354..378K};
-(5) \citet{2010ApJ...723..684B};
-(6) \citet{2008ApJ...686..528L}; 
-(7) \citet{2016MNRAS.455..357S};
-(8) \citet{2015ApJ...798...73G};
-(9) \citet{2015ApJ...799..154M}
-(10) \citet{2015ApJ...798L..13Y}; 
-}
-\end{deluxetable*}
-
-\begin{figure*}
-\centering
-	\plottwo{image0835-0819.pdf}{image1821+1414.pdf}
-	\label{fig:image1821}
-	\vspace{-.9in}
-	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right).
-Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left.
-The comparison stars referred to in the text appear as blue sources in these images.
-}
-	\label{fig:images}
-	\vspace{0.17in}
-\end{figure*}
-
-To characterize the atmospheric regions probed by our observations, we analyzed previously 
-obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
-Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicate near-infrared
-classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}).
-The former is considerably later than the L5 optical classification previously reported by \citet{2003AJ....126.2421C}.
-We confirm the intermediate low surface gravity classification (INT-G) reported by \citet{2016ApJ...833...96L} based on the indices of \citet{2013ApJ...772...79A} using an L7 classification.
-The discrepancy between the optical and near-infrared classifications of this source is likely related to surface gravity effects.
-{\shb}, on the other hand, is a good match to the L5 spectral standard and has a field dwarf gravity classification.
-
-We computed brightness temperature spectra from these data as
-\begin{equation}
-T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{I_{\lambda,surf}\lambda^5}\right)\right]^{-1}
-\end{equation}
-where the surface flux density $I_{\lambda,surf}$ is computed as
-\begin{equation}
-I_{\lambda,surf} = {\pi}B_{\lambda} = I_{\lambda,obs}\left(\frac{d}{R}\right)^2 = I_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
-\end{equation}
-$I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.
-Both spectra were normalized to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}.
-We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming effective temperatures ({\teff}s) from \citet{2015ApJ...810..158F} based on these sources' bolometric luminosity measurements (Table~\ref{tab:bdProp}).
-Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\teff} and radius were propagated by Monte Carlo simulation.
-For {\sha} we considered two cases: radii corresponding to an age of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}, for which the evolutionary models predict radii of 0.147~R$_{\odot}$ to 0.115~R$_{\odot}$; and an age range of 1--5~Gyr for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.084~R$_{\odot}$.
-For {\shb}, we assumed a lower age limit of 200~Myr based on its FLD-G classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S} range of 1--5~Gyr; evolutionary models predict radii of 0.120~R$_{\odot}$ to 0.097~R$_{\odot}$ for these ages.
-
-Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.
-The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
-{\bf [Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
-Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here.
-For {\shb},
-brightness temperatures range from 1880$\pm$30~K at the $J$-band peak to 1700$\pm$40~K at the $K$-band peak.
-These values are notably warmer than the {\teff} = 1614$\pm$100~K estimated from \citet{2015ApJ...810..158F} {\teff}/spectral type relation, but relatively consistent this source's earlier spectral type as compared to {\sha}.
-We conjecture that the Filippazzo et al.\ relation underestimates the {\teff} of this source due to its unusually dusty spectral energy distribution.
-
-\begin{figure*}
-\centering
-	\plottwo{classify0835.pdf}{classify1821.pdf}
-	\plottwo{tbright0835.png}{tbright1821.png}
-	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
-(Bottom) Calculated brightness temperature spectra of {\sha} (left) and {\shb} (right).
-The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations.
-For {\sha}, we calculate separate brightness temperatures assuming radii consistent with a low surface gravity (50--200 Myr; blue) and field surface gravity (1--5~Gyr; black).
-}
-	\label{fig:tbright}
-	\vspace{0.1in}
-\end{figure*}
-
-\section{Observations}\label{sec:obs}
-
-We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
-{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
-Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
-Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis.
-This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction.
-The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
-Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively.
-The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
-
-%For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
-For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
-
-\begin{deluxetable*}{lccccccccc}
-\tablecaption{Observations}\label{tab:obsParam}
-\tablewidth{0pt}
-\tablehead{
- & \multicolumn{3}{c}{Observation Epoch (UT)} \\
- \cline{2-4}
-\colhead{Target} & 
-\colhead{Date} & 
-\colhead{Start} & 
-\colhead{End} & 
-\colhead{$N_{int}$} & 
-\colhead{$t_{int}$} & 
-\colhead{Duration} & 
-\colhead{Airmass} & 
-\colhead{Reference Star} & 
-\colhead{FWHM \@ $H$} \\
- & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
-\startdata
-{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
-{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
-\enddata
-\tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp.
-The duration is the total time from start to end of the observations including the reset times and overheads.
-The FWHM is the measured median value of the time series around 1.6$\mu$m.}
-\end{deluxetable*}
-
-Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
-
-The images were rectified by shifting each row to match a center row in between the two sources.
-This was achieved by cross correlating the reference row with all other detector rows (which have the same background spectrum) and fitting a smooth function over the sources as in \citealt{2016ApJ...826..156S}.
-We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
-% to measure pixel response and assess flexure in the instrument with telescope orientation.
-For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response.
-To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
-These shifts were used to apply a custom flat field for every image.
-
-For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.
-{\bf [IS THIS TRUE FOR 1821?- \color{red}{YES, there were only 5 good sky frames at the end and 3 at the beginning.}]}
-
-As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit to points more than 30 pixels away from the center of the source dispersion traces.
-Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials along the spectral direction one row at a time with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
-These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 
-Typical signals-to-noise of the extracted spectra were 40 - 100 per spectral pixel (unbinned).
-Relative spectra (source/reference) were then computed for each exposure.
-Our image rectification process described above ensures that the wavelength solution is the same for each row if the image.
-However, there are small additional shifts of the sources within the slit so another cross-correlation is performed between the sources to ensure they match before dividing the two spectra.
-
-For MORIS reduction, we used the raw files and performed aperture photometry with the IDL \texttt{aper} procedure using an aperture size of 6 pixels and a sky annulus of 8-11 pixels.
-{\bf [MORIS REDUCTION FOR 1821?]}
-
-\section{Analysis}\label{sec:analysis}
-
-\subsection{Light Curves}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
-	\label{fig:specphot0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
-	\label{fig:specphot1821}
-	}
-	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).
-These spectra have not been corrected for telluric absorption or instrumental spectral response.
-The reference stars have significantly bluer spectra than the brown dwarfs.
-Bottom Panels: Dynamic spectra of each brown dwarf system.
-The dynamic spectrum for \sha\ shows no significant variability whereas there is a periodic modulation for \shb\ that decrease toward longer wavelengths.
-[MORE DESCRIPTION -- How should the reader interpret these dynamic spectra?]}
-	\label{fig:specphot}
-	\vspace{0.1in}
-\end{figure*}
-
-Figure \ref{fig:specphot} shows the dynamic spectra (relative source brightness as a function of wavelength and time) for both targets, as well as the median spectra of the target and reference stars.
-{\sha} shows a relative flat response with shows no obvious variations at the $\lesssim1$\% level.
-{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
-The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
-Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.
-
-{\bf [MORIS ANALYSIS FOR 1821?]}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_t_series.png}
-	\label{fig:tserPhase0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_t_series.png}
-	\label{fig:tserPhase1821}
-	}
-	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
-	\label{fig:tserPfold}
-\end{figure*}
-
-Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
-The uncertainties in these curves are 0.2\% in high throughput regions of the spectrum and 0.6\% per exposure.
-The lower values are areas of high throughput and flux whereas the low values are near telluric absorption features or the edges of the spectrum.
-We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
-In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
-We attribute this to correlated errors between wavelengths. {\bf [WHAT? HOW DETERMINED?]}
-
-As seen in Figure~\ref{fig:tserPfold}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m.
-These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr.
-In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
-As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
-{\bf [WE SHOULD VERIFY THIS]}
-
-Each of the light curves were fit to a simple sinusoidal model:
-\begin{equation}\label{eq:cosfit}
-F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
-\end{equation}
-where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
-For our initial fits, we allowed $A$, $t_0$, $B$ and $C$ to be free parameters, but fixed $\tau$ at the literature value of rotation period to mitigate systematic biases (e.g., convergence on a period of $\sim$24 hr).
-{\bf [IS THIS A PROBLEM IF YOU IGNORE TELLURIC BANDS?
-COULD YOU CONSTRAIN THE ALLOWED PERIOD RANGE (I.E., PRIOR).
-SHOULD DO A FIT WITH PERIOD FREE TO VARY TO GET A MEASURE OF THIS QUANTITY]}
-We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.
-{\bf [THIS IS LIKELY LEADING TO OUR "DETECTION" OF 0835; NEED ANOTHER WAY TO DO THIS]}.
-We use the standard deviation of points near minimum to estimate the noise in the flux time series.
-The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
-
-\begin{figure*}
-\centering
-\subfloat[2MASS J0835 - \colorbox{red}{fit might need more work} ]{
-	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
-	\label{fig:ampspec0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
-	\label{fig:ampspec1821}
-	}
-	\caption{Sine fit amplitude versus wavelength for each brown dwarf.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.
-2MASS J0835 shows no clear trend in wavelength, while 2MASS J1821 has a strong slope indicative of Mie-scattering particles.}
-	\label{fig:ampSpec}
-\end{figure*}
-
-STOPPED HERE
-
-Figure \ref{fig:ampSpec} shows the best fit periodic amplitudes as a function of wavelength.
-For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
-2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
-This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}.
-We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.
-
-%    \begin{figure}[!ht]
-%    \centering
-%    \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
-%    \caption{Sine fit amplitude versus wavelength for 2MASS J1821.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
-%    \end{figure}
-
-\subsection{Mie Scattering Fit}
-
-We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
-We model the extinction coefficient, $Q_{ext}$ from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
-We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains (MgSiO$_3$).
-For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
-\caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption.
-[SOMETHING HERE?
-like, The data are fit] with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
-Also shown in the figure is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}.
-The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
-\end{centering}
-\end{figure}
-
-Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
-In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
-
-\citet{2015ApJ...798L..13Y} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
-Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
-\begin{equation}
-A  = \frac{f_R - 1}{f_R + 1}
-\end{equation}\label{eq:ampFromRatio}
-where $f_R$ is the flux ratio of the maximum over minimum flux.
-
-The WFC3 amplitude spectrum is shown with the data in Figure \ref{fig:ampspec1821mie}.
-There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
-The WFC3 spectrum is not affected by the telluric absorption, unlike the SpeX data.
-\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our Mie scattering fit.
-
-A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
-In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains [WHY DO WE USE PYROXENE INSTEAD OF FORSTERITE?], similar to our characteristic particle size.
-
-\subsection{Spot Model Fit}\label{sec:spotModel}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.4\textwidth]{temperature_drawing.pdf}
-\caption{A simple two region model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
-\end{centering}
-\end{figure}
-
-Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
-In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
-This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
-We assume that are each in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
-The flux ratio between maximum and minimum flux is then
-\begin{equation}
-f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
-\end{equation}
-where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first ($T_1$ and second ($T_2$) regions respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
-$\alpha_1$ and $\alpha_2$ are limited to [0,1].
-Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
-\begin{equation}\label{eq:twoTempAmpAlphas}
-A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
-\end{equation}
-If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
-If we ignore projection effects for small area coverage, the effective temperature is 
-\begin{equation}
-\sigma T_{eff}^4 \approx (\alpha_1 + \alpha_2) \sigma T_1^4 + (2 - \alpha_1 - \alpha_2) \sigma T_2^4
-\end{equation}
-where $\sigma$ is the Stephan-Boltzmann constant.
-
-In the model fitting, we found a strong correlation between $\alpha_1$ and $\alpha_2$.
-Therefore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
-\begin{equation}\label{eq:twoTempAmp}
-A_\lambda = \frac{\beta \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(2 \alpha_1 - \beta \right) B_\lambda(T_1) + \left(2 - 2 \alpha_1 + \beta \right) B_\lambda(T_2)}.
-\end{equation}
-
-We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
-To be close to the effective temperature of the brown dwarf, we fix $T_1$ to be 1600 K and only vary $T_2$.
-This model is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a reduced chi-squared, $\bar{\chi}^2$ = 15.
-Next, we attempt a model where we allow $\alpha_1$ and $\alpha_2$ to be free parameters and restrict the temperature limits of the two regions to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
-The best fit model has $T_{eff} \approx $1590 K and $\bar{\chi}^2$=2.1, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
-Finally, we consider a model where all four parameters, $\alpha_1$, $\alpha_2$, $T_1$ and $T_2$ are all free.
-With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
-The $\alpha$ values are both $<<1$, indicating that the model fits with dark patches on a small fraction of the surface.
-[I MODIFIED THIS SENTENCE; IS IT CORRECT?
-I'm a little confused about how both $\alpha$ values can be $<<1$; if one is small doesn't the other have to be large?]
-
-The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly larger than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
-Therefore, we suspect that hot or cold spots on the surface are a less plausible explanation of the variability of 2MASS J1821 than a heterogenous temperature distribution.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
-\caption{The same data as in Figure \ref{fig:ampspec1821mie}.
-We fit the data with a two region model that assumes the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
-\end{centering}
-\end{figure}
-% Command used:
-% plot_rad_vs_wavl,/amp,/shadetell,custxrange=[0.8,2.5],custyrange=[-0.1,1.9],/showYang,/twoTreg
-
-\section{Conclusions}\label{sec:conclusions}
-
-We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
-These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
-We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
-After fitting sinusoids to both of the time series, we find that 2MASS 0835 has low levels of variability and no significant wavelength dependence.
-
-2MASS J1821 shows significant variability up to the 1.1\% amplitude at short wavelengths (0.8$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
-This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
-The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.
-
-We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with Mg-rich pyroxene grains with sub-micron sized particles.
-A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.
-We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
-The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperature differences.
-Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.
-
-\section{Acknowledgements}
-CHIMERA retrieval makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
-Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.
-Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
-This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
-This research made use of the \texttt{astropy} package \citep{astropy2013}.
-The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.
-We are most fortunate to have the opportunity to conduct observations from this mountain.
-
-\appendix
-\clearpage
-\pagebreak
 

### 2017-02-14 ms.tex
I wiped out the appendix b/c it's now split into a supplement document.

--- 2017-02-11 ms.tex
@@
 
+\vspace{0.2in}
 \begin{figure}
@@
 We are most fortunate to have the opportunity to conduct observations from this mountain.
-
-\appendix
-\clearpage
-\pagebreak
-
-\section{Color-Magnitude Diagram}
-
-Figure \ref{fig:CMD} shows the color magnitude diagram from the sample of brown dwarfs in \citet{dupuy2012ltparallax}, which includes 2MASS J0835 but not 2MASS J1821.
-We highlight these two brown dwarfs to be contrasted with the rest of the population.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{color_mag.pdf}
-\caption{Color-Magnitude diagram from \citet{dupuy2012ltparallax}. We added 2MASS J1821 using Simbad magnitudes and parallaxes.}\label{fig:CMD}
-\end{centering}
-\end{figure}
-
-\pagebreak
-\section{Example Posterior Distributions}
-[DO WE NEED MORE TEXT IN THIS SECTION EXPLAINING EACH FIGURE?]
-\subsection{Time Series}
-In Figure \ref{fig:postCosfit}, we show the posterior distributions of a sinusoidal model (Equation \ref{eq:cosfit}) fit to the data using \texttt{emcee} \citep{foreman-mackey2013emcee} for an example wavelength bin of 1.08~$\mu$m.
-This wavelength bin is one of the high amplitude fits that is relatively unaffected by telluric contamination.
-In this example, we input photon noise only.
-We impose priors on the amplitude $A_1 > 0$, $|t_t| < 6 hr$ (to avoid multiple periodic solutions) and that the period $0 < \tau < 6 hr$ so that the periodicity is shorter than the observation window length.
-The model parameters are close to Gaussian and the only visible correlation is between the time offset, $t_1$, and the rotation period $\tau$.
-The maximum likelihood solution is shown in Figure \ref{fig:model2Cosfit} and has a chi-squared per degree of freedom ($\bar{\chi^2}$) of 12.1
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_example.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfit} for the wavelength bin 1.08~$\mu$m.
-Amplitude, $A_1$ is in percent, the time offset $t_1$ is in hours, the period of oscillation, $\tau$, is in units of hours, B is in units of fraction of flux per hour and C is the offset constant in fraction (not percent).
-We only input photon counting and read noise statistics for the errors.
-This is likely and underestimate for the uncertainty in the time series.
-}\label{fig:postCosfit}
-\end{centering}
-\end{figure}
-
-Since Equation \ref{eq:cosfit} is a poor fit to the data, as visible in Figure \ref{fig:model2Cosfit}, we also explore models with additional sinusoidal frequencies.
-In the multiple term model, we add cosine functions at $n$ times the frequency:
-\begin{equation}\label{eq:cosfitMultiTerm}
-F(t) = B t + C + A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + A_n \cos(2 n \pi (t - t_n)/\tau) +  ...
-\end{equation}
-Now there are $n$ amplitude parameters $A_n$ and $n$ time offset parameters $t_n$.
-Figure \ref{fig:model2Cosfit} shows the best fit compared to the data for 2 term and 3 term sinusoidal fits.
-We assume the same priors as the 1 term sinusoidal fit with  $A_n > 0$.
-For the time offsets, we restrict the range to be $\pm$ 4 hr / $n$.
-The multiple term model appear visually to fit the data well.
-However, the $\bar{\chi^2}$ are still 7.9 and 7.4, so it is not the expected 1.0.
-However, the error bars are underestimated when only including photon and read noise components.
-With exoplanet light curves, the standard deviation of the out-of-transit baseline flux can be used as an estimate for errors.
-With the brown dwarf rotation light curves, there is no flat baseline over which to measure error levels.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
-\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m.
-Error bars are shown for photon and read noise.
-We plot a best-fit models using a single cosine term (green, $\bar{\chi^2}$ = 12.1).
-Additional terms improve the fits to the data and the $\bar{\chi^2}$.}\label{fig:model2Cosfit}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.7\textwidth]{corner_fit_2term.pdf}
-\caption{Example posterior distributions for an MCMC fit to the time series using Equation \ref{eq:cosfitMultiTerm} for 2 terms.
-Again, there is little correlation between the posteriors for the different parameters. {\it Right} Same figure, but with 3 cosine terms.}\label{fig:post2Cosfit}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.48\textwidth]{residual_2term_1080nm.pdf}
-\includegraphics[width=0.48\textwidth]{residual_3term_1080nm.pdf}
-\caption{Residuals after subtracting the maximum likelihood two-term model from Equation \ref{eq:cosfitMultiTerm} from the data.
-We show the residuals when using a 2 term model (left) and a 3 term model (right).
-The standard deviation of the residuals is 0.6\% whereas the error from photon counting statistics is 0.2\%.}\label{fig:resid2Cosfit}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{histo_resids.pdf}
-\caption{Histogram of residuals after subtracting the maximum likelihood model from Equation \ref{eq:cosfitMultiTerm} from the data with 2 terms.}\label{fig:histoResid2Cosfit}
-\end{centering}
-\end{figure}
-
-\clearpage
-\pagebreak
-\subsection{Amplitude Spectrum}
-
-We also use \texttt{emcee} to fit the amplitude spectrum of 2MASS J1821 using the two temperature surface model in Section \label{sec:spotModel} with Equation \ref{eq:twoTempAmp}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{best_fit_spec_2temp.pdf}
-\caption{We repeat the amplitude spectrum of 2MASS J1821 from Figure \ref{fig:ampspec1821tdiff}, which excludes the wavelengths contaminated by telluric absorption.
-We show a maximum likelihood model spectrum, which has a $\chi^2$ per degree of freedom of 1.16.}\label{fig:ML2Tempfit}
-\end{centering}
-\end{figure}
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_fit_2temp.pdf}
-\caption{Example posterior distributions for an MCMC fit to the spectra using Equation \ref{eq:twoTempAmp}.}\label{fig:post2Tempfit}
-\end{centering}
-\end{figure}
-
-\clearpage
-\pagebreak
-\subsection{Manual Shifting}
-
-The trends near 1.4 $\mu$m and 1.8 $\mu$m in \shb\ could probably be reduced by better wavelength shifting.
-I wrote a GUI that let me control the shifts for each spectrum and plot the ratio spectrum.
-I minimized the residuals and ran a test case for \sha.
-As seen in Figure \ref{fig:manualVsAutoShift0835}, the manual shifting dramatically reduces the systematic linear trends in the dynamic spectra.
-In contrast to Figure \ref{fig:specphot}, not linear de-trending has been applied to columns so the systematic linear trends are visible in both cases.
-The automatic shifting finds the peak in the cross correlation.
-It does this by cross-correlating a portion of the spectrum (excluding the endpoints) and zeroed on the wings. 
-The automatic method then fits the cross-correlation pattern with a parabola to find the peak.
-The manual method is where we use keystrokes to shift one spectrum by 0.333 px back in forth until the ratio of another spectrum has the smallest residuals.
-Two iterations were used in the manuals shifting: (1) minimizing the residuals of the target divided by reference and (2) minimizing the residuals of the target divided by the target middle spectrum.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835- Automatic Shifting]{
-	\includegraphics[width=0.5\textwidth]{specphot_0835_auto_noremovel.pdf}
-	\label{fig:specphot0835autoS}
-	}
-\subfloat[2MASS J0835 - Manual shifting ]{
-	\includegraphics[width=0.5\textwidth]{specphot_0835_manual_noremovel.pdf}
-	\label{fig:specphot0835manualS}
-	}
-	\caption{Dynamic spectra of {\sha} using automatic cross correlation wavelength shifting (left) and manual wavelength shifting(right).
-	The manual method shows dramatically better systematics in these dynamic spectra which have no fits along columns to remove trends.}
-	\label{fig:manualVsAutoShift0835}
-	\vspace{0.1in}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J1821- Automatic Shifting]{
-	\includegraphics[width=0.5\textwidth]{specphot_1821_auto_noremovel.pdf}
-	\label{fig:specphot1821autoS}
-	}
-\subfloat[2MASS J1821 - Manual shifting ]{
-	\includegraphics[width=0.5\textwidth]{specphot_1821_manual_noremovel.pdf}
-	\label{fig:specphot1821manualS}
-	}
-	\caption{Dynamic spectra of {\shb} using automatic cross correlation wavelength shifting (left) and manual wavelength shifting(right).
-	The manual method shows better systematics but higher frequency noise.}
-	\label{fig:manualVsAutoShift1821}
-	\vspace{0.1in}
-\end{figure*}
-
-\clearpage
-\pagebreak
-\subsection{MCMC Time Series Fits - first try}
-
-Fitting all light curves to \sha\ with MCMC methods and without the A$_1 >$ 0 prior results in more non-detections, but an unusual pattern to the spectra.
-As with other MCMC fits, error bars are from photon and read noise, so they're likely under-estimated.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835 - Manual Shifting]{
-	\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_0835.pdf}
-	\label{fig:ampSpec0835ManualS}
-	}
-\subfloat[2MASS J1821 - Manual shifting ]{
-	\includegraphics[width=0.5\textwidth]{mcmc_spectrum_2mass_1821.pdf}
-	\label{fig:ampSpec1821ManualS}
-	}
-	\caption{Amplitude spectrum of {\sha} (left)  and {\shb} (right) using manual wavelength shifting, 1 cosine term fit and MCMC fitting with error bars from photon and read noise.}
-	\label{fig:ampSpecManualS}
-	\vspace{0.1in}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835 - 4$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{mcmc_2mass_0835_spectrum_0400perc_err.pdf}
-	\label{fig:ampSpec0835fourTimesErr}
-	}
-\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
-	\includegraphics[width=0.5\textwidth]{mcmc_2mass_1821_spectrum_0400perc_err.pdf}
-	\label{fig:ampSpec1821fourTimesErr}
-	}
-	\caption{As an experiment, I remade the amplitude spectra of Figure \ref{fig:ampSpecManualS} but scaled all error bars up by a factor of 4 for all points to account for some systematic errors.
-IE, Amplitude spectrum of {\sha} (left)  and {\shb} (right) using manual wavelength shifting, 1 cosine term fit and MCMC fitting with error bars from 4$\times$ photon and read noise.}
-	\label{fig:ampSpecManualSfourTimesErr}
-	\vspace{0.1in}
-\end{figure*}
-
-\clearpage
-\pagebreak
-\subsection{MCMC Time Series Fits - second try}
-
-As with my \texttt{IDL} code, I found that I had to impose a tight prior on the rotation period (I actually fixed it at the literature value of 4.1 hr) in order to avoid fitting the systematics at the telluric wavelengths.
-When I do this, the MCMC code produces a very smooth amplitude spectrum for 2MASS 1821, as visible in Figure \ref{fig:ampSpecManualSTauRestrict}.
-I experimented with the restriction that $3.8 < \tau < 4.0$ based on the multi-term Fourier series fits.
-I used two different error scalings - 2.5 $\sigma$ and 4 $\sigma$.
-2.5 $\sigma$ give the expected $\bar{\chi^2} \approx 1$, whereas 4 $\sigma$ gives around 0.4.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J1821 - 2.5$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0250perc_err_taurestrict.pdf}
-	\label{fig:ampSpec1821times2p5ErrTauRest}
-	}
-\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_spectrum_0400perc_err_taurestrict.pdf}
-	\label{fig:ampSpec1821fourTimesErrTauRest}
-	}
-	\caption{Restricting the $\tau$ parameter to, $3.8 < \tau < 4.0$ significantly reduces the long term quadratic terms' contribution to the sinusoidal fit.
-In this case, there were MCMC fits for \shb, one with error bars scaled by 2.5$\sigma$ and the other by 4.0$\sigma$.}
-	\label{fig:ampSpecManualSTauRestrict}
-	\vspace{0.1in}
-\end{figure*}
-
-As with \shb\ I imposed a tight prior on $\tau$ such that $3.0 < \tau < 3.2$ for \sha. This now gives an average amplitude of zero -- see Figure \ref{fig:ampSpec0835TauRestrict}.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835 - 2.5$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0250perc_err_taurestrict.pdf}
-	\label{fig:ampSpec0835times2p5ErrTauRest}
-	}
-\subfloat[2MASS J0835 - 4$\times \sigma$ ]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_spectrum_0400perc_err_taurestrict.pdf}
-	\label{fig:ampSpec0835fourTimesErrTauRest}
-	}
-	\caption{Restricting the $\tau$ parameter to $3.0 < \tau < 3.2$ results in a spectrum that is on average near 0\% amplitude for \sha.
-We show the amplitude spectra for error bars scaled by 2.5$\sigma$ and 4.0$\sigma$.}
-	\label{fig:ampSpec0835TauRestrict}
-	\vspace{0.1in}
-\end{figure*}
-
-One thing to check is the time offset parameter as a function of wavelength.
-AB noticed a trend in this $t_1$ parameter, but didn't have error bars fully incorporated.
-I'm finding the trend is marginal when using 4$\sigma$ noise scaling.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835 - 4$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_t_1_spectrum_0400perc_err_taurestrict.pdf}
-	\label{fig:t1Spec0835TauRest}
-	}
-\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_t_1_spectrum_0400perc_err_taurestrict.pdf}
-	\label{fig:t1Spec1821TauRest}
-	}
-	\caption{Searching for trends in the $t_1$ parameter as a function of wavelength.
-The possible upward trend is marginal for \shb\ when using the 4$\sigma$ scaling of error bars.
-In these cases, we have restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
-	\label{fig:t1SpecTauRestrict}
-	\vspace{0.1in}
-\end{figure*}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835 - 4$\times \sigma$]{
-	\includegraphics[width=0.5\textwidth]{2mass_0835_t1_vs_A1_0400perc_err_taurestrict.pdf}
-	\label{fig:t1vsA1Spec0835}
-	}
-\subfloat[2MASS J1821 - 4$\times \sigma$ ]{
-	\includegraphics[width=0.5\textwidth]{2mass_1821_t1_vs_A1_0400perc_err_taurestrict.pdf}
-	\label{fig:t1vsA1Spec1821}
-	}
-	\caption{Searching for trends in the $t_1$ parameter as a function of Amplitude ($A_1$).
-No clear trend arises in these correlation plots.
-As with Figure \ref{fig:t1SpecTauRestrict}, we have used 4$\sigma$ scaling of error bars and restricted the $\tau$ parameter with priors to $3.0 < \tau < 3.2$ and $3.8 < \tau < 4.0$ for \sha\ and \shb\ respectively.}
-	\label{fig:t1vsA1SpecTest}
-	\vspace{0.1in}
-\end{figure*}
-
-\clearpage
-\pagebreak
-\subsection{Mie scattering}
-
-My old Mie scattering code was in IDL and would be more work to incorporate into MCMC fitting, so I found python package \texttt{miescatter} and did a comparison with my IDL code.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{python_vs_IDL_example.pdf}
-\caption{Example Mie scattering extinction cross sections $Q_{ext}$ for a spherical particle with a radius of 0.5~$\mu$m and a complex index of refraction of n=1.825 - 0.001 $i$.
-The IDL and python code's are in excellent agreement.}\label{fig:IDLvsPython}
-\end{centering}
-\end{figure}
-
-I did an initial MCMC fit where I plugged in these same index of refraction (n=1.825 - 0.001 $i$ for all wavelengths) and fit the spectrum that I found in IDL.
-The best fit matches the data well with a $\bar{\chi^2}$ of 1.3, visible in Figure \ref{fig:mcmcMieBest1particle}.
-However, there are many solutions at different resonances in the Mie extinction curve visible in Figure \ref{fig:mcmcMieCorner1particle}.
-A better way to handle this is a log-normal distribution of particles as in \citet{2016ApJ...826..156S}.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[Single Particle Best fit for \shb]{
-	\includegraphics[width=0.5\textwidth]{best_fit_single_particle_mie.pdf}
-	\label{fig:mcmcMieBest1particle}
-	}
-\subfloat[Single Particle Posterios for \shb]{
-	\includegraphics[width=0.5\textwidth]{corner_single_particle_mie.pdf}
-	\label{fig:mcmcMieCorner1particle}
-	}
-	\caption{An initial fit to the amplitude spectrum when using a single particle.
-	The best fit nicely matches the data but has multiple solutions at the Mie scattering resonances.}
-	\label{fig:mcmcMieCorner1particle}
-	\vspace{0.1in}
-\end{figure*}
-
-I manually created a log-normal distribution of particles in Python and added up their cross sections weighted by number of particles.
-This process is slow, so I calculated it once and found  a 15th order polynomial fit to $Q_{ext}$ and evaluated this in the model.
-The resulting MCMC distribution is shown in Figure \ref{fig:mcmcMieCornerLogNorm}.
-
-\begin{figure*}[!t]
-\centering
-\subfloat[Log-Normal Best fit for \shb]{
-	\includegraphics[width=0.5\textwidth]{best_fit_lognormal_mie.pdf}
-	\label{fig:mcmcMieBestLogNorm}
-	}
-\subfloat[Log-Normal Posteriors for \shb]{
-	\includegraphics[width=0.5\textwidth]{corner_lognormal_mie.pdf}
-	\label{fig:mcmcMieCornerLogNorm}
-	}
-	\caption{An initial fit to the amplitude spectrum when using a log-normal size distribution with a $\sigma=0.5$.
-	Again, there are a few ``walkers'' that stay at large radii.}
-	\label{fig:mcmcMieCornerLogNorm}
-	\vspace{0.1in}
-\end{figure*}
-
-On closer inspection, I see that there is a local minimum for large particle radii where the $\chi^2$ begins to increase from 3~$\mu$m to 2$\mu$m.
-This is illustrated in Figure \ref{fig:localMinLargeRadii}.
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{local_min_illustration.pdf}
-\caption{A set of example Mie scattering models for example parameters for the Amplitude offset and median particle radius written as [A,r].
-The model at 2~$\mu$m is slightly worse than at 3~$\mu$m, so it traps a few walkers in the MCMC run.}\label{fig:localMinLargeRadii}
-\end{centering}
-\end{figure}
-
-When I discard walkers with very low likelihood, as done in CHIMERA, the local minima are not included since their so low probability.
-The resulting MCMC run is shown in Figure \ref{fig:localMinExcludeCorner}.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_lognormal_mie_no_lmin.pdf}
-\caption{MCMC fit when discarding points with a $\chi^2$ more than 5 times the minimum to exclude walkers that were trapped at local minima.}\label{fig:localMinExcludeCorner}
-\end{centering}
-\end{figure}
 

### 2017-02-16 ms.tex
I updated the observations section with the latest reduction pipeline and also added more detail to the description of the dynamic spectra.

@@
 
-Wavelength calibrations were performed using observations of ThAr emission lamps with the 0$\farcs$3$\times$60$\arcsec$.
-
 The images were rectified by shifting each row to match a center row in between the two sources.
@@
 We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
+An additional set of ThAr emission lamp spectra were taken at the beginning and end of the observations (preceding and following the 3$\arcsec \times 60 \arcsec$ lamp spectra) with a 0.3$\arcsec\times60\arcsec$ slit for wavelength calibration.
 % to measure pixel response and assess flexure in the instrument with telescope orientation.
@@
 These shifts were used to apply a custom flat field for every image.
-
 For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.
-{\bf [IS THIS TRUE FOR 1821?- \color{red}{YES, there were only 5 good sky frames at the end and 3 at the beginning.}]}
 
@@
 Our image rectification process described above ensures that the wavelength solution is the same for each row if the image.
-However, there are small additional shifts of the sources within the slit so another cross-correlation is performed between the sources to ensure they match before dividing the two spectra.
+However, there are small additional shifts of the sources within the slit so another shift is performed between the sources to ensure the telluric features removed when dividing the two spectra.
 
-For MORIS reduction, we used the raw files and performed aperture photometry with the IDL \texttt{aper} procedure using an aperture size of 6 pixels and a sky annulus of 8-11 pixels.
-{\bf [MORIS REDUCTION FOR 1821?]}
+%For MORIS reduction, we used the raw files and performed aperture photometry with the IDL \texttt{aper} procedure using an aperture size of 6 pixels and a sky annulus of 8-11 pixels.
 
@@
 	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).
-These spectra have not been corrected for telluric absorption or instrumental spectral response.
-The reference stars have significantly bluer spectra than the brown dwarfs.
 Bottom Panels: Dynamic spectra of each brown dwarf system.
-The dynamic spectrum for \sha\ shows no significant variability whereas there is a periodic modulation for \shb\ that decrease toward longer wavelengths.
-[MORE DESCRIPTION -- How should the reader interpret these dynamic spectra?]}
+The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
+The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
 	\label{fig:specphot}
@@
 
-Figure \ref{fig:specphot} shows the dynamic spectra (relative source brightness as a function of wavelength and time) for both targets, as well as the median spectra of the target and reference stars.
-{\sha} shows a relative flat response with shows no obvious variations at the $\lesssim1$\% level.
+Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
+Neither the reference spectra nor the brown dwarfs spectra have any corrections applied for telluric absorption or instrumental spectral response.
+The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric absorption signatures.
+The regions near 1.37~$\mu$m and 1.83~$\mu$m have significantly lower flux due to telluric water vapor absorption.
+
+Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
+{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim1$\% level.
 {\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
-The periodic signal is coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
+The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
 Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.
-
-{\bf [MORIS ANALYSIS FOR 1821?]}
 

### 2017-02-18 supplement.tex
I added an airmass figure for comparison but my code seems to multiply the residuals because they're not the same as the time series plots.

@@
 \includegraphics[width=0.5\textwidth]{best_fit_multi_terms.pdf}
-\caption{A zoom-in on on the time series of 2MASS J1821 in Figure \ref{fig:tserPhase1821} for the wavelength bin 1.08~$\mu$m.
+\caption{A zoom-in on on the time series of 2MASS J1821 for the wavelength bin 1.08~$\mu$m.
 Error bars are shown for photon and read noise.
@@
 
+\clearpage{Airmass Correlation}
+One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass.
+As I start, I used my code to look at the residuals of the single sinusoid model simultaneously with airmass.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/airmass/residuals_1p38_airmass.pdf}
+\caption{Residuals of a sinusoidal fit (with hard priors to ensure fitting out the BD modulation).
+The magnitude of the residuals is about 5$\times$ what it should be, likely an error in the code.}\label{fig:residAirmass1p38on1821}
+\end{centering}
+\end{figure}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-02-18 ms.tex
I added few changes to the analysis section describing the time series and photon errors.

@@
 Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
-{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim1$\% level.
+{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim$0.5\% level.
 {\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
@@
 In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
-We attribute this to correlated errors between wavelengths. {\bf [WHAT? HOW DETERMINED?]}
+We attribute this to correlated errors between wavelengths.
 

### 2017-02-19 supplement.tex
I added a more careful analysis of the airmass trend analysis near telluric feature.

--- 2017-02-14 supplement.tex
@@
 
+\clearpage
+\section{Airmass Correlation}
+One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass.
+As I start, I took a time series at 1.26~$\mu$m to remove find a trend-line for brown dwarf modulations.
+This is shown in Figure \ref{fig:1p26umFluxTrendFit}.
+I then remove this polynomial trend from the 1.38~$\mu$m time series to remove the brown dwarf oscillations from it.
+The residual light curve has a U shape similar to the airmass trend shown in Figure \ref{fig:1p38residAndAirmass}.
+A direct correlation plot is shown in Figure \ref{fig:residAirmass1p38corr}.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[Flux at 1.26~$\mu$m for the Trend-line]{
+	\includegraphics[width=0.5\textwidth]{images/airmass/trendline_1p26um.pdf}
+	\label{fig:1p26umFluxTrendFit}
+	}
+\subfloat[Flux at 1.38~$\mu$m and Airmass]{
+	\includegraphics[width=0.5\textwidth]{images/airmass/airmass_1p38um_resid_simult.pdf}
+	\label{fig:1p38residAndAirmass}
+	}
+	\caption{In order to investigate correlations with airmass at 1.38~$\mu$m, I first fit the 1.26~$\mu$m time series with a 10th order polynomial fit.
+	I then use the polynomial fit to remove most of the brown dwarf related oscillations in the time series at 1.38$\mu$m. The residuals show a U shape similar to the airmass table.}
+	\label{fig:airmassTimeSer1p38}
+\end{figure*}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/airmass/airmass_flux_correlation.pdf}
+\caption{Time series at 1.38$\mu$m as a function of airmass, where the brown dwarf oscillations are mostly removed as described in Figure \ref{fig:airmassTimeSer1p38}.}\label{fig:residAirmass1p38corr}
+\end{centering}
+\end{figure}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-02-19 ms.tex
Now that I verified the airmass trend in the supplementary material, I removed the we should verify this statment.
I updated the amplitude versus wavelength plots to use the lates MCMC results.

@@
 	}
-	\caption{Time series for each system with an offset added for clarity. Each wavelength bin is labeled on the right side. Alternating colors are used to distinguished the light curves with offsets.}
+	\caption{Time series for each system with an offset added for clarity.
+Each wavelength bin is labeled on the right side.
+Alternating colors are used to distinguished the light curves with offsets.
+\sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
 	\label{fig:tserPfold}
@@
 As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
-{\bf [WE SHOULD VERIFY THIS]}
 
@@
 \centering
-\subfloat[2MASS J0835 - \colorbox{red}{fit might need more work} ]{
+\subfloat[2MASS J0835]{
 	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
@@
 	}
-	\caption{Sine fit amplitude versus wavelength for each brown dwarf.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.
-2MASS J0835 shows no clear trend in wavelength, while 2MASS J1821 has a strong slope indicative of Mie-scattering particles.}
+	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
+	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}.
+The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.}
 	\label{fig:ampSpec}
@@
 [SOMETHING HERE?
-like, The data are fit] with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.
-Also shown in the figure is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}.
-The WFC3 observations were from a different epoch, with different cloud coverage.}\label{fig:ampspec1821mie}
+like, The data are fit] with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.}\label{fig:ampspec1821mie}
 \end{centering}

### 2017-02-20 supplement.tex
I updated the airmass analysis where I have not applied a linear de-trend to the time series. Now the time series at 1.38um very clearly correlates with airmass, almost perfectly.
I added a backup of the original BD amplitude spectra since I replaced the plots.

@@
 One thing to check is that the U shaped light curves near the telluric water bands are correlated to airmass.
-As I start, I took a time series at 1.26~$\mu$m to remove find a trend-line for brown dwarf modulations.
+As I start, I took a time series at 1.26~$\mu$m to remove find a trend-line for brown dwarf modulations and any other tends.
 This is shown in Figure \ref{fig:1p26umFluxTrendFit}.
@@
 \end{figure}
+
+\clearpage
+\section{Original Plots for reference}
+\begin{figure*}
+\centering
+\subfloat[2MASS J0835 - \colorbox{red}{fit might need more work} ]{
+	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
+	\label{fig:ampspec0835}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
+	\label{fig:ampspec1821}
+	}
+	\caption{Sine fit amplitude versus wavelength for each brown dwarf.
+The regions at 1.4~$\mu$m and 1.9~$\mu$m (shaded with a salmon color) are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.
+2MASS J0835 shows no clear trend in wavelength, while 2MASS J1821 has a strong slope indicative of Mie-scattering particles.}
+	\label{fig:ampSpec}
+\end{figure*}
 

### 2017-02-20 ms.tex
I addressed the in-line comments and updated a few notes about the MCMC fitting process.

@@
 Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
-The uncertainties in these curves are 0.2\% in high throughput regions of the spectrum and 0.6\% per exposure.
-The lower values are areas of high throughput and flux whereas the low values are near telluric absorption features or the edges of the spectrum.
+The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
 We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
-In these wavelength bins, the standard deviations of the points is about 2$\times$ the expected read noise and photon noise.
-We attribute this to correlated errors between wavelengths.
+In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
+We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.
 
@@
 In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
-As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and ignore these regions in our subsequent analysis.
+As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and handle it with priors on the rotational period of the brown dwarfs.
 
@@
 \begin{equation}\label{eq:cosfit}
-F(t) = A \cos(2 \pi (t - t_0)/\tau) + B t + C
+F(t) = A \cos(2 \pi (t - t_t)/\tau) + B t + C
 \end{equation}
-where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_0$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
-For our initial fits, we allowed $A$, $t_0$, $B$ and $C$ to be free parameters, but fixed $\tau$ at the literature value of rotation period to mitigate systematic biases (e.g., convergence on a period of $\sim$24 hr).
-{\bf [IS THIS A PROBLEM IF YOU IGNORE TELLURIC BANDS?
-COULD YOU CONSTRAIN THE ALLOWED PERIOD RANGE (I.E., PRIOR).
-SHOULD DO A FIT WITH PERIOD FREE TO VARY TO GET A MEASURE OF THIS QUANTITY]}
-We also imposed a prior that $A \geq 0$ so that solutions with a $\pi$ phase offset and negative amplitude were ignored.
-{\bf [THIS IS LIKELY LEADING TO OUR "DETECTION" OF 0835; NEED ANOTHER WAY TO DO THIS]}.
-We use the standard deviation of points near minimum to estimate the noise in the flux time series.
-The Levenberg-Marquardt chi-squared minimization code \texttt{mpfit} is used to fit each wavelength bin independently and propagate the errors in the flux time series to amplitude uncertainty.
+where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
+Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harminics, we impose a prior on the rotational period $\tau$ from literature values of the period \citep{2004MNRAS.354..378K,2015ApJ...799..154M}.
+For \sha\ we use a prior 3.0 $< \tau < $3.2 hr and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
+The prior for \shb\ is slightly different from the value from \citet{2004MNRAS.354..378K} because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.9 $\pm$ 0.01 hr.
+Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.
 
@@
 
-STOPPED HERE
-
 Figure \ref{fig:ampSpec} shows the best fit periodic amplitudes as a function of wavelength.
-For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.4\%$) amplitudes with a flat trend as a function of wavelength.
-2MASS J1821, on the other hand, shows a clear decreasing trend as function of wavelength.
-This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}.
-We shade the regions from 1.32 to 1.5~$\mu$m and 1.78 to 1.95~$\mu$m in Figure \ref{fig:ampSpec} because these wavelength ranges are affected by telluric water vapor absorption not fully removed by the simultaneous reference star.
-
-%    \begin{figure}[!ht]
-%    \centering
-%    \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
-%    \caption{Sine fit amplitude versus wavelength for 2MASS J1821.
-The regions at 1.4~$\mu$m and 1.9~$\mu$m are contaminated by telluric absorption so the variations can likely be due to telluric variability not corrected by the reference star.}\label{fig:DHSRes}
-%    \end{figure}
+For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.5\%$) amplitudes with a flat trend as a function of wavelength.
+\shb, on the other hand, shows a clear decreasing trend as function of wavelength.
+This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
 
@@
 \caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption.
-[SOMETHING HERE?
-like, The data are fit] with simple Mie scattering models with a log-normal particle size distribution centered at 0.1 and 0.2~$\mu$m.}\label{fig:ampspec1821mie}
+The data are fit] with simple Mie scattering models with a log-normal particle size distribution of forsterite grains.}\label{fig:ampspec1821mie}
 \end{centering}
@@
 A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
-In WISEP J0047, the wavelength trend could be fit by $\sim 0.4~\mu$m forsterite grains [WHY DO WE USE PYROXENE INSTEAD OF FORSTERITE?], similar to our characteristic particle size.
+In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, similar to our characteristic particle size.
 
@@
 
-We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with Mg-rich pyroxene grains with sub-micron sized particles.
+We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
+We use a constant n=1.67 - 0.006 $j$ index of refraction \citep{}.
 A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.
@@
 \section{Acknowledgements}
-CHIMERA retrieval makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
+MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
 Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.

### 2017-02-22 supplement.tex
I added the old IDl mie scattering model and amplitude fits.

@@
 
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/mie_fits/amp_vs_wavl_j1821_mie_sc.pdf}
+\caption{Amplitude spectrum using the \texttt{IDL} fits and holding the rotational period fixed at the literature value.
+Representative Mie-scattering models are shown for a particle size distribution of 0.1$\mu$m and 0.2$\mu$m pyroxene grains.}\label{fig:IDLmieScatterA1821}
+\end{centering}
+\end{figure}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-02-22 ms.tex
I updated the Mie scattering figure with a MCMC model fit.

@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.4\% per band) variability with no spectral dependence {\bf [THIS NEEDS TO BE CHECKED]}, while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 {\bf [PHASE VARIATION]}.
@@
 \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
-\caption{Sine fit amplitude versus wavelength excluding the wavelength regions contaminated by telluric absorption.
-The data are fit] with simple Mie scattering models with a log-normal particle size distribution of forsterite grains.}\label{fig:ampspec1821mie}
+\caption{The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}\label{fig:ampspec1821mie}
 \end{centering}

### 2017-02-22 ms.tex
I added the corner plot for the posterior distributions for the simple Mie model.
I added a reference for the forsterite index of refraction.

@@
 
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
+\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
+The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:ampspec1821mie}
+\end{centering}
+\end{figure}
+
 Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
@@
 
-We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
-We use a constant n=1.67 - 0.006 $j$ index of refraction \citep{}.
+We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite (Mg$_2$SiO$_4$) grains with sub-micron sized particles.
+We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively unchanged across the optical and near infrared \citep{scott1996forsterite}.
 A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.

### 2017-02-23 ms.tex
I updated my description of Mie scattering model fits some more.

@@
 The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
-We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon + read noise.
+We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon and read noise.
 In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
@@
 As seen in Figure~\ref{fig:tserPfold}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
-These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -3~hr and +1~hr.
+These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -2.7~hr and +1.3~hr.
 In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
@@
 where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
-Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harminics, we impose a prior on the rotational period $\tau$ from literature values of the period \citep{2004MNRAS.354..378K,2015ApJ...799..154M}.
-For \sha\ we use a prior 3.0 $< \tau < $3.2 hr and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
-The prior for \shb\ is slightly different from the value from \citet{2004MNRAS.354..378K} because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.9 $\pm$ 0.01 hr.
+Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
+For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
+The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.9 $\pm$ 0.01 hr.
 Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.
@@
 	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
-	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}.
-The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.}
+	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
+	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}
 	\label{fig:ampSpec}
@@
 
-Figure \ref{fig:ampSpec} shows the best fit periodic amplitudes as a function of wavelength.
+Figure \ref{fig:ampSpec} shows the MCMC posterior constraints for periodic amplitudes as a function of wavelength.
 For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.5\%$) amplitudes with a flat trend as a function of wavelength.
+There is low level variability but it is not seen at a constant phase.
 \shb, on the other hand, shows a clear decreasing trend as function of wavelength.
 This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
+Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
+\begin{equation}
+A  = \frac{f_R - 1}{f_R + 1}
+\end{equation}\label{eq:ampFromRatio}
+where $f_R$ is the flux ratio of the maximum over minimum flux.
 
@@
 \begin{centering}
-\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_mie_sc.pdf}
-\caption{The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}\label{fig:ampspec1821mie}
+\includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
+\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
+The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:corner1821mie}
 \end{centering}
@@
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
-\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
-The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:ampspec1821mie}
-\end{centering}
-\end{figure}
-
-Figure \ref{fig:ampspec1821mie} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
+Figure \ref{fig:ampspec1821} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
 In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
-
-\citet{2015ApJ...798L..13Y} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
-Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
-\begin{equation}
-A  = \frac{f_R - 1}{f_R + 1}
-\end{equation}\label{eq:ampFromRatio}
-where $f_R$ is the flux ratio of the maximum over minimum flux.
 
@@
 Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
-In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821mie}.
+In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821}.
 This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.

### 2017-02-23 ms.tex
more updates to the Mie scattering description and model fits.

@@
 \shb, on the other hand, shows a clear decreasing trend as function of wavelength.
-This is the same trend observed for 2MASS J1821 by HST over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
-Their maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
+
+The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
+The HST WFC3 maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
 \begin{equation}
@@
 where $f_R$ is the flux ratio of the maximum over minimum flux.
+There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
+The WFC3 spectrum is not affected by the telluric absorption, unlike the SpeX data.
+\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our Mie scattering fit.
 
@@
 We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-In this simple model, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
-We model the extinction coefficient, $Q_{ext}$ from the \texttt{IDL} Mie theory code \texttt{mie\_single.pro} \citep{grainger04} to calculate the extinction as a function of wavelength.
-We use the complex indices of refraction from \citet{dorschner95pyrox} for Mg-rich pyroxene grains (MgSiO$_3$).
+If we assume the cloud covers one hemisphere of the brown dwarf, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
+We model the extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the extinction as a function of wavelength.
+We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
+We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.
+
 For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
+The spectral dependence is therefore modeled as 
+\begin{equation}
+A_1 = B \bar{Q_{avg}}(r)
+\end{equation}
+where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$.
+
+Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.
+This model has a reduced $\chi^2$ of 0.99 and is thus consistent with the data.
+Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$ and $r$ parameters.
+The derived median particle radius of 0.164 $^{+0.012}_{-0.007}$~$\mu$m is a vary tight constraint for particle size median.
+Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
 
@@
 
-Figure \ref{fig:ampspec1821} shows the simple Mie scattering model as compared to the data for two example particle sizes of 0.1~$\mu$m and 0.2~$\mu$m.
-In these cases the reduced chi-squared values are 9.6 and 2.5 respectively, when ignoring the points within the shaded telluric contamination regions.
-
-The WFC3 amplitude spectrum is shown with the data in Figure \ref{fig:ampspec1821mie}.
-There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
-The WFC3 spectrum is not affected by the telluric absorption, unlike the SpeX data.
-\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our Mie scattering fit.
-
 A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
-In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, similar to our characteristic particle size.
+In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, a few times large than our characteristic particle size.
 
@@
 \includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
-\caption{The same data as in Figure \ref{fig:ampspec1821mie}.
+\caption{The same data as in Figure \ref{fig:ampspec1821}.
 We fit the data with a two region model that assumes the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
@@
 We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite (Mg$_2$SiO$_4$) grains with sub-micron sized particles.
-We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively unchanged across the optical and near infrared \citep{scott1996forsterite}.
 A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.

### 2017-02-23 ms.tex
I re-arranged the figures and Tables so they occur closer to their descriptions in the text.

@@
 
-This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions.
-We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
-In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
-In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
-We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
-We summarize our results in Section~\ref{sec:conclusions}.
-
-\section{Target Selection and Characterization}\label{sec:targets}
-
-We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}.
-The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$.
-We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
-Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
-
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
-This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
-Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
-There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
-2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
-This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
-\citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
-There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.
-
 \begin{deluxetable*}{lllcccccccl}
@@
 
+This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions.
+We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
+In Section~\ref{sec:obs}, we describe our monitoring observations and data reduction procedures to generate relative spectro-photometric time series.
+In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
+We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
+We summarize our results in Section~\ref{sec:conclusions}.
+
+\section{Target Selection and Characterization}\label{sec:targets}
+
+We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}.
+The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$.
+We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
+Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
+
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
+This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
+Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
+There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}). 
+2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
+This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
+\citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
+There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.
+
 To characterize the atmospheric regions probed by our observations, we analyzed previously 
@@
 The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
-{\bf [Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
+{\bf [Adam, Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
 Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here.
@@
 
-\section{Observations}\label{sec:obs}
-
-We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
-{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
-Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
-Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis.
-This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction.
-The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
-Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively.
-The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
-
-%For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
-For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
-
 \begin{deluxetable*}{lccccccccc}
-\tablecaption{Observations}\label{tab:obsParam}
+\tablecaption{Observations\label{tab:obsParam}}
 \tablewidth{0pt}
@@
 
+\section{Observations}\label{sec:obs}
+
+We observed {\sha} and {\shb} for one night each with the IRTF/SpeX (Table \ref{tab:obsParam}).
+{\sha} was observed for 4.65 hours, covering 1.5 rotation periods; {\shb} was observed for 7.47 hours, covering 1.8 rotation periods.
+Following \citet{2014ApJ...783....5S}, we used SpeX in its prism-dispersed mode, obtaining 0.9--2.4~$\micron$ spectra in a single order at low dispersion. 
+Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis.
+This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction.
+The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
+Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively.
+The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
+
+%For {\sha} our MORIS exposures were 15~sec, which was sufficient for guiding but not precision photometry.
+For {\shb}, we were able to guide on sources in the SpeX imaging channel, so we increased the $i$-band exposures to 60~sec to obtain a simultaneous $i$-band light-curve.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
+	\label{fig:specphot0835}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
+	\label{fig:specphot1821}
+	}
+	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).
+Bottom Panels: Dynamic spectra of each brown dwarf system.
+The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
+The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
+	\label{fig:specphot}
+	\vspace{0.1in}
+\end{figure*}
+
 The images were rectified by shifting each row to match a center row in between the two sources.
@@
 
-\section{Analysis}\label{sec:analysis}
-
-\subsection{Light Curves}
-
-\begin{figure*}[!t]
-\centering
-\subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{specphot_j0835.pdf}
-	\label{fig:specphot0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{specphot_j1821.pdf}
-	\label{fig:specphot1821}
-	}
-	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).
-Bottom Panels: Dynamic spectra of each brown dwarf system.
-The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
-The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
-	\label{fig:specphot}
-	\vspace{0.1in}
-\end{figure*}
-
-Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
-Neither the reference spectra nor the brown dwarfs spectra have any corrections applied for telluric absorption or instrumental spectral response.
-The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric absorption signatures.
-The regions near 1.37~$\mu$m and 1.83~$\mu$m have significantly lower flux due to telluric water vapor absorption.
-
-Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
-{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim$0.5\% level.
-{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
-The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
-Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.
-
 \begin{figure*}[!t]
@@
 
-Individual narrow-band light curves for extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
+\begin{figure*}
+\centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
+	\label{fig:ampspec0835}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
+	\label{fig:ampspec1821}
+	}
+	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
+	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
+	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}
+	\label{fig:ampSpec}
+\end{figure*}
+
+\section{Analysis}\label{sec:analysis}
+
+\subsection{Light Curves}
+
+Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
+Neither the reference spectra nor the brown dwarfs spectra have any corrections applied for telluric absorption or instrumental spectral response.
+The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric absorption signatures.
+The regions near 1.37~$\mu$m and 1.83~$\mu$m have significantly lower flux due to telluric water vapor absorption.
+
+Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
+{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim$0.5\% level.
+{\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
+The periodic signal is nearly coincident with the 4.2~hr period measured by \citet{2015ApJ...799..154M}, enabling confirmation that the signal is astrophysical rather than systematic (see \citealt{2016ApJ...826..156S}).
+Both sources exhibit some systematic features in the strong telluric absorption bands at 1.4 and 1.8~$\mu$m, likely caused by residual wavelength drifts from flexure and lower signals-to-noise.
+
+Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
 The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
@@
 
-\begin{figure*}
-\centering
-\subfloat[2MASS J0835]{
-	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j0835.pdf}
-	\label{fig:ampspec0835}
-	}
-\subfloat[2MASS J1821]{
-	\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821.pdf}
-	\label{fig:ampspec1821}
-	}
-	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
-	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
-	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}
-	\label{fig:ampSpec}
-\end{figure*}
-
 Figure \ref{fig:ampSpec} shows the MCMC posterior constraints for periodic amplitudes as a function of wavelength.
@@
 \subsection{Mie Scattering Fit}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
+\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
+The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:corner1821mie}
+\end{centering}
+\end{figure}
 
@@
 Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
-
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
-\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
-The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:corner1821mie}
-\end{centering}
-\end{figure}
 

### 2017-02-23 ms.tex
A few more clarifications in the Mie scattering fits.

@@
 In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
-As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and handle it with priors on the rotational period of the brown dwarfs.
+As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and impose priors on the rotational period of the brown dwarfs to ensure the sinusoidal fits do not fit the airmass trend.
 
@@
 For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
-The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.9 $\pm$ 0.01 hr.
+The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
 Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.
@@
 There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
-The WFC3 spectrum is not affected by the telluric absorption, unlike the SpeX data.
-\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our Mie scattering fit.
+\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
 
@@
 We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud covers one hemisphere of the brown dwarf, the amplitude of the variability is directly proportional to the opacity or $Q_{ext}$ of the particles.
-We model the extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the extinction as a function of wavelength.
+If we assume the cloud covers one hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
+We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
 We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
@@
 \begin{equation}
-A_1 = B \bar{Q_{avg}}(r)
+A = B \bar{Q_{avg}}(r)
 \end{equation}
@@
 Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.
-This model has a reduced $\chi^2$ of 0.99 and is thus consistent with the data.
+This model has a reduced $\chi^2$ of 0.99 and is consistent with the measured amplitude spectrum.
 Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$ and $r$ parameters.
-The derived median particle radius of 0.164 $^{+0.012}_{-0.007}$~$\mu$m is a vary tight constraint for particle size median.
+The derived median particle radius of $r$=0.164 $^{+0.012}_{-0.007}$~$\mu$m is a vary tight constraint for particle size median.
 Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
@@
 This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
-We assume that are each in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
+We assume for the purposes of variability that each hemisphere and layer is in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
 The flux ratio between maximum and minimum flux is then

### 2017-02-26 ms.tex
I updated the temperature spot model drawing and curves.

@@
 	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
-	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 $\pm$ 0.01 grains.}
+	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 grains.}
 	\label{fig:ampSpec}
@@
 \end{equation}
-where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
+where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations\footnote{The total amplitude is 2$A$ in our convention.
+Some other conventions describe $A$ as a ``semi-amplitude''}, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
@@
 The HST WFC3 maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
-\begin{equation}
+\begin{equation}\label{eq:ampFromRatio}
 A  = \frac{f_R - 1}{f_R + 1}
-\end{equation}\label{eq:ampFromRatio}
+\end{equation}
 where $f_R$ is the flux ratio of the maximum over minimum flux.
@@
 \end{equation}
-where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first ($T_1$ and second ($T_2$) regions respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
+where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first temperature ($T_1$) for the first and second hemispheres respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
 $\alpha_1$ and $\alpha_2$ are limited to [0,1].
@@
 With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
-The $\alpha$ values are both $<<1$, indicating that the model fits with dark patches on a small fraction of the surface.
-[I MODIFIED THIS SENTENCE; IS IT CORRECT?
-I'm a little confused about how both $\alpha$ values can be $<<1$; if one is small doesn't the other have to be large?]
+The $\alpha$ values are both $<<1$, indicating that the model fits with bright patches on a small fraction of the surface.
+The maximum to minimum contrast in this spot model is sensitive to the relative areas of these bright patches so a small difference in areas controls the maximum over minimum flux.
 
@@
 
-2MASS J1821 shows significant variability up to the 1.1\% amplitude at short wavelengths (0.8$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
+2MASS J1821 shows significant variability up to the 1.3\% amplitude (2.6\% peak-to-valley) at short wavelengths (0.9$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
 This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.

### 2017-02-26 supplement.tex
I added a little bit of text on Yang et al. 2015 I took out of the main paper.
I added more material to the supplement that will be deleted from the paper.

@@
 \clearpage
-\section{Original Plots for reference}
+\section{Original Plots and text for reference}
+
+\citet{2015ApJ...798L..13Y} also observe wavelength-dependent variability of 2MASS J1821 with the Hubble Space Telescope's (HST's) Wide Field Camera (WFC3) over 2 visits of 3 orbits each.
+
 \begin{figure*}
@@
 \end{figure}
+
+\subsection{Old Time series Fit}
+Each of the light curves were fit to a simple sinusoidal model:
+\begin{equation}\label{eq:cosfit}
+F(t) = A \cos(2 \pi (t - t_t)/\tau) + B t + C
+\end{equation}
+where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations\footnote{The total amplitude is 2$A$ in our convention.
+Some other conventions describe $A$ as a ``semi-amplitude''}, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
 

### 2017-02-28 ms.tex
I updated the formula and the 2MASS 1821 spectrum to be consistent with the latest time series analysis.

@@
 
-Each of the light curves were fit to a simple sinusoidal model:
+Each of the light curves were fit to a double sinusoidal model:
 \begin{equation}\label{eq:cosfit}
-F(t) = A \cos(2 \pi (t - t_t)/\tau) + B t + C
+\begin{split}
+F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + \\
+B t + C + D a(t)
+\end{split}
 \end{equation}
-where $F(t)$ is the relative flux as a function of time $t$, $A$ is the amplitude of periodic variations\footnote{The total amplitude is 2$A$ in our convention.
-Some other conventions describe $A$ as a ``semi-amplitude''}, $t_t$ is the time of maximum periodic flux, $\tau$ is period of the variations, and $B$ and $C$ are linear terms describing any baseline trend.
+where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ is the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, and $B$, $C$ and $D$ are terms describing the baseline trend and $a(t)$ is the airmass as a function of time.
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.

### 2017-03-01 supplement.tex
I copied the old time series plots here for comparison.

@@
 
+\subsection{Old Time Series}
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{images/tser/2mass_0835_t_series.png}
+	\label{fig:tserPhase0835}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{images/tser/2mass_1821_t_series.png}
+	\label{fig:tserPhase1821}
+	}
+	\caption{Time series for each system with an offset added for clarity.
+Each wavelength bin is labeled on the right side.
+Changing colors are used to distinguished the light curves with offsets.
+\sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
+	\label{fig:tserPfold}
+\end{figure*}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-03-04 ms.tex
I replaced the time series plots with a Python version that also shows the maximum likelihood models.
I adjusted the descriptions of the Mie scattering fits.

@@
 Each wavelength bin is labeled on the right side.
-Alternating colors are used to distinguished the light curves with offsets.
+Changing colors are used to distinguished the light curves with offsets.
 \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
@@
 	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
-	 The amplitude spectrum for \shb\ is fit with a simple Mie scattering models for a log-normal particle size distribution of spherical forsterite grains with a best-fit radius of 0.17 grains.}
+	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
+	 \sha\ is consistent with a zero amplitude flat amplitude model which essentially puts no constraints on the particle size distribution.
+	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
 	\label{fig:ampSpec}
@@
 
-We model the wavelength dependence of 2MASS 1821 as an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud covers one hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
+We model the wavelength dependence of \sha\ and \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
+If we assume the cloud covers one longitudinal hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
@@
 where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$.
+When fitting the amplitude spectra to our Mie model, we impose a prior on the maximum median particle size radius ($0 \mu m < r < 5 \mu m$).
 
+For \sha\ we find that since no significant variability is detected that the particle size is unconstrained over the prior of $0 \mu < r < 5 \mu m$).
+We show the maximum likelihood particle radius of 2.3 $\mu$m
 Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.

### 2017-03-06 ms.tex
I adjusted the baseline in the equation from additive to multiplicative times a 1 + variation which makes very little difference. I updated the relevant time series and amplitude spectra plots.
I added the original light curves to an appendix for the interested reader.

@@
 \sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
-	\label{fig:tserPfold}
+	\label{fig:tserDetrend}
 \end{figure*}
@@
 
-Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserPfold}.
+Individual narrow-band light curves are extracted for each target in 25 spectral bins of width 0.060~$\mu$m; these are shown in Figure~\ref{fig:tserDetrend}.
+The baseline trends (which scale linearly with time and linearly with airmass) have been removed from Figure~\ref{fig:tserDetrend}, but the original light curves can be viewed in Figure \ref{fig:tserNoDetrend}.
 The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
@@
 
-As seen in Figure~\ref{fig:tserPfold}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
+As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
 These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -2.7~hr and +1.3~hr.
-In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
 As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and impose priors on the rotational period of the brown dwarfs to ensure the sinusoidal fits do not fit the airmass trend.
@@
 \begin{split}
-F(t) = A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + \\
-B t + C + D a(t)
+F(t) = \left( A_1 \cos(2 \pi (t - t_1)/\tau) + A_2 \cos(4 \pi (t - t_2)/\tau) + 1\right) \\
+\times (B t + C + D a(t))
 \end{split}
@@
 
-%\appendix
+\appendix
+
+\section{Original Light Curves}
+
+We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}.
+The linear baseline terms as a function of time and airmass in Equation \ref{eq:cosfit} fit the baseline variations not due to the brown dwarf variations.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{2mass_0835_tser_no_detrend.pdf}
+	\label{fig:tserPhase0835NoDetrend}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{2mass_1821_tser_no_detrend.pdf}
+	\label{fig:tserPhase1821NoDetrend}
+	}
+	\caption{Time series for each system with an offset added for clarity, as in Fig \ref{fig:tserDetrend}, but in this case showing the raw light curves without de-trending.
+	Each wavelength bin is labeled on the right side.
+Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near telluric absorption features at 1.38$\mu$m and 1.87$\mu$m.}
+	\label{fig:tserNoDetrend}
+\end{figure*}
 

### 2017-03-07 ms.tex
I updated the plots and descriptions of the priors for looser priors so they're not driving the period too much.

@@
 	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
-	 \sha\ is consistent with a zero amplitude flat amplitude model which essentially puts no constraints on the particle size distribution.
+	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
 	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
@@
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-For \sha\ we use a prior 3.0 $< \tau < $3.2 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.8 $< \tau <$ 4.0 hr.
-The prior for \shb\ is slightly different from the value from \citet{2015ApJ...799..154M}(4.2 hr) because it came from a fit in a clear region of the time series (at 1.08~$\mu$m) where a double sinusoidal fit resulted in a period of 3.90 $\pm$ 0.01 hr.
+For \sha\ we use a prior 2.6 $< \tau < $3.6 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.7 $< \tau <$ 4.7 hr from \citet{2015ApJ...799..154M}, using wide 0.5 hr priors around the measured values.
+These priors are used to ensure that the sinusoidal fits to not fit the airmass trends with time.
 Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.

### 2017-03-08 ms.tex
I updated the text to reflect the latest time series model fits.

@@
 As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
-These variations are approximately sinusoidal, although we detect ``double-hump'' structures with slight downturns in flux at peak amplitudes around -2.7~hr and +1.3~hr.
-As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and impose priors on the rotational period of the brown dwarfs to ensure the sinusoidal fits do not fit the airmass trend.
+These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr.
+The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short wavelengths and near-zero amplitude at the longest wavelengths.
 
@@
 \end{equation}
-where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ is the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, and $B$, $C$ and $D$ are terms describing the baseline trend and $a(t)$ is the airmass as a function of time.
+where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are terms describing the baseline trend.
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-For \sha\ we use a prior 2.6 $< \tau < $3.6 hr from \citet{2004MNRAS.354..378K} and for \shb\ we use 3.7 $< \tau <$ 4.7 hr from \citet{2015ApJ...799..154M}, using wide 0.5 hr priors around the measured values.
-These priors are used to ensure that the sinusoidal fits to not fit the airmass trends with time.
-Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ to make sure there are no 2$\pi$ degeneracies in the fit.
+For \sha\ we use a prior 2.6 $< \tau < $3.6 hr and for \shb\ we use 3.7 $< \tau <$ 4.7 hr.
+Each of these ranges are $\pm$0.5 hr from the literature values \citep[3.1,4.2][]{2004MNRAS.354..378K,2015ApJ...799..154M}.
+These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for \shb\ but narrow enough to ensure that the sinusoidal fits do not fit the airmass trends with time.
+Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to make sure there are no 2$\pi$ degeneracies in the fit.
 
@@
 For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.5\%$) amplitudes with a flat trend as a function of wavelength.
-There is low level variability but it is not seen at a constant phase.
+There is possible low level variability for the wavelengths long than 2.1$\mu$m.
 \shb, on the other hand, shows a clear decreasing trend as function of wavelength.
+In neither case, is there any statistically significant wavelength dependence to the time of maximum variation $t_1$.
 

### 2017-03-08 ms.tex
I removed the spot model section and updated the conclusions section.

@@
 We model the wavelength dependence of \sha\ and \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud covers one longitudinal hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
+If we assume the cloud is confined to one hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
@@
 When fitting the amplitude spectra to our Mie model, we impose a prior on the maximum median particle size radius ($0 \mu m < r < 5 \mu m$).
+Beyond 5~$\mu$m the models are essentially unchanged with median particle radius.
 
-For \sha\ we find that since no significant variability is detected that the particle size is unconstrained over the prior of $0 \mu < r < 5 \mu m$).
-We show the maximum likelihood particle radius of 2.3 $\mu$m
+For \sha\ we find that since no significant variability is detected that the particle size is unconstrained over the prior of $0~\mu m < r < 5~\mu m$.
+We show the maximum likelihood model which has a near-zero amplitude.
+For \shb\ we find that the median particle radius is better constrained.
 Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.
@@
 
-\subsection{Spot Model Fit}\label{sec:spotModel}
-
 \begin{figure}
@@
 
-Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
-In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821}.
-This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
-We assume for the purposes of variability that each hemisphere and layer is in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
-The flux ratio between maximum and minimum flux is then
-\begin{equation}
-f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
-\end{equation}
-where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first temperature ($T_1$) for the first and second hemispheres respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
-$\alpha_1$ and $\alpha_2$ are limited to [0,1].
-Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
-\begin{equation}\label{eq:twoTempAmpAlphas}
-A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
-\end{equation}
-If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
-If we ignore projection effects for small area coverage, the effective temperature is 
-\begin{equation}
-\sigma T_{eff}^4 \approx (\alpha_1 + \alpha_2) \sigma T_1^4 + (2 - \alpha_1 - \alpha_2) \sigma T_2^4
-\end{equation}
-where $\sigma$ is the Stephan-Boltzmann constant.
-
-In the model fitting, we found a strong correlation between $\alpha_1$ and $\alpha_2$.
-Therefore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
-\begin{equation}\label{eq:twoTempAmp}
-A_\lambda = \frac{\beta \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(2 \alpha_1 - \beta \right) B_\lambda(T_1) + \left(2 - 2 \alpha_1 + \beta \right) B_\lambda(T_2)}.
-\end{equation}
-
-We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
-To be close to the effective temperature of the brown dwarf, we fix $T_1$ to be 1600 K and only vary $T_2$.
-This model is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a reduced chi-squared, $\bar{\chi}^2$ = 15.
-Next, we attempt a model where we allow $\alpha_1$ and $\alpha_2$ to be free parameters and restrict the temperature limits of the two regions to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
-The best fit model has $T_{eff} \approx $1590 K and $\bar{\chi}^2$=2.1, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
-Finally, we consider a model where all four parameters, $\alpha_1$, $\alpha_2$, $T_1$ and $T_2$ are all free.
-With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
-The $\alpha$ values are both $<<1$, indicating that the model fits with bright patches on a small fraction of the surface.
-The maximum to minimum contrast in this spot model is sensitive to the relative areas of these bright patches so a small difference in areas controls the maximum over minimum flux.
-
-The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly larger than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
-Therefore, we suspect that hot or cold spots on the surface are a less plausible explanation of the variability of 2MASS J1821 than a heterogenous temperature distribution.
-
-\vspace{0.2in}
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
-\caption{The same data as in Figure \ref{fig:ampspec1821}.
-We fit the data with a two region model that assumes the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
-\end{centering}
-\end{figure}
-% Command used:
-% plot_rad_vs_wavl,/amp,/shadetell,custxrange=[0.8,2.5],custyrange=[-0.1,1.9],/showYang,/twoTreg
-
 \section{Conclusions}\label{sec:conclusions}
@@
 We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
-These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
+These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
 We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
@@
 
-2MASS J1821 shows significant variability up to the 1.3\% amplitude (2.6\% peak-to-valley) at short wavelengths (0.9$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
+2MASS J1821 shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
 This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
@@
 
-We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite (Mg$_2$SiO$_4$) grains with sub-micron sized particles.
-A log-normal particle size distribution with a median of 0.2$\mu$m fits the data with a $\bar{\chi^2}$ of 2.5.
-We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
-The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperature differences.
-Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.
+We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
+A log-normal particle size distribution with a median of 0.16$\mu$m fits the data with a $\chi^2$ per degree of freedom of 0.99.
+Continued ground-based surveys such as with SpeX on IRTF will provide powerful constraints on dust particle sizes in other brown dwarf atmospheres which can have different temperature profiles and cloud altitudes.
 

### 2017-03-08 ms.tex
I updated the appendix.

@@
 We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}.
-The linear baseline terms as a function of time and airmass in Equation \ref{eq:cosfit} fit the baseline variations not due to the brown dwarf variations.
+The original light curves show significant variations as a function of time and airmass.
+Our sinusoidal model using Equation \ref{eq:cosfit} is shown for each of the light curves in Figure \ref{fig:tserNoDetrend}.
+For \ref{fig:tserDetrend} we remove the fit the baseline variations to show the astrophysical modulations due to brown dwarf rotation.
 

### 2017-03-12 ms.tex
I updated the particle size distributions and descriptions with the latest log-normal free-sigma parameter models.

@@
 	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
-	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
+	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.}
 	\label{fig:ampSpec}
@@
 \includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
-\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb.
-The model includes an amplitude offset, $B$, (to account for areal coverage) and a median particle radius, $r$.}\label{fig:corner1821mie}
+\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb\ assuming a forsterite composition.
+The model includes an amplitude offset, $B$, (to account for areal coverage), a median particle radius, $r$ and a scale parameter $\sigma$.
+The upper right inset plot shows the log-normal particle size distribution in blue for samples drawn from the MCMC results.
+The red curve is the maximum likelihood log-normal particle size distribution.}\label{fig:corner1821mie}
 \end{centering}
@@
 \begin{equation}
-A = B \bar{Q_{avg}}(r)
+A_1 = B \bar{Q_{avg}}(r)
 \end{equation}
 where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$.
-When fitting the amplitude spectra to our Mie model, we impose a prior on the maximum median particle size radius ($0 \mu m < r < 5 \mu m$).
+When fitting the amplitude spectra to our Mie model, we impose a prior on the median particle size radius ($0 \mu m < r < 5 \mu m$).
 Beyond 5~$\mu$m the models are essentially unchanged with median particle radius.
@@
 We show the maximum likelihood model which has a near-zero amplitude.
-For \shb\ we find that the median particle radius is better constrained.
-Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.16~$\mu$m grains.
-This model has a reduced $\chi^2$ of 0.99 and is consistent with the measured amplitude spectrum.
-Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$ and $r$ parameters.
-The derived median particle radius of $r$=0.164 $^{+0.012}_{-0.007}$~$\mu$m is a vary tight constraint for particle size median.
+For \shb\ we find that the amplitude spectrum is well fit by a Mie scattering model and the median particle radius is better constrained.
+Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.28~$\mu$m grains.
+This model has a reduced $\chi^2$ of 1.08 and is consistent with the measured amplitude spectrum.
+Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$, $r$ and $\sigma$ parameters.
+The derived median particle radius is $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for our assumptions of optically thin clouds and a log-normal particle size distribution.
 Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
+Future work could include full modeling of atmospheres with more complex spatial distributions and compositions.
 

### 2017-03-12 ms.tex
I updated the abstract and conclusions with the latest particle radius constraints.

@@
 We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
-{\bf [PHASE VARIATION]}.
-The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of sub-micron dust particles, although this model becomes too strong at short wavelengths.
-An alternate model based on surface hot spots requires implausibly large temperature variations.
+We detect no statistically significant variation across the wavelengths for the phase of maximum flux variation.
+The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of 0.24 $\mu$m dust particles.
 The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
@@
 Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
-Future work could include full modeling of atmospheres with more complex spatial distributions and compositions.
+Future work could include full modeling of atmospheres with more complex spatial distributions, grain geometries and compositions.
 
@@
 We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
-A log-normal particle size distribution with a median of 0.16$\mu$m fits the data with a $\chi^2$ per degree of freedom of 0.99.
+A log-normal particle size distribution fits the data with a median grain radius of 0.24 $^{+0.05}_{-0.07}$ $\mu$m.
 Continued ground-based surveys such as with SpeX on IRTF will provide powerful constraints on dust particle sizes in other brown dwarf atmospheres which can have different temperature profiles and cloud altitudes.

### 2017-03-12 ms.tex
I clarified the log-normal distribution in the abstract.

@@
 We detect no statistically significant variation across the wavelengths for the phase of maximum flux variation.
-The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction of 0.24 $\mu$m dust particles.
+The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
 The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.

### 2017-03-13 ms.tex
I added a few more wording changes and discussions in the analysis and conclusions after re-doing the MCMC fits.

@@
 For \sha\ we use a prior 2.6 $< \tau < $3.6 hr and for \shb\ we use 3.7 $< \tau <$ 4.7 hr.
-Each of these ranges are $\pm$0.5 hr from the literature values \citep[3.1,4.2][]{2004MNRAS.354..378K,2015ApJ...799..154M}.
+Each of these ranges are $\pm$0.5 hr from the literature values \citep[3.1,4.2hr][]{2004MNRAS.354..378K,2015ApJ...799..154M}.
 These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for \shb\ but narrow enough to ensure that the sinusoidal fits do not fit the airmass trends with time.
@@
 We model the wavelength dependence of \sha\ and \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud is confined to one hemisphere of the brown dwarf, the amplitude of the variability ($A$) is directly proportional to the opacity of the particles.
+If we assume the cloud is confined to one hemisphere of the brown dwarf, the amplitude of the variability ($A_1$) is directly proportional to the opacity of the particles.
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
@@
 \begin{equation}
-A_1 = B \bar{Q_{avg}}(r)
+A_1 = B \bar{Q_{avg}}(r,\sigma)
 \end{equation}
-where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$.
+where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r,\sigma)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$ and scale parameter $\sigma$.
 When fitting the amplitude spectra to our Mie model, we impose a prior on the median particle size radius ($0 \mu m < r < 5 \mu m$).
@@
 This model has a reduced $\chi^2$ of 1.08 and is consistent with the measured amplitude spectrum.
+
 Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$, $r$ and $\sigma$ parameters.
 The derived median particle radius is $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for our assumptions of optically thin clouds and a log-normal particle size distribution.
-Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in median particle size.
+We show the maximum likelihood particle size distribution in the inset of Figure \ref{fig:corner1821mie} as well as a series of other possible distributions from the MCMC fitting.
+Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in particle sizes.
 Future work could include full modeling of atmospheres with more complex spatial distributions, grain geometries and compositions.
@@
 A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
-In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, a few times large than our characteristic particle size.
+In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.
 

### 2017-03-15 ms.tex
I added a sentence about phase offsets in the conclusions.
I made some minor word changes to the abstract and intro.

@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.3\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
-We detect no statistically significant variation across the wavelengths for the phase of maximum flux variation.
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
+We detect no statistically phase variations with wavelength.
 The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
@@
 The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
-Wavelength-dependent phase variance in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
+Wavelength-dependent phase variations in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
 Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.
@@
 \tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
-A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
+A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.
+\textcolor{red}{\bf I get 8.0$\times 10^{-3} Pv\sin(i)$.}}
 \tablenotetext{b}{Tentative period.}
@@
 The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.
+We find no statistically significant phase offsets in the light curves for \sha\ nor \shb\ from wavelength to wavelength.
 

### 2017-03-15 ms.tex
I added a reference to Hiranaka's results on the particle size distribution which are similar to our constraints for 2MASS 1821+1414

@@
 A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
-In WISEP J0047, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.
+In WISEP J0047+6803, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.
+
+\citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
+They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
+Our median particle radius of $r$=0.24 $\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened stars in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
 

### 2017-05-18 ms.tex
added a reference to the new paper Vos et al. 2017.

@@
 These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr.
-The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short wavelengths and near-zero amplitude at the longest wavelengths.
+The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 
+wavelengths and near-zero amplitude at the longest wavelengths.
+A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
+Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
 

### 2017-05-19 ms.tex
Updates from ShareLaTeX
added a short description of the spot models and some preliminary figures from Theodora.

@@
 
+\begin{figure*}
+\begin{centering}
+\includegraphics[width=0.45\textwidth]{e_1821_096_map.png}\\
+\includegraphics[width=0.45\textwidth]{e_1821_120_map.png}
+\hspace{0.2in}
+\includegraphics[width=0.45\textwidth]{e_1821_126_map.png}
+\caption{{\it Aeolus} maps of the light curves at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.}\label{fig:spotModel}
+\end{centering}
+\end{figure*}
+
 For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
@@
 
-\begin{figure}
-\begin{centering}
-\includegraphics[width=0.4\textwidth]{temperature_drawing.pdf}
-\caption{A simple two region model with two different temperatures and different areal fractions for longitudes 0\degree\ and 180\degree.}\label{fig:tdiffschem}
-\end{centering}
-\end{figure}
+\section{Spot Distribution}
+\newcommand{\maxSpots}{\#?}
+We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.
+We allow up to \maxSpots\ across the sphere of the brown dwarf, all with a constant temperature contrast.
+We set the ``background'' at the measured effective temperature of 1614 K.
+
+Figure \ref{fig:spotModel} shows the spot models fit to the light curve at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.
+At all three wavelengths, the fitted brightness temperature contrast is around 50 K above the background.
+These higher temperature spots are indicative of either holes in clouds or regions of elevated temperature.
+The distribution of spots changes with wavelength, suggesting that the distribution of clouds or temperatures is complex.
+The low amplitude and signal to noise of the light curves makes it difficult to put tight constraints on the spot distribution.
 

### 2017-05-22 supplement.tex
Added parameter some exploration plots as well as some older time series.

@@
 
+In the regions of strong telluric absorption, the variability pattern changes, with a U-shaped profile minimized at $-$1~hr.
+
+\subsection{Old Time Series and Fits}
+
+These sinusoidal fits had very tight priors on the rotation period (3.0 to 3.2 hr) and (3.8 to 4.0 hr), not quite consistent with \citep[][4.2hr]{2015ApJ...799..154M}.
+\begin{figure*}[!t]
+\centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{images/tser/2mass_0835_t_series.pdf}
+	\label{fig:tserPhase0835}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{images/tser/2mass_1821_t_series.pdf}
+	\label{fig:tserPhase1821}
+	}
+	\caption{Time series for each system with an offset added for clarity.
+	Each wavelength bin is labeled on the right side.
+Changing colors are used to distinguished the light curves with offsets.
+\sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
+	\label{fig:tserDetrend}
+\end{figure*}
+
+\begin{figure*}
+\centering
+\subfloat[2MASS J0835]{
+	\includegraphics[width=0.5\textwidth]{images/old_tight_period_constraints/amp_vs_wavl_j0835.pdf}
+	\label{fig:ampspec0835}
+	}
+\subfloat[2MASS J1821]{
+	\includegraphics[width=0.5\textwidth]{images/old_tight_period_constraints/amp_vs_wavl_j1821.pdf}
+	\label{fig:ampspec1821}
+	}
+	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
+	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
+	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
+	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
+	 \shb\ is shown with the best fit median particle size of 0.17 $\mu$m grains.}
+	\label{fig:ampSpec}
+\end{figure*}
+
+As this pattern aligns with the airmass trend over the sequence of observations, we attribute this pattern to systematic effects and impose priors on the rotational period of the brown dwarfs to ensure the sinusoidal fits do not fit the airmass trend.
+
+\section{Spot Model Fit}\label{sec:spotModel}
+
+Another simple model we attempt assumes  that the brown dwarf spectral variability has to do with a non-uniform temperature distribution on the brown dwarf in the same way that starspots modulate the brightness of hydrogen burning stars as they spin.
+In Figure \ref{fig:ampspec1821tdiff}, we fit the same amplitude spectrum as in Figure \ref{fig:ampspec1821}.
+This time we model the data with two temperature regions as shown in Figure \ref{fig:tdiffschem}, with two opposite longitudes of the planet at the brightness minimum and maximum.
+We assume for the purposes of variability that each hemisphere and layer is in local thermodynamic equilibrium (LTE) so that the flux is proportional to the Planck function times the areal coverage.
+The flux ratio between maximum and minimum flux is then
+\begin{equation}
+f_{R,\lambda} = \frac{\alpha_1 B_\lambda(T_1) + (1-\alpha_1) B_\lambda(T_2)}{\alpha_2 B_\lambda(T_1) + (1-\alpha_2) B_\lambda(T_2)}
+\end{equation}
+where $\alpha_1$ and $\alpha_2$ are the areal fractions of the first temperature ($T_1$) for the first and second hemispheres respectively, $B_\lambda$ is the Planck function, and $T_1$ and $T_2$ are the temperatures of the two regions.
+$\alpha_1$ and $\alpha_2$ are limited to [0,1].
+Using equation \ref{eq:ampFromRatio}, the amplitude then becomes
+\begin{equation}\label{eq:twoTempAmpAlphas}
+A_\lambda = \frac{\left(\alpha_1 - \alpha_2 \right) \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(\alpha_1 + \alpha_2\right) B_\lambda(T_1) + \left(2 - \alpha_1 - \alpha_2\right) B_\lambda(T_2)}.
+\end{equation}
+If the temperature difference is significant so that one Planck function is in the Wien's limit while the other is in the Rayleigh Jeans tail, the cooler temperature essentially becomes black and the contrast approaches a constant for short wavelengths.
+If we ignore projection effects for small area coverage, the effective temperature is 
+\begin{equation}
+\sigma T_{eff}^4 \approx (\alpha_1 + \alpha_2) \sigma T_1^4 + (2 - \alpha_1 - \alpha_2) \sigma T_2^4
+\end{equation}
+where $\sigma$ is the Stephan-Boltzmann constant.
+
+In the model fitting, we found a strong correlation between $\alpha_1$ and $\alpha_2$.
+Therefore we re-parameterized with $\beta = \alpha_1 - \alpha_2$, so that $\alpha_2 = \alpha_1 - \beta$.
+\begin{equation}\label{eq:twoTempAmp}
+A_\lambda = \frac{\beta \left(B_\lambda(T_1) - B_\lambda(T_2) \right)}{\left(2 \alpha_1 - \beta \right) B_\lambda(T_1) + \left(2 - 2 \alpha_1 + \beta \right) B_\lambda(T_2)}.
+\end{equation}
+
+We start by considering a two-faced model where $\alpha_1$ = 1 and $\alpha_2$ = 0, so that the two halves of the brown dwarf are different temperatures.
+To be close to the effective temperature of the brown dwarf, we fix $T_1$ to be 1600 K and only vary $T_2$.
+This model is a poor match to the data, also shown in Figure \ref{fig:ampspec1821tdiff} with a reduced chi-squared, $\bar{\chi}^2$ = 15.
+Next, we attempt a model where we allow $\alpha_1$ and $\alpha_2$ to be free parameters and restrict the temperature limits of the two regions to [1300,2500] to ensure that the final effective temperature is close to the measured 1600 K \citep{gagne2015banyan7}.
+The best fit model has $T_{eff} \approx $1590 K and $\bar{\chi}^2$=2.1, but pushes to the edges of our prior with $T_1$ = 2500 K and $T_2$ = 1300 K.
+Finally, we consider a model where all four parameters, $\alpha_1$, $\alpha_2$, $T_1$ and $T_2$ are all free.
+With these loose constraints, the model fits the data with $\bar{\chi}^2$ = 1.3, consistent with the data, but not with the effective temperature ($T_{eff}$ = 850 K).
+The $\alpha$ values are both $<<1$, indicating that the model fits with bright patches on a small fraction of the surface.
+The maximum to minimum contrast in this spot model is sensitive to the relative areas of these bright patches so a small difference in areas controls the maximum over minimum flux.
+
+The temperature contrasts in these models (with the exception of the two-faced model which poorly matches the data) are significantly larger than the expected 50 K horizontal temperature variations expected in circulation models \citep{showman2013bdgpDynamics}.
+Therefore, we suspect that hot or cold spots on the surface are a less plausible explanation of the variability of 2MASS J1821 than a heterogenous temperature distribution.
+
+\vspace{0.2in}
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_t_diff.pdf}
+\caption{The same data as in Figure \ref{fig:ampspec1821}.
+We fit the data with a two region model that assumes the effective temperature of the brown dwarf and a cooler temperature.}\label{fig:ampspec1821tdiff}
+\end{centering}
+\end{figure}
+% Command used:
+% plot_rad_vs_wavl,/amp,/shadetell,custxrange=[0.8,2.5],custyrange=[-0.1,1.9],/showYang,/twoTreg
+
+\section{Old Conclusions}
+These brown dwarfs have temperatures near the condensation temperatures of MgSiO$_3$ and Mg$_2$SiO$_4$.
+
+We also model the wavelength dependence with a spotted surface model with two different Planck functions covering different spatial regions.
+The two temperature region model can fit variability amplitude spectrum well within errors, but gives implausible temperature differences.
+Therefore, we favor the Mie scattering model as a better explanation for the variability amplitude spectrum.
+
+\section{Re-visiting The $\Delta$ T models}
+
+After Theodora's questions, I decided to re-visit the spot models. I went back to Equation \ref{eq:twoTempAmp} and just plotted some example models as a function of different parameters.
+
+\begin{figure*}[!t]
+\centering
+\subfloat[T$_1$ Parameter]{
+	\includegraphics[width=0.5\textwidth]{images/two_temp_models/temp_varied.pdf}
+	\label{fig:twoTempModelTvar}
+	}
+\subfloat[$\beta$ Parameter]{
+	\includegraphics[width=0.5\textwidth]{images/two_temp_models/beta_varied.pdf}
+	\label{fig:twoTempModelBetavar}
+	}\\
+\subfloat[$\alpha_1$ Parameter]{
+	\includegraphics[width=0.5\textwidth]{images/two_temp_models/alpha_1_varied.pdf}
+	\label{fig:twoTempModelAlphavar}
+	}
+	\caption{Variations in model parameters compared to the data, with points near the expected spot coverages and temperature contrasts.}
+	\label{fig:twoTempModelParamsVar}
+	\vspace{0.1in}
+\end{figure*}
+
+\begin{figure*}[!t]
+\centering
+\subfloat[T$_1$ Parameter]{
+	\includegraphics[width=0.5\textwidth]{images/two_temp_models/extreme_temp_varied.pdf}
+	\label{fig:twoTempModelTvarE}
+	}
+\subfloat[$\beta$ Parameter]{
+	\includegraphics[width=0.5\textwidth]{images/two_temp_models/extreme_beta_varied.pdf}
+	\label{fig:twoTempModelBetavarE}
+	}\\
+\subfloat[$\alpha_1$ Parameter]{
+	\includegraphics[width=0.5\textwidth]{images/two_temp_models/extreme_alpha_1_varied.pdf}
+	\label{fig:twoTempModelAlphavarE}
+	}
+	\caption{Variations in model parameters compared to the data, with more extreme parameters that best-fit the data.}
+	\label{fig:twoTempModelParamsVarE}
+	\vspace{0.1in}
+\end{figure*}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-05-24 ms.tex
I added a short note to explain the bottom panels with time of maximum variation.

@@
 
-\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J. Gizis\altaffilmark{4}, T. Karalidi\altaffilmark{1}, \and J. Teske\altaffilmark{5}}
+\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, T. Karalidi\altaffilmark{1}, J.\ E.\  Gizis\altaffilmark{4},  \and J. Teske\altaffilmark{5}}
 
@@
 	}
-	\caption{Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
+	\caption{{\it Top Panels: }Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
 	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
@@
 	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
-	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.}
+	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
+	 {\it Bottom Panels:} The time of maximum variation $t_1$ for each brown dwarf shows no clear trend with wavelength.
+	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.}
 	\label{fig:ampSpec}

### 2017-05-24 supplement.tex
added some discussion of optical depth of dust.

@@
 
+\clearpage
+\section{Optical Depth of Possible Haze Clouds}
+
+\subsection{Lower limit Optical Depth}
+Let's assume that there is a haze layer that covers 50\% of \shb's surface (ie. one hemisphere).
+This will give us a lower limit on the optical depth to explain the variability amplitudes.
+The flux after extinction is 
+\begin{equation}
+F_\mathrm{obs} = F_\mathrm{d} e^{-\tau}
+\end{equation}
+where $F_\mathrm{obs}$ is the observed flux, $F_\mathrm{d} $ is the flux from a deep layer underneath the haze and $\tau$ is the optical depth of the haze.
+Under our assumption that the haze covers one hemisphere, the brighter hemisphere will have a flux $F_\mathrm{obs}  = F_\mathrm{d}$ so the maximum to minimum flux ratio is
+\begin{equation}
+f_R = e^{\tau}
+\end{equation}
+or
+\begin{equation}
+\tau = \ln{(f_R)}
+\end{equation}
+From the main paper, the relationship between variability amplitude and $f_R$ is
+\begin{equation}\label{eq:ampFromRatio}
+A  = \frac{f_R - 1}{f_R + 1}
+\end{equation}
+so
+\begin{equation}
+f_R = \frac{A + 1}{1 - A}.
+\end{equation}
+so
+\begin{equation}
+\tau = \ln{\left(\frac{A+1}{1 - A}\right)}
+\end{equation}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/optical_depth/tau_plot_lower.pdf}
+\caption{Optical depth if the haze layer is assumed to cover a full hemisphere to explain the flux variations.}\label{fig:opticalDepthLower}
+\end{centering}
+\end{figure}
+
+\subsection{Optical Depth for Assumed Spot Contrast}
+
 %If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.

### 2017-05-25 ms.tex
adjusted the quickk inclination calculations.

@@
 \startdata
-\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
-\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 83 & 5-10 \\
+\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 17-26 & 1-5 \\
+\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 54-90 & 5-10 \\
 \enddata
-\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.2$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
-A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.
-\textcolor{red}{\bf I get 8.0$\times 10^{-3} Pv\sin(i)$.}}
+\tablenotetext{a}{Estimated inclination angle $i$, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i} / R$, where $P$ is in hours and $v\sin{i}$ is in km/s and $R$ is assumed to be 0.8 to 1.2 $\times$ the equatorial radius of Jupiter.
+A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
 \tablenotetext{b}{Tentative period.}

### 2017-05-27 supplement.tex
added some more notes about the optical depth calculated from spot contrast.

@@
 
-\subsection{Lower limit Optical Depth}
-Let's assume that there is a haze layer that covers 50\% of \shb's surface (ie. one hemisphere).
+\subsection{Hemispheric Coverage Assumption}\label{sec:hemisphOpticalDepth}
+Let's assume that there is a haze layer that covers 50\% of \shb's surface (ie.
+one hemisphere) and that the maximum and minimum fluxes represent when this cloudy hemisphere is facing towards or away from our observed line of sight.
 This will give us a lower limit on the optical depth to explain the variability amplitudes.
@@
 
+\clearpage
 \subsection{Optical Depth for Assumed Spot Contrast}
+
+While section \ref{sec:hemisphOpticalDepth} represents a lower limit estimate for the optical depth needed to explain the variability amplitudes, smaller spots/clouds will produce higher contrasts and therefore will need higher optical depths.
+In this section, we also include an estimate based on the spot coverage maps.
+The {\it Aeolus} code \citep{2015ApJ...814...65K} finds a near-constant spot brightness contrast for all wavelengths of around 50 K.
+We start by calculating the flux constrast for a brightness temperature difference of 50 K in the opt panel of Figure \ref{fig:opticalDepthAeolusSpot}.
+
+If we assume that this spot contrast is due to extinction by dust, then the optical depth is, as before $\tau = \ln{(f_R)}$.
+The resulting $\tau$ is plotted in the bottom panel of \ref{fig:opticalDepthAeolusSpot}.
+We can calculate the column density of the dust if we assume a particle radius.
+As found in the paper the radius of the particles $r_p$ is $\sim$ 0.3 $\mu$m.
+Then, the column density is:
+\begin{equation}
+N_{dust} = \frac{\tau} {\pi * r_p^2 Q_{ext}}.
+\end{equation}
+Assuming $Q_{ext} \sim 1$, then $N_{dust} = 1.2 \times 10^{12}$~m$^{-2}$.
+If we assume a density of 0.2 g cm$^{-3}$, this corresponds to a mass column density of 2.7 $\times 10^{-5}$ kg m$^{-2}$.
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{images/optical_depth/tau_plot_spot_constrast.pdf}
+\caption{{\it Top Panel} The flux contrast for a 50 K brightness temperature difference.
+{\it Bottom Panel} Optical depth of a haze layer if this 50 K spot contrast is due to dust extinction.}\label{fig:opticalDepthAeolusSpot}
+\end{centering}
+\end{figure}
 

### 2017-06-21 ms.tex
filled in max spots
Adam updated the brightness temperature section, put in a few questions and went through the other sections.

@@
 
-\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, T. Karalidi\altaffilmark{1}, J.\ E.\  Gizis\altaffilmark{4},  \and J. Teske\altaffilmark{5}}
+\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J.\ E.\  Gizis\altaffilmark{4}, T. Karalidi\altaffilmark{1}, \and J. Teske\altaffilmark{5}}
 
@@
 The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
-We detect no statistically phase variations with wavelength.
+We detect no statistically significant phase variations with wavelength.
 The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
@@
 
-\begin{deluxetable*}{lllcccccccl}
+\begin{deluxetable*}{lllccccccccl}
 \tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
 \tablewidth{0pt}
+\tabletypesize{\footnotesize}
 \tablehead{
- & \multicolumn{2}{c}{Spectral Type} \\
-\colhead{Name} & 
-\colhead{Opt} & 
-\colhead{NIR} & 
+ colhead{Name} & 
+\multicolumn{2}{c}{Spectral Type} & 
 \colhead{$d$} & 
@@
 \colhead{$J-K_s$} & 
+\colhead{\lbol} & 
 \colhead{\teff} & 
@@
 \colhead{Refs} \\
- &  &  & \colhead{(pc)} & &  & \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
+ &  \colhead{Opt} & \colhead{NIR} &  \colhead{(pc)} & &  & &  \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
  }
 \startdata
-\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 17-26 & 1-5 \\
-\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & 1614$\pm$100\tablenotemark{c} & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 54-90 & 5-10 \\
+\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
+\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & $-$4.18$\pm$0.03 & 1635$\pm$66 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 76 & 5-11 \\
 \enddata
-\tablenotetext{a}{Estimated inclination angle $i$, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i} / R$, where $P$ is in hours and $v\sin{i}$ is in km/s and $R$ is assumed to be 0.8 to 1.2 $\times$ the equatorial radius of Jupiter.
+\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
 A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
 \tablenotetext{b}{Tentative period.}
-\tablenotetext{c}{Estimated from the \citet{2015ApJ...810..158F} {\teff}/spectral type relation.}
 \tablerefs{(1) \citet{2003AJ....126.2421C};
-(2) \citet{2012ApJ...752...56F}; 
+(2) \citet{2016AJ....152...24W}; 
 (3) \citet{2015ApJ...810..158F};
@@
 (7) \citet{2016MNRAS.455..357S};
-(8) \citet{2015ApJ...798...73G};
-(9) \citet{2015ApJ...799..154M}
-(10) \citet{2015ApJ...798L..13Y}; 
+(8) \cite{2016ApJS..225...10F};
+(9) \citet{2015ApJ...798...73G};
+(10) \citet{2015ApJ...799..154M}
+(11) \citet{2015ApJ...798L..13Y}; 
 }
@@
 	\vspace{-.9in}
-	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right).
+	\caption{2MASS $JHK_s$ three-color images of the fields around our targets {\sha} (left) and {\shb} (right)
+	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).
 Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left.
@@
 
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C} is a bright, nearby ($d$ = 8.5$\pm$0.8~pc; \citealt{2012ApJ...752...56F}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 8.52$\pm$0.08~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
 This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
-Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius R = 1~{\rjup}.
+Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius\footnote{We adopt the equatorial radius of Jupiter, {\rjup} = 7.15$\times$10$^9$~cm.} R = 1~{\rjup}.
 There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+
 2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
@@
 $I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.
-Both spectra were normalized to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}.
-We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming effective temperatures ({\teff}s) from \citet{2015ApJ...810..158F} based on these sources' bolometric luminosity measurements (Table~\ref{tab:bdProp}).
-Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\teff} and radius were propagated by Monte Carlo simulation.
-For {\sha} we considered two cases: radii corresponding to an age of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}, for which the evolutionary models predict radii of 0.147~R$_{\odot}$ to 0.115~R$_{\odot}$; and an age range of 1--5~Gyr for which the evolutionary models predict radii of 0.092~R$_{\odot}$ to 0.084~R$_{\odot}$.
-For {\shb}, we assumed a lower age limit of 200~Myr based on its FLD-G classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S} range of 1--5~Gyr; evolutionary models predict radii of 0.120~R$_{\odot}$ to 0.097~R$_{\odot}$ for these ages.
+Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}.
+We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).}  \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}).
+Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radius were propagated by Monte Carlo simulation.
+For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
+For {\shb}, we assumed an lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}.
+The Baraffe et al.\ evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.
 
 Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.
-The spectral peaks for {\sha} are roughly constant at {\teff} = 1900$\pm$50~K in the field surface gravity case, and declines from 1700$\pm$20~K at the $J$-band peak to 1570$\pm$60~K at the $K$-band peak in the low surface gravity case.
-{\bf [Adam, Are these Numbers still true? Also, should it be T$_b$ instead of T$_{eff}$?]}
-Spectra models (e.g., \citealt{2012RSPTA.370.2765A}) predict brightness temperatures closer to the effective temperature at the $JHK$ flux peaks, so these data suggest {\sha} has an intermediate age/radius compared the assumptions made here.
+The spectral peaks for {\sha} are around 1800--1850~K in the field surface gravity case, and decline from 1700~K at $J$-band (1.2~$\micron$) to 1580~K at $K$-band (2.2~$\micron$) in the low surface gravity case.
+We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
+Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.
+These comparisons slightly favor the field surface gravity case, although differences in the properties of dust between source and models likely play a significant role.
 For {\shb},
-brightness temperatures range from 1880$\pm$30~K at the $J$-band peak to 1700$\pm$40~K at the $K$-band peak.
-These values are notably warmer than the {\teff} = 1614$\pm$100~K estimated from \citet{2015ApJ...810..158F} {\teff}/spectral type relation, but relatively consistent this source's earlier spectral type as compared to {\sha}.
-We conjecture that the Filippazzo et al.\ relation underestimates the {\teff} of this source due to its unusually dusty spectral energy distribution.
+brightness temperatures range from 1850~K at $J$-band to 1670~K at $K$-band, again overlapping but declining more strongly with wavelength than the equivalent spectral model, which has a {\teff} similar to that inferred by \citet{2016ApJS..225...10F} and the  \citet{2015ApJ...810..158F} {\teff}/spectral type relation.
 
@@
 	\plottwo{classify0835.pdf}{classify1821.pdf}
-	\plottwo{tbright0835.png}{tbright1821.png}
+	\plottwo{tbright0835.pdf}{tbright1821.pdf}
 	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
+	Primary absorption features are labeled.
 	(Bottom) Calculated brightness temperature spectra of {\sha} (left) and {\shb} (right).
-The faint lines represent individual calculations assuming a Monte Carlo realization of spectral flux, absolute magnitude, {\teff} and radius uncertainties; the dark lines represent the median of these realizations.
-For {\sha}, we calculate separate brightness temperatures assuming radii consistent with a low surface gravity (50--200 Myr; blue) and field surface gravity (1--5~Gyr; black).
-}
+The faint lines represent individual calculations for a Monte Carlo realization of spectral flux, absolute magnitude, {\lbol} and age uncertainties; the dark lines represent the median of these realizations.
+For {\sha}, we show two  brightness temperature spectra corresponding to a young brown dwarf (50--200 Myr; blue) and a field dwarf (0.5--3~Gyr; black).
+We also show the brightness temperature spectra of the equivalent spectral model for the measured luminosity and assumed ages (dotted lines)  The corresponding {\teff} and {\logg} values are given in the legend.}
 	\label{fig:tbright}
@@
 Relative spectra (source/reference) were then computed for each exposure.
-Our image rectification process described above ensures that the wavelength solution is the same for each row if the image.
-However, there are small additional shifts of the sources within the slit so another shift is performed between the sources to ensure the telluric features removed when dividing the two spectra.
+Our image rectification process described above ensures that the wavelength solution is the same for each row of the image.
+However, there are small additional shifts of the sources within the slit so another shift was performed between the sources to ensure that telluric features were removed when dividing the two spectra.
 
@@
 	}
-	\caption{{\it Top Panels: }Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
+	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
 	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
@@
 	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
-	 {\it Bottom Panels:} The time of maximum variation $t_1$ for each brown dwarf shows no clear trend with wavelength.
-	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.}
+	 [{\bf bottom panels need to be explained; what are y-axis units? why is t1 centered at 0? is this relative to some assumed peak time? what is that time? what about t2?}]}
 	\label{fig:ampSpec}
@@
 Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
-Neither the reference spectra nor the brown dwarfs spectra have any corrections applied for telluric absorption or instrumental spectral response.
+Neither the reference spectra nor the brown dwarf spectra have any corrections applied for telluric absorption or instrumental spectral response.
 The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric absorption signatures.
@@
 
-Figure \ref{fig:specphot} also shows the dynamic spectra (relative source brightness as a function of wavelength and time.
-{\sha} has a dynamic spectra resembling white noise with no significant variations in either the spectral or spatial direction at the $\lesssim$0.5\% level.
+Figure \ref{fig:specphot} also shows the dynamic spectra, the relative source brightness as a function of wavelength and time.
+{\sha} has a dynamic spectra resembling white noise with no significant variations in either spectral or temporal axes at the $\lesssim$0.5\% level.
 {\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
@@
 
-As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particular in bands $<$1.8~$\mu$m. 
-These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr.
+As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
+These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr. {\bf [relative to what time?]}
 The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 
@@
 For \sha\ we use a prior 2.6 $< \tau < $3.6 hr and for \shb\ we use 3.7 $< \tau <$ 4.7 hr.
-Each of these ranges are $\pm$0.5 hr from the literature values \citep[3.1,4.2hr][]{2004MNRAS.354..378K,2015ApJ...799..154M}.
-These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for \shb\ but narrow enough to ensure that the sinusoidal fits do not fit the airmass trends with time.
-Secondly, we restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to make sure there are no 2$\pi$ degeneracies in the fit.
+Each of these ranges are $\pm$0.5 hr from the literature values.
+These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for \shb\ but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
+We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
+{\bf [do you also constraint A1 $>$ A2?]}
 
 Figure \ref{fig:ampSpec} shows the MCMC posterior constraints for periodic amplitudes as a function of wavelength.
-For {\sha} (Figure \ref{fig:ampspec0835}) we find small ($\lesssim 0.5\%$) amplitudes with a flat trend as a function of wavelength.
-There is possible low level variability for the wavelengths long than 2.1$\mu$m.
-\shb, on the other hand, shows a clear decreasing trend as function of wavelength.
-In neither case, is there any statistically significant wavelength dependence to the time of maximum variation $t_1$.
+For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
+\shb, on the other hand, shows clear variability with a decreasing trend in amplitude as function of wavelength.
+In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
 
@@
 where $f_R$ is the flux ratio of the maximum over minimum flux.
-There is a multiplicative offset between the IRTF and WFC3 spectrum because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
+There is a multiplicative offset 
+{\bf [what is the value?]}
+between the IRTF and WFC3 spectrum, presumably because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
 \citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
@@
 \caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb\ assuming a forsterite composition.
-The model includes an amplitude offset, $B$, (to account for areal coverage), a median particle radius, $r$ and a scale parameter $\sigma$.
-The upper right inset plot shows the log-normal particle size distribution in blue for samples drawn from the MCMC results.
+The model includes an amplitude offset $B$ to account for areal coverage, a median particle radius $r$, and a scale parameter $\sigma$.
+The upper right inset plot shows the log-normal particle size distribution in blue for samples drawn from the posterior distribution.
 The red curve is the maximum likelihood log-normal particle size distribution.}\label{fig:corner1821mie}
@@
 
-We model the wavelength dependence of \sha\ and \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud is confined to one hemisphere of the brown dwarf, the amplitude of the variability ($A_1$) is directly proportional to the opacity of the particles.
+We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
+If we assume the cloud is confined to one hemisphere of the brown dwarf (i.e., maximum surface heterogeneity), the amplitude of the variability ($A_1$) is directly proportional to the opacity of the particles.
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
@@
 
-For \sha\ we find that since no significant variability is detected that the particle size is unconstrained over the prior of $0~\mu m < r < 5~\mu m$.
+%For \sha\ we find that since no significant variability is detected that the particle size is unconstrained over the prior of $0~\mu m < r < 5~\mu m$.
 We show the maximum likelihood model which has a near-zero amplitude.
-For \shb\ we find that the amplitude spectrum is well fit by a Mie scattering model and the median particle radius is better constrained.
+For \shb\ we find that the amplitude spectrum is well-fit by a Mie scattering model and the median particle radius is reasonably constrained.
 Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.28~$\mu$m grains.
@@
 Considering the large number of possible grain geometries and compositions, this is an underestimate for the true uncertainty in particle sizes.
-Future work could include full modeling of atmospheres with more complex spatial distributions, grain geometries and compositions.
+Future work could include full modeling of the atmosphere with more complex spatial distributions, grain geometries and compositions (e.g., \citealt{2008ApJ...675L.105H}).
 
@@
 \newcommand{\maxSpots}{\#?}
+
+{\bf AJB has some concerns over this section: it is extremely terse with no clear conclusions, and no discussion on the uniqueness of the spot solutions shown.
+The same temperature is used for each of the wavelengths, when the underlying brightness temperature actually changes; suggest using background temperature of for 1795 K for 0.96$\mu$m, 1788 K for 1.20$\mu$m, and 1853 K for 1.26$\mu$m based on the brightness temperature analysis.
+I would naively assume that the spot structures would be at the same location at each wavelength but vary in temperature offset - can a prior be applied so that each map has the same structure but different spot temperature (with Tspot = Tback as a possibility)?}
+
 We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.
-We allow up to \maxSpots\ across the sphere of the brown dwarf, all with a constant temperature contrast.
+We allow up to \maxSpots\ {\bf [please fill in]} across the sphere of the brown dwarf, all with a constant temperature contrast.
 We set the ``background'' at the measured effective temperature of 1614 K.
@@
 This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
-The lack of the water vapor band gives evidence of a high altitude aerosol layer in the atmosphere.
+The lack of the variability in the water vapor bands gives evidence of a high altitude aerosol layer in the atmosphere.
 We find no statistically significant phase offsets in the light curves for \sha\ nor \shb\ from wavelength to wavelength.
@@
 A log-normal particle size distribution fits the data with a median grain radius of 0.24 $^{+0.05}_{-0.07}$ $\mu$m.
-Continued ground-based surveys such as with SpeX on IRTF will provide powerful constraints on dust particle sizes in other brown dwarf atmospheres which can have different temperature profiles and cloud altitudes.
+{\bf [need summary of AEOLUS results]}
+
+Using ground-based facilities such as SpeX on IRTF allows us to expand our monitoring of cloud-bearing ultracool dwarfs, both in sample size and long-term tracking.
+The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations; while the latter allows us to study weather-related changes to cloud structures over multiple rotation periods.
+We are currently pursuing a larger monitoring sample that will be reported in future publications.
 
@@
 
-%If  used, this work made use of the \texttt{astropy} package \citep{astropy2013}.
-%If used, some data was collected from the Open Exoplanet Catalogue \citep{rein2012openExoCat}.
-
-%% In a manner similar to \objectname authors can provide links to dataset
-%% hosted at participating data centers via the \dataset{} command.  The
-%% second curly bracket argument is printed in the text while the first
-%% parentheses argument serves as the valid data set identifier.  Large
-%% lists of data set are best provided in a table (see Table 3 for an example).
-%% Valid data set identifiers should be obtained from the data center that
-%% is currently hosting the data.
-%%
-%% Note that AASTeX interprets everything between the curly braces in the 
-%% macro as regular text, so any special characters, e.g. "#" or "_," must be 
-%% preceded by a backslash. Otherwise, you will get a LaTeX error when you 
-%% compile your manuscript.  Special characters do not 
-%% need to be escaped in the optional, square-bracket argument.
-
-%% In this section, we use  the \subsection command to set off
-%% a subsection.  \footnote is used to insert a footnote to the text.
-
-%% Observe the use of the LaTeX \label
-%% command after the \subsection to give a symbolic KEY to the
-%% subsection for cross-referencing in a \ref command.
-%% You can use LaTeX's \ref and \label commands to keep track of
-%% cross-references to sections, equations, tables, and figures.
-%% That way, if you change the order of any elements, LaTeX will
-%% automatically renumber them.
-
-%% This section also includes several of the displayed math environments
-%% mentioned in the Author Guide.
-
-%% The equation environment wil produce a numbered display equation.
-
-%% The \notetoeditor{TEXT} command allows the author to communicate
-%% information to the copy editor.  This information will appear as a
-%% footnote on the printed copy for the manuscript style file.  Nothing will
-%% appear on the printed copy if the preprint or
-%% preprint2 style files are used.
-
-%% The eqnarray environment produces multi-line display math. The end of
-%% each line is marked with a \\. Lines will be numbered unless the \\
-%% is preceded by a \nonumber command.
-%% Alignment points are marked by ampersands (&). There should be two
-%% ampersands (&) per line.
-
-%% Putting eqnarrays or equations inside the mathletters environment groups
-%% the enclosed equations by letter. For instance, the eqnarray below, instead
-%% of being numbered, say, (4) and (5), would be numbered (4a) and (4b).
-%% LaTeX the paper and look at the output to see the results.
-
-%% This section contains more display math examples, including unnumbered
-%% equations (displaymath environment). The last paragraph includes some
-%% examples of in-line math featuring a couple of the AASTeX symbol macros.
-
-%% The displaymath environment will produce the same sort of equation as
-%% the equation environment, except that the equation will not be numbered
-%% by LaTeX.
-%% If you wish to include an acknowledgments section in your paper,
-%% separate it off from the body of the text using the \acknowledgments
-%% command.
-
-%% Included in this acknowledgments section are examples of the
-%% AASTeX hypertext markup commands. Use \url without the optional [HREF]
-%% argument when you want to print the url directly in the text. Otherwise,
-%% use either \url or \anchor, with the HREF as the first argument and the
-%% text to be printed in the second.
-
 \acknowledgments
 
-%% To help institutions obtain information on the effectiveness of their
-%% telescopes, the AAS Journals has created a group of keywords for telescope
-%% facilities. A common set of keywords will make these types of searches
-%% significantly easier and more accurate. In addition, they will also be
-%% useful in linking papers together which utilize the same telescopes
-%% within the framework of the National Virtual Observatory.
-%% See the AASTeX Web site at http://aastex.aas.org/
-%% for information on obtaining the facility keywords.
-
-%% After the acknowledgments section, use the following syntax and the
-%% \facility{} macro to list the keywords of facilities used in the research
-%% for the paper.  Each keyword will be checked against the master list during
-%% copy editing.  Individual instruments or configurations can be provided 
-%% in parentheses, after the keyword, but they will not be verified.
-
-%{\it Facilities:} \facility{Nickel}, \facility{HST (STIS)}, \facility{CXO (ASIS)}.
-
-%% Appendix material should be preceded with a single \appendix command.
-%% There should be a \section command for each appendix. Mark appendix
-%% subsections with the same markup you use in the main body of the paper.
-
-%% Each Appendix (indicated with \section) will be lettered A, B, C, etc.
-%% The equation counter will reset when it encounters the \appendix
-%% command and will number appendix equations (A1), (A2), etc.
+{\it Facilities:} \facility{IRTF (SpeX)}.
 
@@
 Our sinusoidal model using Equation \ref{eq:cosfit} is shown for each of the light curves in Figure \ref{fig:tserNoDetrend}.
-For \ref{fig:tserDetrend} we remove the fit the baseline variations to show the astrophysical modulations due to brown dwarf rotation.
+For Figure~\ref{fig:tserDetrend} we remove the fit the baseline variations to show the astrophysical modulations due to brown dwarf rotation.
 

### 2017-06-21 ms.tex

@@
 
-\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, J.\ E.\  Gizis\altaffilmark{4}, T. Karalidi\altaffilmark{1}, \and J. Teske\altaffilmark{5}}
+\author{E. Schlawin\altaffilmark{1,2}, Adam J.\ Burgasser\altaffilmark{2,3}, T. Karalidi\altaffilmark{1}, J.\ E.\  Gizis\altaffilmark{4},  \and J. Teske\altaffilmark{5}}
 
@@
 	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
+	 {\it Bottom Panels:} The time of maximum variation $t_1$ for each brown dwarf shows no clear trend with wavelength.
+	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.
  [{\bf bottom panels need to be explained; what are y-axis units? why is t1 centered at 0? is this relative to some assumed peak time? what is that time? what about t2?}]}
@@
 \section{Spot Distribution}
-\newcommand{\maxSpots}{\#?}
+\newcommand{\maxSpots}{6}
 
@@
 
+>>>>>>> remotes/origin/sharelatex-2017-06-21-0322
 We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.

### 2017-06-21 ms.tex
I answered the questions Adam wrote in on the amplitude spectrum plots.

@@
 	}
-	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf. \sha\ shows no clear trend in wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
+	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf.
+\sha\ shows no significant variability nor trends with wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
 	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
@@
 	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
-	 {\it Bottom Panels:} The time of maximum variation $t_1$ for each brown dwarf shows no clear trend with wavelength.
-	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.
- [{\bf bottom panels need to be explained; what are y-axis units? why is t1 centered at 0? is this relative to some assumed peak time? what is that time? what about t2?}]}
+	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (BJD 2457388.0 and BJD 2457565 for \sha\ and \shb\ respectively).
+	 Neither $t_1$ spectrum shows a clear trend with wavelength indicating no significant spot offsets.
+	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$. $t_2$ (not shown) also shows no trend with wavelength.}
 	\label{fig:ampSpec}
@@
 We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
-{\bf [do you also constraint A1 $>$ A2?]}
+We do not put any constraints on A$_1$ relative to A$_2$.
 
@@
 where $f_R$ is the flux ratio of the maximum over minimum flux.
-There is a multiplicative offset 
-{\bf [what is the value?]}
-between the IRTF and WFC3 spectrum, presumably because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
+There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum, presumably because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
 \citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.

### 2017-06-22 ms.tex
moved the Aeolus section to the supplement writeup.

@@
 	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
-	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (BJD 2457388.0 and BJD 2457565 for \sha\ and \shb\ respectively).
+	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (JD 2457388.0 and JD 2457565 for \sha\ and \shb\ respectively).
 	 Neither $t_1$ spectrum shows a clear trend with wavelength indicating no significant spot offsets.
@@
 
-\section{Spot Distribution}
-\newcommand{\maxSpots}{6}
-
-{\bf AJB has some concerns over this section: it is extremely terse with no clear conclusions, and no discussion on the uniqueness of the spot solutions shown.
-The same temperature is used for each of the wavelengths, when the underlying brightness temperature actually changes; suggest using background temperature of for 1795 K for 0.96$\mu$m, 1788 K for 1.20$\mu$m, and 1853 K for 1.26$\mu$m based on the brightness temperature analysis.
-I would naively assume that the spot structures would be at the same location at each wavelength but vary in temperature offset - can a prior be applied so that each map has the same structure but different spot temperature (with Tspot = Tback as a possibility)?}
-
->>>>>>> remotes/origin/sharelatex-2017-06-21-0322
-We also fit our light curves to an {\it Aeolus} spot model \citep{2015ApJ...814...65K,2016ApJ...825...90K}.
-We allow up to \maxSpots\ {\bf [please fill in]} across the sphere of the brown dwarf, all with a constant temperature contrast.
-We set the ``background'' at the measured effective temperature of 1614 K.
-
-Figure \ref{fig:spotModel} shows the spot models fit to the light curve at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.
-At all three wavelengths, the fitted brightness temperature contrast is around 50 K above the background.
-These higher temperature spots are indicative of either holes in clouds or regions of elevated temperature.
-The distribution of spots changes with wavelength, suggesting that the distribution of clouds or temperatures is complex.
-The low amplitude and signal to noise of the light curves makes it difficult to put tight constraints on the spot distribution.
-
 \section{Conclusions}\label{sec:conclusions}
@@
 A log-normal particle size distribution fits the data with a median grain radius of 0.24 $^{+0.05}_{-0.07}$ $\mu$m.
-{\bf [need summary of AEOLUS results]}
 

### 2017-06-22 ms.tex
also removed the Aeolus figure.

@@
 We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
-The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 1--2.5~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
+The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
 We detect no statistically significant phase variations with wavelength.
@@
 
-\begin{figure*}
-\begin{centering}
-\includegraphics[width=0.45\textwidth]{e_1821_096_map.png}\\
-\includegraphics[width=0.45\textwidth]{e_1821_120_map.png}
-\hspace{0.2in}
-\includegraphics[width=0.45\textwidth]{e_1821_126_map.png}
-\caption{{\it Aeolus} maps of the light curves at 0.96$\mu$m, 1.20$\mu$m and 1.26 $\mu$m.}\label{fig:spotModel}
-\end{centering}
-\end{figure*}
-
 For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.

### 2017-06-22 ms.tex
fixed a few typos abstract through section 2.

@@
 \tablehead{
- colhead{Name} & 
+\colhead{Name} & 
 \multicolumn{2}{c}{Spectral Type} & 
@@
 \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
-There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 29$\arcsec$ separation; we chose the latter for our monitoring observations.
+There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 19$\arcsec$ separation; we chose the latter for our monitoring observations.
 
@@
 
-Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.
-The spectral peaks for {\sha} are around 1800--1850~K in the field surface gravity case, and decline from 1700~K at $J$-band (1.2~$\micron$) to 1580~K at $K$-band (2.2~$\micron$) in the low surface gravity case.
-We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
-Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.
-These comparisons slightly favor the field surface gravity case, although differences in the properties of dust between source and models likely play a significant role.
-For {\shb},
-brightness temperatures range from 1850~K at $J$-band to 1670~K at $K$-band, again overlapping but declining more strongly with wavelength than the equivalent spectral model, which has a {\teff} similar to that inferred by \citet{2016ApJS..225...10F} and the  \citet{2015ApJ...810..158F} {\teff}/spectral type relation.
-
 \begin{figure*}
@@
 \end{figure*}
+
+Figure~\ref{fig:tbright} shows the resulting brightness temperature spectra and their uncertainties from these calculations.
+The spectral peaks for {\sha} are around 1800--1850~K in the field surface gravity case, and decline from 1700~K at $J$-band (1.2~$\micron$) to 1580~K at $K$-band (2.2~$\micron$) in the low surface gravity case.
+We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
+Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.
+These comparisons slightly favor the field surface gravity case, although differences in the properties of dust between source and models likely play a significant role.
+For {\shb},
+brightness temperatures range from 1850~K at $J$-band to 1670~K at $K$-band, again overlapping but declining more strongly with wavelength than the equivalent spectral model, which has a {\teff} similar to that inferred by \citet{2016ApJS..225...10F} and the  \citet{2015ApJ...810..158F} {\teff}/spectral type relation.
 

### 2017-06-28 ms.tex
Added several fixes to intro, explained reference time and changed the symbol for flux from I to F.

@@
 The comparison stars referred to in the text appear as blue sources in these images.
-}
+	For \sha\, we use the comparison star to the left and for \shb\ the lower right.}
 	\label{fig:images}
@@
 In Section~\ref{sec:analysis}, we analyze these time series using sinusoidal model fits over discrete spectral bands to generate individual light curves and amplitude spectra.
-We then fit the variability amplitude spectra to two different physical models, Mie scattering from clouds and heterogeneous temperature spots, to assess which more accurately reproduces the data.
+We then fit the variability amplitude spectra with a Mie extinction model for the clouds and constrain the particle size distribution.
 We summarize our results in Section~\ref{sec:conclusions}.
@@
 \begin{equation}
-T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{I_{\lambda,surf}\lambda^5}\right)\right]^{-1}
+T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1}
 \end{equation}
-where the surface flux density $I_{\lambda,surf}$ is computed as
+where the surface flux density $F_{\lambda,surf}$ is computed as
 \begin{equation}
-I_{\lambda,surf} = {\pi}B_{\lambda} = I_{\lambda,obs}\left(\frac{d}{R}\right)^2 = I_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
+F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
 \end{equation}
-$I_{\lambda,obs}$ and $I_{\lambda,abs}$ are the observed and absolute flux densities, $d$ the source distance and $R$ the source radius.
+$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.
 Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}.
@@
 As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
-These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr. {\bf [relative to what time?]}
+These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
 The amplitude of these variations is strongly wavelength-dependent with $\sim$3.0\% peak-to-trough variations at short 

### 2017-06-28 ms.tex
updated description of color from red to magenta.

@@
 	\plottwo{tbright0835.pdf}{tbright1821.pdf}
-	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in red]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
+	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in magenta]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
 	Primary absorption features are labeled.
@@
 	For {\sha}, we show two  brightness temperature spectra corresponding to a young brown dwarf (50--200 Myr; blue) and a field dwarf (0.5--3~Gyr; black).
-We also show the brightness temperature spectra of the equivalent spectral model for the measured luminosity and assumed ages (dotted lines)  The corresponding {\teff} and {\logg} values are given in the legend.}
+	We also show the brightness temperature spectra of the equivalent spectral model for the measured luminosity and assumed ages (dotted lines).
+	The corresponding {\teff} and {\logg} values are given in the legend.}
 	\label{fig:tbright}

### 2017-06-29 ms.tex
fixed a few typos and added a qualifier about the particle size distribution in the conclusions.

@@
 These spatial profiles were then used to calculate a weighted sum spectrum across the illuminated detector for each source and exposure. 
-Typical signals-to-noise of the extracted spectra were 40 - 100 per spectral pixel (unbinned).
+Typical signal-to-noise of the extracted spectra were 40 - 100 per spectral pixel (unbinned).
 Relative spectra (source/reference) were then computed for each exposure.
@@
 where $f_R$ is the flux ratio of the maximum over minimum flux.
-There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum, presumably because they were taken at different epochs and therefore different spatial cloud and temperature distributions.
+There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum because they were taken at different epochs and presumably have different spatial cloud and temperature distributions.
 \citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
@@
 They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
-Our median particle radius of $r$=0.24 $\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened stars in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
+Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened stars in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
 
@@
 
-2MASS J1821 shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9$\mu$m) which decreases towards the near infrared (2.4$\mu$m).
-This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
+2MASS J1821 shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which decreases towards the near infrared (2.4$~\mu$m).
+This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1~$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
 The lack of the variability in the water vapor bands gives evidence of a high altitude aerosol layer in the atmosphere.
@@
 A log-normal particle size distribution fits the data with a median grain radius of 0.24 $^{+0.05}_{-0.07}$ $\mu$m.
+However, considering different particle compositions and grain geometries can widen the allowed range of particle sizes.
 
@@
 
-{\it Facilities:} \facility{IRTF (SpeX)}.
+\facility{IRTF (SpeX)}.
 

### 2017-07-06 ms.tex
added text to explain the regions affected by telluric absorption

@@
 Changing colors are used to distinguished the light curves with offsets.
-\sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.}
+\sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.
+	Green brackets show regions where telluric absorption can contaminate the time series.}
 	\label{fig:tserDetrend}
@@
 	Each wavelength bin is labeled on the right side.
-Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near telluric absorption features at 1.38$\mu$m and 1.87$\mu$m.}
+Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near edges of telluric absorption features at 1.32$\mu$m and 1.81$\mu$m.
+	Green brackets show regions where telluric absorption can contaminate the time series.}
 	\label{fig:tserNoDetrend}

### 2017-07-08 ms.tex
shaded the telluric regions in the spectral plots.
updated the spectra plots with time labels and telluric bands.

@@
 	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
-	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (JD 2457388.0 and JD 2457565 for \sha\ and \shb\ respectively).
+	 In all plots the regions potentially contaminated by telluric absorption are shaded in light green.
+	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (JD 2457388.0 and JD 2457565.0 for \sha\ and \shb\ respectively).
 	 Neither $t_1$ spectrum shows a clear trend with wavelength indicating no significant spot offsets.

### 2017-07-12 ms.tex
Updates from ShareLaTeX
started updating references in the parameter table to tie each number with a specific reference.
incorporated both Johanna's and Theodora's suggestions.

@@
 The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
-Wavelength-dependent phase variations in lightcurves has also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
-Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsation \citep{2014ApJ...785..158R}.
+Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
+Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations.
+Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact wiht clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.
 
@@
 
-\begin{deluxetable*}{lllccccccccl}
+\begin{deluxetable*}{lllllllllll}
 \tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
@@
 \colhead{$v\sin{i}$} & 
-\colhead{$i$\tablenotemark{a}} & 
-\colhead{Refs} \\
- &  \colhead{Opt} & \colhead{NIR} &  \colhead{(pc)} & &  & &  \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
+\colhead{$i$\tablenotemark{a}} \\
+ &  \colhead{Opt} & \colhead{NIR\tablenotemark{a}} &  \colhead{(pc)} & &  & &  \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
  }
 \startdata
-\sha\ & L5 & L7 & 8.52$\pm$0.08 & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08 & 1754$\pm$112 & 3.1\tablenotemark{b} & 14.18$\pm$0.43 & 21 & 1-5 \\
-\shb\ & L4.5p & L5 & 9.38$\pm$0.03 & 12.40$\pm$0.02 & 1.78$\pm$0.03 & $-$4.18$\pm$0.03 & 1635$\pm$66 & 4.2$\pm$0.1 & 28.85$\pm$0.16 & 76 & 5-11 \\
+\sha\ & L5$^{(1)}$ & L7 & 7.27$\pm$0.02$^{(2)}$ & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08$^{(3)}$ & 1754$\pm$112$^{(3)}$ & 3.1\tablenotemark{b}$^{(4)}$ & 14.18$\pm$0.43$^{(5)}$ & 21 \\
+\shb\ & L4.5p$^{(6)}$ & L5 & 9.38$\pm$0.03$^{(7)}$ & 12.40$\pm$0.02 & 1.78$\pm$0.03 & $-$4.18$\pm$0.03$^{(8)}$ & 1635$\pm$66$^{(8)}$ & 4.2$\pm$0.1$^{(9)}$ & 28.85$\pm$0.16$^{(5)}$ & 76 \\
 \enddata
-\tablenotetext{a}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
+\tablenotetext{a}{This Work.}
+\tablenotetext{b}{Estimated inclination angle $i$ assuming a radius = 1 Jupiter radius, so that $\sin{i}$ = 8.0$\times$10$^{-3}Pv\sin{i}$, where $P$ is in hours and $v\sin{i}$ is in km/s.
 A value of $i$ $\approx$ 0{\degree} is viewed pole-on, $i$ $\approx$ 90{\degree} is viewed equator-on.}
-\tablenotetext{b}{Tentative period.}
+\tablenotetext{c}{Tentative period.}
 \tablerefs{(1) \citet{2003AJ....126.2421C};
@@
 (7) \citet{2016MNRAS.455..357S};
-(8) \cite{2016ApJS..225...10F};
-(9) \citet{2015ApJ...798...73G};
-(10) \citet{2015ApJ...799..154M}
-(11) \citet{2015ApJ...798L..13Y}; 
+(8) \cite{2016ApJS..225...10F} with updated values as discussed in Section \ref{sec:targets};
+(9) \citet{2015ApJ...799..154M}
 }
@@
 	\caption{Top Panels: Normalized median raw spectra of {\sha} (left) and {\shb} (right) in black, compared with the respective reference stars (blue) and background emission (red; mostly telluric OH emission and thermal background).
+The areas of higher telluric absorption are visible near 1.4~$\mu$m and 1.8~$\mu$m.
 Bottom Panels: Dynamic spectra of each brown dwarf system.
@@
 They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
-Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened stars in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
+Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
 
@@
 We find no statistically significant phase offsets in the light curves for \sha\ nor \shb\ from wavelength to wavelength.
+This is different from  \citep{2016ApJ...826....8Y} who found a significant phase offset using simultaneous Spitzer and HST light curves at two different epochs.
+This may be due to the different pressures probed by the Spitzer Channel's 1 and 2 (3.6 $\mu$m and 4.5 $\mu$m) not found in our wavelength range.
 

### 2017-07-13 ms.tex
added a constraint on the rotation period for 2MASS 1821.
added a plot to show constraints on A2 and t2 for 2MASS 1821.

@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
@@
 	 Neither $t_1$ spectrum shows a clear trend with wavelength indicating no significant spot offsets.
-	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$. $t_2$ (not shown) also shows no trend with wavelength.}
+	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.}
 	\label{fig:ampSpec}
 \end{figure*}
+
+\begin{figure}
+\begin{centering}
+\includegraphics[width=0.5\textwidth]{amp_vs_wavl_j1821_a2_t2.pdf}
+\caption{Secondary sinusoidal amplitude ($A_2$) as a function of wavelength for \shb.
+As in Figure \ref{fig:ampSpec}, the regions potentially contaminated by telluric absorption are shown in green.
+The secondary amplitude $A_2$ shows a gradual decrease as a function of wavelength as with $A_1$, indicative of Mie scattering grains.
+{\it Bottom Panel:} The time of maximum variation $t_2$ shows no clear phase shift trend.
+The constraints approach the prior $\pm \tau$/4 when no significant variability is detected.
+The $A_2$ constraints for \sha\ (not shown) are all consistent with zero.}\label{fig:amp2Spec}
+\end{centering}
+\end{figure}
 
@@
 In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
+The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}.
+If we optimistically assume all wavelengths are statistically independent, the weighted average rotation period is 4.10 $\pm$ 0.03 hours.
+
+Figure \ref{fig:amp2Spec} shows the posterior constraints on the secondary sinusoidal term.
+As with $A_1$, the amplitude spectrum decreases as a function of wavelength, indicating Mie scattering grains and that the higher frequency term is likely just smaller scale cloud structures with similar properties as the longer timescale variability.
+As with Figure \ref{fig:ampSpec}, we find no strong phase shift for the second time of maximum variation $t_2$ as a function of wavelength.
 
@@
 \includegraphics[width=0.5\textwidth]{corner_j1821_mie_sc.pdf}
-\caption{Posterior distributions to the simple Mie scattering fit to the amplitude spectrum for \shb\ assuming a forsterite composition.
+\caption{Posterior distributions to the simple Mie scattering fit to the $A_1$ amplitude spectrum for \shb\ assuming a forsterite composition.
 The model includes an amplitude offset $B$ to account for areal coverage, a median particle radius $r$, and a scale parameter $\sigma$.

### 2017-07-13 ms.tex
Adam changed some wording and re-ordered a few sentences.

@@
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
-We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
+We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
 We detect no statistically significant phase variations with wavelength.
-The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader variability survey.
+The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
 \end{abstract}
@@
 
-Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects  (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}) can significantly improve the precision of ground-based spectro-photometry.
+Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
 \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
@@
 	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).
-Each image is centered on the target, and span a 1$\arcmin\times\arcmin$ field of view oriented with North up and East the left.
+Each image is centered on the target, and span a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
 The comparison stars referred to in the text appear as blue sources in these images.
-	For \sha\, we use the comparison star to the left and for \shb\ the lower right.}
+	For \sha\, we use the comparison star to the left and for \shb\ to the lower right.}
 	\label{fig:images}
@@
 
-This article reports the results of a pilot study adapting these methods to measuring the variability of two L-type dwarfs with nearby visual companions.
+This article reports the results of a pilot study adapting these methods to measure the variability of two L-type dwarfs with nearby visual companions.
 We describe our target selection process and pilot target properties in Section~\ref{sec:targets}.
@@
 $F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.
-Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes \citep{2016MNRAS.455..357S,2016AJ....152...24W}.
+Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes.
 We adopted radii from the evolutionary models of \citet{2003A&A...402..701B} assuming bolometric luminosities from \citet{2015ApJ...810..158F} for {\sha} and from\footnote{The parameters reported for {\shb} in \citet{2016ApJS..225...10F} are in error, but have been updated here based on a forthcoming erratum (J.\ Faherty, 2017, priv.\ comm.).} \citet{2016ApJS..225...10F} for {\shb} (Table~\ref{tab:bdProp}).
-Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radius were propagated by Monte Carlo simulation.
+Uncertainties in the spectral fluxes, absolute photometric calibration, adopted {\lbol} and radii were propagated by Monte Carlo simulation.
 For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
@@
 \tablecomments{N$_{int}$ is the number of integrations and t$_{int}$ is the effective integration time for the 32 non-destructive reads up the ramp.
-The duration is the total time from start to end of the observations including the reset times and overheads.
-The FWHM is the measured median value of the time series around 1.6$\mu$m.}
+The duration is the total time from start to end of the observations including array sampling and overheads.
+The FWHM is the measured full width half maximum of the spatial point spread function around 1.6$\mu$m, taken as the median value over the entire time series.}
 \end{deluxetable*}
@@
 Bottom Panels: Dynamic spectra of each brown dwarf system.
-The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant repeated modulations with a period near 4 hours.
-The variability in \shb\ is prominent at the short wavelengths with a magnitude of ~$\sim$2\% peak-to-trough at short wavelengths but $\lesssim 0.5\%$ toward 2~$\mu$m.}
+The dynamic spectrum for \sha\ shows no significant variability in the spatial or spectral direction whereas \shb\ shows significant modulations with a period near 4 hours.
+The variability in \shb\ is prominent at the short wavelengths with a magnitude of $\sim$2--3\% peak-to-trough, but $\lesssim 0.5\%$ toward 2~$\mu$m.}
 	\label{fig:specphot}
@@
 	}
-	\caption{Time series for each system with an offset added for clarity.
-	Each wavelength bin is labeled on the right side.
-Changing colors are used to distinguished the light curves with offsets.
-\sha\ shows relatively flat light curves whereas \shb\ has large amplitude double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.
-	Green brackets show regions where telluric absorption can contaminate the time series.}
+	\caption{Time series for each system, after subtraction of baseline trends.
+Each wavelength binned lightcurve is color coded, offset, and labeled on the right side.
+\sha\ shows relatively flat light curves whereas \shb\ has clearly visible double-peaked oscillations at short wavelengths and flat light curves at long wavelengths.
+	Lines trace the best double sinusoidal model fit for each light curve.
+	Green brackets show regions where telluric absorption may contaminate the time series.}
 	\label{fig:tserDetrend}
@@
 	\caption{(Top panels) Sine fit amplitude versus wavelength for each brown dwarf.
-\sha\ shows no significant variability nor trends with wavelength, while \shb\ has a strong slope indicative of Mie-scattering particles.
-	 Also shown in the figure for \shb\ is the WFC3 amplitude from \citet{2015ApJ...798L..13Y}. The WFC3 observations were from a different epoch, with different cloud coverage, but show a similar slope.
-	 The amplitude spectrum for each system is fit a simple Mie scattering model for a log-normal particle size distribution of spherical forsterite grains.
-	 \sha\ is consistent with a zero amplitude model which puts no constraints on the particle size distribution.
-	 \shb\ is shown with the best fit median particle size of 0.28 $\mu$m grains.
+\sha\ shows only marginally significant variability near 1.7~$\micron$ and 2.1--2.4~$\micron$, and no obvious trends with wavelength.
+\shb\ has significant variability over wavelengths $<$1.7$\micron$ with a strong spectral slope.
+	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained on a different epoch, but show a similar slope.
+	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle size of 0.28 $\mu$m.
 	 In all plots the regions potentially contaminated by telluric absorption are shaded in light green.
-	 {\it Bottom Panels:} The time of maximum variation $t_1$ (in hours) is shown for each brown dwarf relative to the reference epoch (JD 2457388.0 and JD 2457565.0 for \sha\ and \shb\ respectively).
-	 Neither $t_1$ spectrum shows a clear trend with wavelength indicating no significant spot offsets.
+	 {\it Bottom Panels:} The time offset of maximum amplitude, $t_1$ (in hours), relative to the reference epoch (JD 2457388.0 for \sha\ and JD 2457565.0 for {\shb}).
+	 Neither shows a clear trend with wavelength, indicating no significant phase offsets.
 	 For wavelengths with small variability amplitudes, $t_1$ becomes as wide as the prior window $-\tau/2 < t_1 < \tau/2$.}
@@
 As in Figure \ref{fig:ampSpec}, the regions potentially contaminated by telluric absorption are shown in green.
-The secondary amplitude $A_2$ shows a gradual decrease as a function of wavelength as with $A_1$, indicative of Mie scattering grains.
-{\it Bottom Panel:} The time of maximum variation $t_2$ shows no clear phase shift trend.
+The secondary amplitude $A_2$ shows a gradual decrease as a function of wavelength, similar to that seen with $A_1$.
+{\it Bottom Panel:} The time offset of maximum variation, $t_2$ (in hours) shows no clear phase shift trend.
 The constraints approach the prior $\pm \tau$/4 when no significant variability is detected.
@@
 Neither the reference spectra nor the brown dwarf spectra have any corrections applied for telluric absorption or instrumental spectral response.
-The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric absorption signatures.
-The regions near 1.37~$\mu$m and 1.83~$\mu$m have significantly lower flux due to telluric water vapor absorption.
+The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric water absorption signatures
+near 1.37~$\mu$m and 1.83~$\mu$m, resulting in significantly lower flux.
 
 Figure \ref{fig:specphot} also shows the dynamic spectra, the relative source brightness as a function of wavelength and time.
-{\sha} has a dynamic spectra resembling white noise with no significant variations in either spectral or temporal axes at the $\lesssim$0.5\% level.
+{\sha} has dynamic spectra resembling white noise, with no significant variations in either spectral or temporal axes at the $\lesssim$0.5\% level.
 {\shb}, on the other hand, shows a clear periodic signal that is strongest at the shortest wavelengths and declines in amplitude toward the longest wavelengths.
@@
 
-As seen in Figure~\ref{fig:tserDetrend}, we see minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
+We find minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
 These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
@@
 wavelengths and near-zero amplitude at the longest wavelengths.
-A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
-Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
 
-Each of the light curves were fit to a double sinusoidal model:
+Each of the raw light curves were fit to a double sinusoidal model:
 \begin{equation}\label{eq:cosfit}
@@
 \end{equation}
-where $F(t)$ is the flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each cosine term, $\tau$ is period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are terms describing the baseline trend.
+where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-For \sha\ we use a prior 2.6 $< \tau < $3.6 hr and for \shb\ we use 3.7 $< \tau <$ 4.7 hr.
-Each of these ranges are $\pm$0.5 hr from the literature values.
-These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for \shb\ but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
+of 2.6 $< \tau < $3.6 hr for \sha]\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
+These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
 We also restrict the time of maximum periodic flux such that $-\tau/2 < t_1 < \tau/2$ and $-\tau/4 < t_2 < \tau/4$ to assure there are no 2$\pi$ degeneracies in the fit.
@@
 For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
-\shb, on the other hand, shows clear variability with a decreasing trend in amplitude as function of wavelength.
+\shb, on the other hand, shows highly significant variability with a decreasing trend in amplitude as function of wavelength.
 In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
@@
 As with $A_1$, the amplitude spectrum decreases as a function of wavelength, indicating Mie scattering grains and that the higher frequency term is likely just smaller scale cloud structures with similar properties as the longer timescale variability.
-As with Figure \ref{fig:ampSpec}, we find no strong phase shift for the second time of maximum variation $t_2$ as a function of wavelength.
+As with Figure \ref{fig:ampSpec}, we find no significant wavelength dependence on the time of maximum variation, $t_2$.
 
-The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, also shown in Figure \ref{fig:ampspec1821}.
-The HST WFC3 maximum over minimum flux spectrum is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be 
+The same trend of decreasing variability amplitude for \shb\ was observed by HST's WFC3 grism over a shorter wavelength range (1.1 to 1.7~$\mu$m) by \citet{2015ApJ...798L..13Y}, shown in Figure \ref{fig:ampspec1821}.
+The HST WFC3 maximum over minimum flux spectrum ($f_R$) is converted to an amplitude spectrum by assuming that the amplitude is half the difference in maximum and minimum flux, which can be shown to be
 \begin{equation}\label{eq:ampFromRatio}
@@
 \end{equation}
-where $f_R$ is the flux ratio of the maximum over minimum flux.
-There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum because they were taken at different epochs and presumably have different spatial cloud and temperature distributions.
-\citet{2015ApJ...798L..13Y} find that the WFC3 spectrum has no significant water vapor absorption which indicates a high haze layer in 2MASS J1821 and is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
+There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum that may be due to different spatial cloud and temperature distributions  different epochs.
+\citet{2015ApJ...798L..13Y} find that the WFC3 amplitude spectrum has no significant water vapor absorption which indicates a high haze layer in {\shb}.
+This is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
 
@@
 We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud is confined to one hemisphere of the brown dwarf (i.e., maximum surface heterogeneity), the amplitude of the variability ($A_1$) is directly proportional to the opacity of the particles.
+If we assume the cloud is confined to one hemisphere of the brown dwarf (i.e., maximum surface heterogeneity), the amplitude of the variability is directly proportional to the opacity of the particles.
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
@@
 
-For the particle size distribution we assume a log-normal distribution around a characteristic size, $s$ and a standard deviation of the logarithm (scale parameter), $\sigma$ =0.5.
-The spectral dependence is therefore modeled as 
+For the particle size distribution we assume a log-normal distribution with a median radius $r$ and width (scale parameter) $\sigma$.
+The spectral dependence is modeled as 
 \begin{equation}
-A_1 = B \bar{Q_{avg}}(r,\sigma)
+A = B \bar{Q_{avg}}(r,\sigma)
 \end{equation}
-where $A_1$ is the amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r,\sigma)$ is the average extinction coefficient averaged over all particles in the log-normal distribution with a median radius of $r$ and scale parameter $\sigma$.
-When fitting the amplitude spectra to our Mie model, we impose a prior on the median particle size radius ($0 \mu m < r < 5 \mu m$).
-Beyond 5~$\mu$m the models are essentially unchanged with median particle radius.
+where $A$ is the variability amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r,\sigma)$ is the average extinction coefficient averaged over all particles in the log-normal distribution.
+When fitting the amplitude spectra to our Mie model, we imposed a prior of $r < 5 \mu m$; beyond this scale, the models are essentially unchanged with median particle radius.
 
@@
 We show the maximum likelihood model which has a near-zero amplitude.
-For \shb\ we find that the amplitude spectrum is well-fit by a Mie scattering model and the median particle radius is reasonably constrained.
-Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.28~$\mu$m grains.
-This model has a reduced $\chi^2$ of 1.08 and is consistent with the measured amplitude spectrum.
+For {shb}, we find that the amplitude spectrum is well-fit by a Mie scattering model and the median particle radius is reasonably constrained.
+Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.28~$\mu$m grains and $\sigma$ = 0.3.
+This model has a reduced $\chi^2$ of 1.08 and is thus consistent with the measured amplitude spectrum.
 
 Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$, $r$ and $\sigma$ parameters.
-The derived median particle radius is $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for our assumptions of optically thin clouds and a log-normal particle size distribution.
+The derived median particle radius is $r$ = 0.24$^{+0.05}_{-0.07}$~$\mu$m 
+and $\sigma$ = 0.32$^{+0.15}_{-0.12}$.
 We show the maximum likelihood particle size distribution in the inset of Figure \ref{fig:corner1821mie} as well as a series of other possible distributions from the MCMC fitting.
@@
 \citet{hiranaka2016subMicronDust} find that the observed spectra of reddened L dwarfs can be explained by extinction from a haze layer of sub-micron forsterite grains.
-They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarf stars.
-Our median particle radius of $r$=0.24 $^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
+They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarfs.
+Our median particle radius of $r$=0.24$^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or of WISEP J0047+6803.
 
@@
 
-We observed two brown dwarfs of spectral type L4-L5: 2MASS 1821 and 2MASS 0835.
+We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral type L4-L5: {\sha} and {\shb}.
 These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
-We obtained high precision ground-based spectrophotometry of both systems to measure the variability spectra of these systems with the IRTF.
-After fitting sinusoids to both of the time series, we find that 2MASS 0835 has low levels of variability and no significant wavelength dependence.
+We find that {\sha} has marginal variability and no significant wavelength dependence; while
+{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines towards the near infrared (2.4$~\mu$m).
+A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
+Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
 
-2MASS J1821 shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which decreases towards the near infrared (2.4$~\mu$m).
-This is consistent with HST measurements for the system that show a gradual decrease in variability amplitude with wavelength \citep{2016ApJ...826....8Y} from 1.1~$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band.
-The lack of the variability in the water vapor bands gives evidence of a high altitude aerosol layer in the atmosphere.
+The variability of {\shb} is consistent with previous HST measurements for the system that also show a gradual decrease in variability amplitude with wavelength from 1.1~$\mu$m to 1.7 $\mu$m with no decrease in the water vapor band \citep{2016ApJ...826....8Y}.
+The lack of the variability in the water vapor bands in both the WFC3 data and the data presented here supports evidence of a high altitude aerosol layer in the atmosphere of this L dwarf.
 We find no statistically significant phase offsets in the light curves for \sha\ nor \shb\ from wavelength to wavelength.
-This is different from  \citep{2016ApJ...826....8Y} who found a significant phase offset using simultaneous Spitzer and HST light curves at two different epochs.
-This may be due to the different pressures probed by the Spitzer Channel's 1 and 2 (3.6 $\mu$m and 4.5 $\mu$m) not found in our wavelength range.
+This is different from  \citep{2016ApJ...826....8Y} who found a significant phase offset using simultaneous {\em Spitzer} and {\em HST} light curves at two different epochs.
+This may be due to the larger differences in pressures probed by the {\em Spitzer} observations (3.6 $\mu$m and 4.5 $\mu$m), not sampled by our more restricted wavelength range.
 
-We fit the variability amplitude spectrum with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
-A log-normal particle size distribution fits the data with a median grain radius of 0.24 $^{+0.05}_{-0.07}$ $\mu$m.
+We fit the variability amplitude spectrum of {\shb} with an optically thin Mie scattering model and find it is consistent with forsterite grains with sub-micron sized particles.
+A log-normal particle size distribution reproduces the data with a median grain radius of 0.24$^{+0.05}_{-0.07}$ $\mu$m.
 However, considering different particle compositions and grain geometries can widen the allowed range of particle sizes.
@@
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
-This research has made use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at exoplanets.org.
-This research made use of the \texttt{astropy} package \citep{astropy2013}.
+The material is based upon work supported by
+the National Aeronautics and Space Administration under
+Grant No.~NNX15AI75G. 
+This research has made
+use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at \url{http://exoplanets.org}; SIMBAD database, operated at CDS, Strasbourg,
+France; NASA’s Astrophysics Data System Bibliographic
+Services; the M, L, T, and Y dwarf compendium
+housed at \url{http://DwarfArchives.org}; the SpeX Prism
+Libraries at \url{http://www.browndwarfs.org/spexprism}; and the \texttt{astropy} package \citep{astropy2013}. 
 The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.
@@
 
-We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}.
-The original light curves show significant variations as a function of time and airmass.
+We show the original light curves used in model fitting in Figure \ref{fig:tserNoDetrend}, which preserve the significant variations of flux as a function of time and airmass.
 Our sinusoidal model using Equation \ref{eq:cosfit} is shown for each of the light curves in Figure \ref{fig:tserNoDetrend}.

### 2017-07-13 ms.tex
slight update to acknowledgements, taking out the exoplanets.org ref.

@@
 This research has made
-use of the Exoplanet Orbit Database and the Exoplanet Data Explorer at \url{http://exoplanets.org}; SIMBAD database, operated at CDS, Strasbourg,
-France; NASA’s Astrophysics Data System Bibliographic
+use of the SIMBAD database, operated at CDS, Strasbourg,
+France; NASA'۪s Astrophysics Data System Bibliographic
 Services; the M, L, T, and Y dwarf compendium

### 2017-07-14 ms.tex
fixed a few typos as well as mixups (like Nints between 2MASS 0835/2MASS 1821) in preparation for submission.

@@
 Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
-\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star Corot-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
-This was sufficient to infer the presence of a cloud/haze layer in Corot-1b via transmission spectroscopy.
+\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
+This was sufficient to infer the presence of a cloud/haze layer in CoRoT-1b via transmission spectroscopy.
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
@@
 \colhead{$v\sin{i}$} & 
-\colhead{$i$\tablenotemark{a}} \\
+\colhead{$i$\tablenotemark{b}} \\
  &  \colhead{Opt} & \colhead{NIR\tablenotemark{a}} &  \colhead{(pc)} & &  & &  \colhead{(K)} & \colhead{(hr)} & \colhead{(km/s)} & \colhead{($\degr$)} \\
@@
 \startdata
-\sha\ & L5$^{(1)}$ & L7 & 7.27$\pm$0.02$^{(2)}$ & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08$^{(3)}$ & 1754$\pm$112$^{(3)}$ & 3.1\tablenotemark{b}$^{(4)}$ & 14.18$\pm$0.43$^{(5)}$ & 21 \\
+\sha\ & L5$^{(1)}$ & L7 & 7.27$\pm$0.02$^{(2)}$ & 11.94$\pm$0.02 & 2.03$\pm$0.03 & $-$4.05$\pm$0.08$^{(3)}$ & 1754$\pm$112$^{(3)}$ & 3.1\tablenotemark{c}$^{(4)}$ & 14.18$\pm$0.43$^{(5)}$ & 21 \\
 \shb\ & L4.5p$^{(6)}$ & L5 & 9.38$\pm$0.03$^{(7)}$ & 12.40$\pm$0.02 & 1.78$\pm$0.03 & $-$4.18$\pm$0.03$^{(8)}$ & 1635$\pm$66$^{(8)}$ & 4.2$\pm$0.1$^{(9)}$ & 28.85$\pm$0.16$^{(5)}$ & 76 \\
@@
 Each image is centered on the target, and span a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
-The comparison stars referred to in the text appear as blue sources in these images.
-	For \sha\, we use the comparison star to the left and for \shb\ to the lower right.}
+The comparison stars referred to in the text appear as blue or white sources in these images.
+	For \sha\, we use the comparison star to the left and for \shb\ to the right on the edge of this image.}
 	\label{fig:images}
@@
 
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 8.52$\pm$0.08~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
 This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
 Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius\footnote{We adopt the equatorial radius of Jupiter, {\rjup} = 7.15$\times$10$^9$~cm.} R = 1~{\rjup}.
-There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 19$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
 
 2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
-This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}, suggesting a near equator-on orientation.
+This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.
 \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
-There are two suitably bright comparison stars within 20$\arcsec$ for relative calibration: 2MASS~J18212812+1414089 with $H$ = 12.6 at 7$\arcsec$ separation and 2MASS~J18212715+1413482 with $H$ = 12.0 at 19$\arcsec$ separation; we chose the latter for our monitoring observations.
+There are three suitably bright comparison stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
+We chose 2MASS~J18212622+1414064 with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
 
@@
 \startdata
-{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 352 & 60 & 7.47 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
-{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 363 & 45 & 4.65 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
+{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
+{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
 \enddata
@@
 The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
-Integration times were 60~s and 45~s for {\sha} and {\shb}, respectively.
+Integration times were 45~s and 60~s for {\sha} and {\shb}, respectively.
 The short-wavelength limit of our spectral coverage was set by the use of a 0.9~$\mu$m dichroic which deflected optical light into the MIT Optical Rapid Imaging System (MORIS) camera \citep{2011PASP..123..461G}, which was used for $i$-band guiding.
@@
 We show the maximum likelihood model which has a near-zero amplitude.
-For {shb}, we find that the amplitude spectrum is well-fit by a Mie scattering model and the median particle radius is reasonably constrained.
+For \shb, we find that the amplitude spectrum is well-fit by a Mie scattering model and the median particle radius is reasonably constrained.
 Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.28~$\mu$m grains and $\sigma$ = 0.3.

### 2017-08-04 ms.tex
shrank the size of the table of brown dwarf properties since I got a formatting error back from AAS Journals.
updated software references using the \software command

@@
 \begin{abstract}
-Low-temperature L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
+\textbf{L dwarfs} exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
 The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds.
-Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
+Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs \textbf{that have variability reported in the literature}, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
 By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
@@
 The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
-We detect no statistically significant phase variations with wavelength.
-The different variability behaviors of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
+\textbf{We do not detect} statistically significant phase variations with wavelength.
+The different variability \textbf{behavior} of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
 \end{abstract}
@@
 The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
-In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}
-whose surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
-Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), and virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
+In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}\textbf{,
+whose} surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
+Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}) \textbf{and} virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
 Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
 
-Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
-The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature, ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
+Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows \textbf{for} the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
+The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} \textbf{and} amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) \textbf{and} surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
 Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
 Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations.
-Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact wiht clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.
+Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact \textbf{with} clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.
 
 Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
-Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient calibrators \citep{2003MNRAS.339..477B}.
-In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision, and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
-However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity, or evolution in variability modes.
+Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient \textbf{numbers of nearby reference stars which can be used to correct time-variable telluric absorption} \citep{2003MNRAS.339..477B}.
+In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision \textbf{and} have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
+However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity \textbf{or} evolution in variability modes.
 
-Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which references stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
-\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide (3$\arcsec$) slit.
-This was sufficient to infer the presence of a cloud/haze layer in CoRoT-1b via transmission spectroscopy.
+Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which \textbf{reference stars} are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
+\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide \textbf{and long (3$\arcsec \times 60 \arcsec$) slit.} This was sufficient to infer the presence of a cloud/haze layer in CoRoT-1b via transmission spectroscopy.
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
@@
 
-\begin{deluxetable*}{lllllllllll}
+\begin{deluxetable*}{llllllllllr}
 \tablecaption{Brown Dwarf Properties}\label{tab:bdProp}
 \tablewidth{0pt}
-\tabletypesize{\footnotesize}
+\tabletypesize{\scriptsize}
 \tablehead{
@@
 Each image is centered on the target, and span a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
-The comparison stars referred to in the text appear as blue or white sources in these images.
-	For \sha\, we use the comparison star to the left and for \shb\ to the right on the edge of this image.}
+The \textbf{reference} stars referred to in the text appear as blue or white sources in these images.
+	For \sha\, we use the \textbf{reference} star to the left and for \shb\ to the right on the edge of this image.}
 	\label{fig:images}
@@
 We identified potential targets for relative spectro-photometry by selecting among the $\approx$200 known L dwarfs\footnote{We identified these sources from DwarfArchives,  \url{http://dwarfarchives.org}.
-The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) visual binary companions at apparent separations of 5$\arcsec$--30$\arcsec$.
-We identified 30 potential targets, and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
+The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree}.
+\textbf{We downselected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) \textbf{reference stars} at apparent separations of 5$\arcsec$--30$\arcsec$.
+We identified 30 potential targets \textbf{and} prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
 Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
 
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of low surface gravity \citep{2016ApJ...833...96L}.
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of \textbf{low surface gravity \citep[][however, see \citet{2015ApJS..219...33G}]{2016ApJ...833...96L}.
+There is no Li I absorption reported for this source \citep{2003AJ....126.2421C,2015ApJS..220...18B}; however its low temperature \citep[T$_{eff}$=1800~K][]{2015ApJS..219...33G} and likely youth ($<$1 Gyr) is consistent with a mass below the hydrogen-burning mass limit \citep{2003A&A...402..701B,2000ApJ...531..438B}.}
 This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
 Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius\footnote{We adopt the equatorial radius of Jupiter, {\rjup} = 7.15$\times$10$^9$~cm.} R = 1~{\rjup}.
-There is an $H$ = 12.3 source (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+There is an $H$ = 12.3 \textbf{reference star} (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
 
-2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L}.
+2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} \textbf{and Li absorption \citep{2008ApJ...686..528L}.}
 This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.
 \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
-There are three suitably bright comparison stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
+There are three suitably bright \textbf{reference} stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
 We chose 2MASS~J18212622+1414064 with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
@@
 \section{Acknowledgements}
-MCMC fitting makes use of \texttt{emcee} \citep{foreman-mackey2013emcee} and the covariance plot was made with \texttt{corner.py} \citep{foremanCorner}.
-Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature model.
+Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature models.
 Funding for the E Schlawin is provided by NASA Goddard Spaceflight Center.
@@
 use of the SIMBAD database, operated at CDS, Strasbourg,
-France; NASA'۪s Astrophysics Data System Bibliographic
+France; NASA's Astrophysics Data System Bibliographic
 Services; the M, L, T, and Y dwarf compendium
 housed at \url{http://DwarfArchives.org}; the SpeX Prism
-Libraries at \url{http://www.browndwarfs.org/spexprism}; and the \texttt{astropy} package \citep{astropy2013}. 
+Libraries at \url{http://www.browndwarfs.org/spexprism}.
 The authors wish to recognize and acknowledge the very significant cultural role and reverence that the summit of Mauna Kea has always had within the indigenous Hawaiian community.
@@
 \facility{IRTF (SpeX)}.
+
+\textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}.
+SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.}}
 

### 2017-08-04 ms.tex
clarified the spectral rectification and background subtraction process.

@@
 Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis.
-This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differental color refraction.
+This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes \textbf{differential} color refraction.
 The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
@@
 
-The images were rectified by shifting each row to match a center row in between the two sources.
-This was achieved by cross correlating the reference row with all other detector rows (which have the same background spectrum) and fitting a smooth function over the sources as in \citealt{2016ApJ...826..156S}.
+\textbf{The 2D images were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
+This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
+A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a smooth X (spectral) shift function as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
+Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 15th order polynomial.
+The reduction software is available online\footnote{https://github.com/eas342/iraf\_and\_idl\_processing}.}
+
 We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.

### 2017-08-05 ms.tex
added reference info for IRAF and IDL.

@@
 \textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}.
-SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.}}
+SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.\texttt{IRAF} \citep{tody86}, \texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}
 

### 2017-08-05 ms.tex
edited referee comments about section 3.

@@
 This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
-A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a smooth X (spectral) shift function as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
-Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 15th order polynomial.
-The reduction software is available online\footnote{https://github.com/eas342/iraf\_and\_idl\_processing}.}
+A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a one dimensional smooth X (spectral) shift function as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
+Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 4th order polynomial.
+The reduction software is available online\footnote{https://github.com/eas342/spectral\_pipeline\_and\_scripts}.}
 
-We also obtained calibration sequences of ThAr and flat-field incadescent lamps with the 3$\arcsec$$\times$60$\arcsec$ slit  before and after the brown dwarf time series.
-An additional set of ThAr emission lamp spectra were taken at the beginning and end of the observations (preceding and following the 3$\arcsec \times 60 \arcsec$ lamp spectra) with a 0.3$\arcsec\times60\arcsec$ slit for wavelength calibration.
-% to measure pixel response and assess flexure in the instrument with telescope orientation.
+\textbf{We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
+The ThAr data is taken for wavelength calibration with the 0.3$\arcsec\times60\arcsec$ slit since it has a resolving power high enough to separate the ThAr lines and identify them.
+This wavelength calibration data is taken at the very beginning and very end of the sequence to ensure the 3$\arcsec \times 60 \arcsec$ slit is unmoved during the rest of the calibration and science data.
+Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
+We take flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
 For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response.
-To correct for instrument flexure, we also cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
+To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.}
 These shifts were used to apply a custom flat field for every image.
@@
 
-As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit to points more than 30 pixels away from the center of the source dispersion traces.
+As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit \textbf{(described above)} to points more than 30 pixels away from the center of the source dispersion traces.
 Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials along the spectral direction one row at a time with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
@@
 Our image rectification process described above ensures that the wavelength solution is the same for each row of the image.
-However, there are small additional shifts of the sources within the slit so another shift was performed between the sources to ensure that telluric features were removed when dividing the two spectra.
+However, there are small additional shifts of the sources within the \textbf{slit, so} another shift was performed between the sources to ensure that telluric features were removed when dividing the two spectra.
 
@@
 Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
-Neither the reference spectra nor the brown dwarf spectra have any corrections applied for telluric absorption or instrumental spectral response.
+Neither the reference spectra nor the brown dwarf spectra have \textbf{had} any corrections applied for telluric absorption or instrumental spectral response.
 The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric water absorption signatures

### 2017-08-06 ms.tex
addressed 4 comments from referee in section 4.

@@
 The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
-We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period of the brown dwarfs and compare it to the expected photon and read noise.
+We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period \textbf{for each brown dwarf} and compare it to the expected photon and read noise.
 In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
@@
 
-We find minimal variation in the lightcurves of {\sha}, but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
+We find minimal variation in the lightcurves of {\sha} \textbf{but} pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
 These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
@@
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-of 2.6 $< \tau < $3.6 hr for \sha]\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
+of 2.6 $< \tau < $3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
 These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
@@
 We do not put any constraints on A$_1$ relative to A$_2$.
+\textbf{The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.}
 
@@
 For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
+\textbf{If one were to average all of these K-band points together, they are consistent with a 3.4 $\pm$ 0.1 hr rotation period, though this is somewhat driven by the prior 2.6 $< \tau < $3.6 hr.}
+
 \shb, on the other hand, shows highly significant variability with a decreasing trend in amplitude as function of wavelength.

### 2017-08-06 ms.tex
finished addressing the section 4 comments.

@@
 \end{equation}
-There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum that may be due to different spatial cloud and temperature distributions  different epochs.
-\citet{2015ApJ...798L..13Y} find that the WFC3 amplitude spectrum has no significant water vapor absorption which indicates a high haze layer in {\shb}.
+There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum that may be due to different spatial cloud and temperature distributions \textbf{at} different epochs.
+\citet{2015ApJ...798L..13Y} \textbf{found} that the WFC3 amplitude spectrum has no significant water vapor \textbf{absorption, which} indicates a high haze layer in {\shb}.
 This is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
@@
 \caption{Posterior distributions to the simple Mie scattering fit to the $A_1$ amplitude spectrum for \shb\ assuming a forsterite composition.
-The model includes an amplitude offset $B$ to account for areal coverage, a median particle radius $r$, and a scale parameter $\sigma$.
+The model includes an amplitude offset $B$ to account for areal coverage, a median particle radius $r$, and a scale parameter $\sigma_s$.
 The upper right inset plot shows the log-normal particle size distribution in blue for samples drawn from the posterior distribution.
@@
 We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud is confined to one hemisphere of the brown dwarf (i.e., maximum surface heterogeneity), the amplitude of the variability is directly proportional to the opacity of the particles.
+If we assume the cloud is confined to one \textbf{East/West hemisphere of the brown dwarf (i.e., confined to longitudes between 0\degree\ and 180\degree, which produces maximum surface heterogeneity), then} the amplitude of the variability is directly proportional to the opacity of the particles.
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
 We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
-We use a constant n=1.67 - 0.006 $j$ index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.
+We use a constant n=1.67 \textbf{and k=0.006 complex} index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.
 
-For the particle size distribution we assume a log-normal distribution with a median radius $r$ and width (scale parameter) $\sigma$.
+For the particle size distribution we assume a log-normal distribution with a median radius $r$ and width (scale parameter) $\sigma_s$.
 The spectral dependence is modeled as 
 \begin{equation}
-A = B \bar{Q_{avg}}(r,\sigma)
+A = B \bar{Q_{avg}}(r,\sigma_s)
 \end{equation}
-where $A$ is the variability amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r,\sigma)$ is the average extinction coefficient averaged over all particles in the log-normal distribution.
+where $A$ is the variability amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r,\sigma_s)$ is the average extinction coefficient averaged over all particles in the log-normal distribution.
 When fitting the amplitude spectra to our Mie model, we imposed a prior of $r < 5 \mu m$; beyond this scale, the models are essentially unchanged with median particle radius.
@@
 We show the maximum likelihood model which has a near-zero amplitude.
-For \shb, we find that the amplitude spectrum is well-fit by a Mie scattering model and the median particle radius is reasonably constrained.
-Figure \ref{fig:ampspec1821} shows the best-fit model which has a median particle radius of 0.28~$\mu$m grains and $\sigma$ = 0.3.
+For \shb, we find that the amplitude spectrum is well-fit by a Mie scattering model and \textbf{that} the median particle radius is reasonably constrained.
+Figure \ref{fig:ampspec1821} shows the best-fit model\textbf{, which} has a median particle radius of 0.28~$\mu$m and $\sigma_s$ = 0.3.
 This model has a reduced $\chi^2$ of 1.08 and is thus consistent with the measured amplitude spectrum.
 
-Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$, $r$ and $\sigma$ parameters.
+Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$, $r$ and $\sigma_s$ parameters.
 The derived median particle radius is $r$ = 0.24$^{+0.05}_{-0.07}$~$\mu$m 
-and $\sigma$ = 0.32$^{+0.15}_{-0.12}$.
+and $\sigma_s$ = 0.32$^{+0.15}_{-0.12}$.
 We show the maximum likelihood particle size distribution in the inset of Figure \ref{fig:corner1821mie} as well as a series of other possible distributions from the MCMC fitting.
@@
 
-A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has very red ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
+A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has \textbf{a redder than average} ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
 In WISEP J0047+6803, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.

### 2017-08-06 ms.tex
finished referee comments on conclusions.

@@
 
-We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral type L4-L5: {\sha} and {\shb}.
+We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral \textbf{types} L4-L5: {\sha} and {\shb}.
 These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
@@
 Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
+\textbf{\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.}
 
@@
 Using ground-based facilities such as SpeX on IRTF allows us to expand our monitoring of cloud-bearing ultracool dwarfs, both in sample size and long-term tracking.
-The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations; while the latter allows us to study weather-related changes to cloud structures over multiple rotation periods.
+The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations \textbf{while} the latter allows us to study weather-related changes to cloud structures over multiple rotation periods.
 We are currently pursuing a larger monitoring sample that will be reported in future publications.
@@
 
-\textbf{\software{\texttt{emcee} \citep{foreman-mackey2013emcee}, \texttt{corner.py} \citep{foremanCorner}.
-SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B}, \texttt{astropy} \citep{astropy2013}.\texttt{IRAF} \citep{tody86}, \texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}
+\textbf{\software{
+\texttt{emcee} \citep{foreman-mackey2013emcee},
+\texttt{corner.py} \citep{foremanCorner},
+\texttt{miescatter} \citep{bohren1983mie},
+SpeX Prism Library Analysis Toolkit \citep{2017arXiv170700062B},
+\texttt{astropy} \citep{astropy2013},
+\texttt{IRAF} \citep{tody86} and
+\texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}
 

### 2017-08-08 ms.tex
explained how BT-Settl models were interpolated.

@@
 We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
+\textbf{To achieve temperatures and gravities between the pre-computed spectra in the BT-Settl atmospheric grid, we interpolated the spectra.}
 Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.

### 2017-08-11 ms.tex
started a section where I discuss relaxing the hemispheric assumption.
for now we are just saying that we're ignoring limb darkening since the models are not close matches to the spectra anyway.

@@
 $F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.
+\textbf{We have ignored limb darkening in our calculations, which affect the surface intensity of brown dwarf surfaces \citep{2011A&A...529A..75C}, but since the models are not close matches to the spectra anyway we do not consider limb darkening effects.
+Here, we are calculating the average brightness temperature of the brown dwarf surface.}
+
 Both spectra were calibrated to absolute flux densities using their 2MASS $H$ magnitudes and measured parallaxes.
@@
 
+\textbf{
+\subsubsection{Testing the Hemispheric Assumption}
+We have assumed that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.
+We discuss here the implications of relaxing our assumption. 
+}
+
 \section{Conclusions}\label{sec:conclusions}

### 2017-08-14 ms.tex
updated the brightness temperature figure for 2m1821.
added some calcs for relaxing the hemispheric assumption.

@@
 	\plottwo{classify0835.pdf}{classify1821.pdf}
-	\plottwo{tbright0835.pdf}{tbright1821.pdf}
+	\plottwo{tbright0835.png}{tbright1821.png}
 	\caption{(Top) SpeX prism spectra (in black) of {\sha} (left; \citealt{2010ApJ...710.1142B}) and {\shb} (right; \citealt{2008ApJ...686..528L}) scaled to absolute flux densities, compared to their closest-match L dwarf spectral standards as defined in \citet[in magenta]{2010ApJS..190..100K}: the L7 2MASSI~J01033203+1935361 (data from \citealt{2014ApJ...794..143B}) and the L5 SDSS~J083506.16+195304.4 (data from \citealt{2006AJ....131.2722C}), respectively.
@@
 \subsubsection{Testing the Hemispheric Assumption}
-We have assumed that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.
+We have previously assumed  that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.
+We assumed that the clouds were confined to one East-West hemisphere between longitudes 0\degree\ and 180\degree.
 We discuss here the implications of relaxing our assumption. 
+Let $\alpha_{min}$ and $\alpha_{max}$ be the minimum and maximum cloud coverage.
+If we assume that the clouds are optically thin, the ratio of maximum over minimum flux is
+\begin{equation}
+f_{R,NH} = \frac{1 - \tau \alpha_{min}}{1 - \tau \alpha_{max}},
+\end{equation}
+where $\tau$ is the clouds' optical depth and the $NH$ subscript denotes no hemispheric assumption.
+Using Equation \ref{eq:ampFromRatio}, the amplitude is
+\begin{equation}
+A_{NH} = \frac{\tau \left(\alpha_{max} - \alpha_{min} \right)}{2 - \tau \left(\alpha_{max} + \alpha_{min} \right)}.
+\end{equation}
+In the optically thin case ($\tau \ll1$) the linear term dominates, so the the amplitude, $A_{NH}$, is proportional to the optical depth $\tau$.
+So, only in the case where $\tau \gtrsim 1$ does the East-West hemispheric assumption break down. 
 }
-
 \section{Conclusions}\label{sec:conclusions}

### 2017-08-15 ms.tex
Reading through the abstract to halway in section 2 for typos and other fixes.

@@
 \textbf{L dwarfs} exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
-The spectral character of these variations yield insight into the particle sizes and vertical structure of the clouds.
+The spectral character of these variations \textbf{yields} insight into the particle sizes and vertical structure of the clouds.
 Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs \textbf{that have variability reported in the literature}, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
@@
 Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which \textbf{reference stars} are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
-\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby visual binary companion in a wide \textbf{and long (3$\arcsec \times 60 \arcsec$) slit.} This was sufficient to infer the presence of a cloud/haze layer in CoRoT-1b via transmission spectroscopy.
+\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby \textbf{reference star} in a wide \textbf{and long (3$\arcsec \times 60 \arcsec$) slit.}
+This was sufficient to infer the presence of a cloud/haze layer \textbf{and disfavor TiO/VO absorption} in CoRoT-1b via transmission spectroscopy.
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
@@
 	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).
-Each image is centered on the target, and span a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
-The \textbf{reference} stars referred to in the text appear as blue or white sources in these images.
-	For \sha\, we use the \textbf{reference} star to the left and for \shb\ to the right on the edge of this image.}
+Each image is centered on the target \textbf{and spans} a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
+	The \textbf{reference stars labeled in each image are observed simultaneously in the 3$\arcsec \times 60 \arcsec$ SpeX slit to remove telluric variability.}}
 	\label{fig:images}
@@
 There are three suitably bright \textbf{reference} stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
-We chose 2MASS~J18212622+1414064 with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
+We chose 2MASS~J18212622+1414064 \textbf{(Visible in Figure~\ref{fig:images})} with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
 
@@
 obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
-Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicate near-infrared
+Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} \textbf{indicates} near-infrared
 classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}).
@@
 $F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.
-\textbf{We have ignored limb darkening in our calculations, which affect the surface intensity of brown dwarf surfaces \citep{2011A&A...529A..75C}, but since the models are not close matches to the spectra anyway we do not consider limb darkening effects.
-Here, we are calculating the average brightness temperature of the brown dwarf surface.}
+\textbf{We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
+Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.}
 
@@
 \end{equation}
-In the optically thin case ($\tau \ll1$) the linear term dominates, so the the amplitude, $A_{NH}$, is proportional to the optical depth $\tau$.
-So, only in the case where $\tau \gtrsim 1$ does the East-West hemispheric assumption break down. 
+In the optically thin case ($\tau \ll1$) the linear term dominates, so the amplitude, $A_{NH}$, is proportional to the optical depth $\tau$ and our assumption that $A = B \bar{Q_{avg}(r,\sigma_s)}$ is valid.
+Only in the case where $\tau \gtrsim 1$ does the East-West hemispheric assumption break down. 
 }

### 2017-08-15 ms.tex
went through section 2 for typos/fixes.

@@
 \begin{equation}
-T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1}
+T_{\lambda,surf} = \frac{hc}{k\lambda}\left[\ln\left(1+\frac{2\pi{hc^2}}{F_{\lambda,surf}\lambda^5}\right)\right]^{-1},
 \end{equation}
@@
 \begin{equation}
-F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2
+F_{\lambda,surf} = {\pi}B_{\lambda} = F_{\lambda,obs}\left(\frac{d}{R}\right)^2 = F_{\lambda,abs}\left(\frac{10~{\rm pc}}{R}\right)^2.
 \end{equation}
-$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ the source distance and $R$ the source radius.
+$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ \textbf{is} the source distance and $R$ \textbf{is} the source radius.
 \textbf{We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
@@
 
+\section{Observations}\label{sec:obs}
 \begin{deluxetable*}{lccccccccc}
@@
 \end{deluxetable*}
-
-\section{Observations}\label{sec:obs}
 
@@
 \textbf{
-\subsubsection{Testing the Hemispheric Assumption}
+\subsubsection{Exploring the Hemispheric Assumption}
 We have previously assumed  that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.

### 2017-08-16 ms.tex
more editing through section 4.1

@@
 The duration is the total time from start to end of the observations including array sampling and overheads.
-The FWHM is the measured full width half maximum of the spatial point spread function around 1.6$\mu$m, taken as the median value over the entire time series.}
+The FWHM is the measured full width half maximum of the spatial point spread function around \textbf{H band (1.7$\mu$m)}, taken as the median value over the entire time series.}
 \end{deluxetable*}
@@
 This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes \textbf{differential} color refraction.
-The effective resolution of the spectral data, set by seeing and pointing errors, are $\lambda$/$\Delta\lambda$ $\approx$ 50.
+The effective resolution of the spectral data, set by seeing and pointing errors, \textbf{was} $\lambda$/$\Delta\lambda$ $\approx$ 50.
 Integration times were 45~s and 60~s for {\sha} and {\shb}, respectively.
@@
 This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
-A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a one dimensional smooth X (spectral) shift function as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
+A third order polynomial was fit to the cross correlation peaks (masking out the sources) to determine a one dimensional smooth X (spectral) shift solution as a function of Y (spatial) position  \citep{2016ApJ...826..156S}.
 Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 4th order polynomial.
@@
 We take flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
-For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response.
+For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum.
 To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.}
@@
 
-As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit \textbf{(described above)} to points more than 30 pixels away from the center of the source dispersion traces.
+As described in \citet{2016ApJ...826..156S}, we performed spatial background subtraction over the entire slit using a 4th-order polynomial fit to points more than 30 pixels away from the center of the source dispersion traces.
 Spectra were optimally extracted \citep{1986ApJ...302..757H}, with spatial profiles fit to low order polynomials along the spectral direction one row at a time with 20$\sigma$ rejection to remove cosmic rays and bad pixels.
@@
 Typical signal-to-noise of the extracted spectra were 40 - 100 per spectral pixel (unbinned).
-Relative spectra (source/reference) were then computed for each exposure.
+Relative spectra (source \textbf{divided by} reference) were then computed for each exposure.
 Our image rectification process described above ensures that the wavelength solution is the same for each row of the image.
@@
 \shb\ has significant variability over wavelengths $<$1.7$\micron$ with a strong spectral slope.
-	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained on a different epoch, but show a similar slope.
+	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained \textbf{at} a different epoch, but show a similar slope.
 	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle size of 0.28 $\mu$m.
@@
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-of 2.6 $< \tau < $3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
+\textbf{We impose} 2.6 $< \tau < $3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
 These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
@@
 For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
-\textbf{If one were to average all of these K-band points together, they are consistent with a 3.4 $\pm$ 0.1 hr rotation period, though this is somewhat driven by the prior 2.6 $< \tau < $3.6 hr.}
+\textbf{If one were to average all of the K-band points together, they are consistent with a 3.4 $\pm$ 0.1 hr rotation period, though this is somewhat driven by the prior 2.6 $< \tau < $3.6 hr.}
 
@@
 In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
-The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}.
+The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}, \textbf{4.2$\pm$0.1 hr}.
 If we optimistically assume all wavelengths are statistically independent, the weighted average rotation period is 4.10 $\pm$ 0.03 hours.

### 2017-08-17 ms.tex
relabeled variables and finished read-through of analysis and conclusion.

@@
 	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained \textbf{at} a different epoch, but show a similar slope.
-	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle size of 0.28 $\mu$m.
+	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle \textbf{radius} of 0.28 $\mu$m.
 	 In all plots the regions potentially contaminated by telluric absorption are shaded in light green.
@@
 \caption{Posterior distributions to the simple Mie scattering fit to the $A_1$ amplitude spectrum for \shb\ assuming a forsterite composition.
-The model includes an amplitude offset $B$ to account for areal coverage, a median particle radius $r$, and a scale parameter $\sigma_s$.
+The model includes an amplitude offset $K$ to account for areal coverage, a median particle radius $r$ and a scale parameter $\sigma_s$.
 The upper right inset plot shows the log-normal particle size distribution in blue for samples drawn from the posterior distribution.
@@
 
-We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an optically thin cloud layer consisting of a log-normal distribution of particle sizes.
-If we assume the cloud is confined to one \textbf{East/West hemisphere of the brown dwarf (i.e., confined to longitudes between 0\degree\ and 180\degree, which produces maximum surface heterogeneity), then} the amplitude of the variability is directly proportional to the opacity of the particles.
+We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an \textbf{optically thin grouping of clouds} consisting of a log-normal distribution of particle sizes.
+\textbf{
+Let $\alpha_{min}$ and $\alpha_{max}$ be the minimum and maximum cloud coverages corresponding to the maximum and minimum flux levels, respectively.
+If we assume that the clouds are optically thin ($\tau \ll 1$), the ratio of maximum over minimum flux is
+\begin{equation}
+f_{R,Clouds} = \frac{1 - \tau \alpha_{min}}{1 - \tau \alpha_{max}},
+\end{equation}
+where $\tau$ is the clouds' optical depth.
+Using Equation \ref{eq:ampFromRatio}, the amplitude is
+\begin{equation}
+A_{Clouds} = \frac{\tau \left(\alpha_{max} - \alpha_{min} \right)}{2 - \tau \left(\alpha_{max} + \alpha_{min} \right)}.
+\end{equation}
+In the optically thin case ($\tau \ll1$) the linear term dominates, so the amplitude, $A_{Clouds}$, is proportional to the optical depth $\tau$.
+For the particle size distribution we assume a log-normal distribution with a median radius $r$ and width (scale parameter) $\sigma_s$ so our model reduces to
+\begin{equation}
+A_{Clouds} \approx K Q_{avg}(r,\sigma_s)
+\end{equation}
+where $A_{Clouds}$ is the variability amplitude, $K$ is a constant encapsulating the area and column density and $Q_{avg}(r,\sigma_s)$ is the extinction coefficient averaged over all particles.}
+
 We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
@@
 We use a constant n=1.67 \textbf{and k=0.006 complex} index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.
-
-For the particle size distribution we assume a log-normal distribution with a median radius $r$ and width (scale parameter) $\sigma_s$.
-The spectral dependence is modeled as 
-\begin{equation}
-A = B \bar{Q_{avg}}(r,\sigma_s)
-\end{equation}
-where $A$ is the variability amplitude, $B$ is a constant encapsulating the area and column density and $\bar{Q_{avg}}(r,\sigma_s)$ is the average extinction coefficient averaged over all particles in the log-normal distribution.
 When fitting the amplitude spectra to our Mie model, we imposed a prior of $r < 5 \mu m$; beyond this scale, the models are essentially unchanged with median particle radius.
@@
 
-Figure \ref{fig:corner1821mie} shows the posterior distribution for the $B$, $r$ and $\sigma_s$ parameters.
+Figure \ref{fig:corner1821mie} shows the posterior distribution for the $K$, $r$ and $\sigma_s$ parameters.
 The derived median particle radius is $r$ = 0.24$^{+0.05}_{-0.07}$~$\mu$m 
@@
 
-\textbf{
-\subsubsection{Exploring the Hemispheric Assumption}
-We have previously assumed  that the there is maximum surface heterogeneity on the brown dwarf to produce the rotationally-modulated flux variations and fit for the particle size distribution.
-We assumed that the clouds were confined to one East-West hemisphere between longitudes 0\degree\ and 180\degree.
-We discuss here the implications of relaxing our assumption. 
-Let $\alpha_{min}$ and $\alpha_{max}$ be the minimum and maximum cloud coverage.
-If we assume that the clouds are optically thin, the ratio of maximum over minimum flux is
-\begin{equation}
-f_{R,NH} = \frac{1 - \tau \alpha_{min}}{1 - \tau \alpha_{max}},
-\end{equation}
-where $\tau$ is the clouds' optical depth and the $NH$ subscript denotes no hemispheric assumption.
-Using Equation \ref{eq:ampFromRatio}, the amplitude is
-\begin{equation}
-A_{NH} = \frac{\tau \left(\alpha_{max} - \alpha_{min} \right)}{2 - \tau \left(\alpha_{max} + \alpha_{min} \right)}.
-\end{equation}
-In the optically thin case ($\tau \ll1$) the linear term dominates, so the amplitude, $A_{NH}$, is proportional to the optical depth $\tau$ and our assumption that $A = B \bar{Q_{avg}(r,\sigma_s)}$ is valid.
-Only in the case where $\tau \gtrsim 1$ does the East-West hemispheric assumption break down. 
-}
 \section{Conclusions}\label{sec:conclusions}
@@
 We find that {\sha} has marginal variability and no significant wavelength dependence; while
-{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines towards the near infrared (2.4$~\mu$m).
+{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines toward the near infrared (2.4$~\mu$m).
 A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.

### 2017-08-30 ms.tex
went through the difference between this and the originally submitted paper to check if there was anything I forgot to put in boldface. Only found 1 word like this that was bovious.

@@
 We find that {\sha} has marginal variability and no significant wavelength dependence; while
-{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m) which declines toward the near infrared (2.4$~\mu$m).
+{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m), which declines \textbf{toward} the near infrared (2.4$~\mu$m).
 A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.

### 2017-08-30 ms.tex
corrected another inconsistent name for the reference star in the abstract.

@@
 Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs \textbf{that have variability reported in the literature}, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
-By simultaneously observing a nearby visual companion, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
+By simultaneously observing a \textbf{nearby reference star}, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
 We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.

### 2017-08-30 ms.tex
fixed typos after reading aloud through sections 1 and 2.

@@
 The atmospheres of L-type stars and brown dwarfs (1300~K $\lesssim$ {\teff} $\lesssim$ 2200~K; \citealt{2015ApJ...810..158F}) are sufficiently cool that species of mineral and metal condensates form spontaneously in their atmospheres \citep{1996A&A...305L...1T,2010ApJ...716.1060V}.
-In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}\textbf{,
-whose} surface and vertical structure may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}), and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
-Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}) \textbf{and} virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
+In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}.
+\textbf{These structures} may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) \textbf{and} long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
+Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
 Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
@@
 \citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby \textbf{reference star} in a wide \textbf{and long (3$\arcsec \times 60 \arcsec$) slit.}
-This was sufficient to infer the presence of a cloud/haze layer \textbf{and disfavor TiO/VO absorption} in CoRoT-1b via transmission spectroscopy.
+This was sufficient to infer the presence of a cloud/haze layer \textbf{or disfavor TiO/VO absorption} in CoRoT-1b via transmission spectroscopy.
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
@@
 There are three suitably bright \textbf{reference} stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
-We chose 2MASS~J18212622+1414064 \textbf{(Visible in Figure~\ref{fig:images})} with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
+We chose 2MASS~J18212622+1414064 \textbf{(visible in Figure~\ref{fig:images})} with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
 
@@
 For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
-For {\shb}, we assumed an lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}.
-The Baraffe et al.\ evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.
+For {\shb}, we assumed \textbf{a} lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}.
+The \textbf{\citet{2003A&A...402..701B}} evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.
 

### 2017-08-31 ms.tex
removed the UT end time since its redundant information with the Duration column in the observation table.
finished reading aloud and touching up sections 3-6 + appendix.

@@
 \section{Observations}\label{sec:obs}
-\begin{deluxetable*}{lccccccccc}
+\begin{deluxetable*}{lcccccccc}[b]
 \tablecaption{Observations\label{tab:obsParam}}
@@
 \tablehead{
- & \multicolumn{3}{c}{Observation Epoch (UT)} \\
- \cline{2-4}
+ & \multicolumn{2}{c}{Observation Epoch (UT)} \\
+ \cline{2-3}
 \colhead{Target} & 
@@
 \colhead{Start} & 
-\colhead{End} & 
 \colhead{$N_{int}$} & 
@@
 \colhead{FWHM \@ $H$} \\
- & &  &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
+ & &  & & \colhead{(s)} & \colhead{(hr)} & \colhead{Start-End} & & \colhead{(\arcsec)}}
 \startdata
-{\sha} & 2015-12-31 & 09:35:10 & 14:14:22 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
-{\shb} & 2016-06-25 & 07:29:31 & 14:57:58 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
+{\sha} & 2015-12-31 & 09:35:10 & 272 & 45 & 4.65 & 1.59-1.28 & J08354383-0819212 & 0.5 \\
+{\shb} & 2016-06-25 & 07:29:31 & 352 & 60 & 7.47 & 1.42-2.15 & J18212622+1414064 & 0.5 \\
 \enddata
@@
 The duration is the total time from start to end of the observations including array sampling and overheads.
-The FWHM is the measured full width half maximum of the spatial point spread function around \textbf{H band (1.7$\mu$m)}, taken as the median value over the entire time series.}
+The FWHM is the measured full width \textbf{at} half maximum of the spatial point spread function around \textbf{H band (1.7$\mu$m)}, taken as the median value over the entire time series.}
 \end{deluxetable*}
@@
 \end{equation}
-where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
+where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is \textbf{the} period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-\textbf{We impose} 2.6 $< \tau < $3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
+\textbf{We impose} 2.6 $< \tau <$ 3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
 These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
@@
 
-We model the single particle extinction coefficient, $Q_{ext}$ from the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
+We model the single particle extinction coefficient, $Q_{ext}$ \textbf{with} the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
 We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
@@
 They find typical mean particle radii of 0.15 to 0.35 $\mu$m for a sample of L dwarfs.
-Our median particle radius of $r$=0.24$^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or of WISEP J0047+6803.
+Our median particle radius of $r$=0.24$^{+0.05}_{-0.07}$~$\mu$m for \shb\ is consistent with this range and may represent a partially cloudy version of the reddened brown dwarfs in \citet{hiranaka2016subMicronDust} or WISEP J0047+6803.
 
@@
 \section{Acknowledgements}
+\textbf{Thanks to the anonymous referee for useful improvements and corrections to this work.}
 Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature models.
@@
 Our sinusoidal model using Equation \ref{eq:cosfit} is shown for each of the light curves in Figure \ref{fig:tserNoDetrend}.
-For Figure~\ref{fig:tserDetrend} we remove the fit the baseline variations to show the astrophysical modulations due to brown dwarf rotation.
+For Figure~\ref{fig:tserDetrend} we remove the baseline variations to show the astrophysical modulations due to brown dwarf rotation.
 
@@
 	Each wavelength bin is labeled on the right side.
-Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near edges of telluric absorption features at 1.32$\mu$m and 1.81$\mu$m.
+Significant variations in the baseline are modeled as linear functions of airmass and time which are most prominent near edges of telluric absorption features at 1.3$\mu$m and 1.8$\mu$m.
 	Green brackets show regions where telluric absorption can contaminate the time series.}

### 2017-09-08 ms.tex
removed all \textbf commands since we will have new highlighed changes.

@@
 \begin{abstract}
-\textbf{L dwarfs} exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
-The spectral character of these variations \textbf{yields} insight into the particle sizes and vertical structure of the clouds.
-Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs \textbf{that have variability reported in the literature}, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
-By simultaneously observing a \textbf{nearby reference star}, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
+L dwarfs exhibit low-level, rotationally-modulated photometric variability generally associated with heterogeneous, cloud-covered atmospheres.
+The spectral character of these variations yields insight into the particle sizes and vertical structure of the clouds.
+Here we present the results of a high precision, ground-based, near-infrared, spectral monitoring study of two mid-type L dwarfs that have variability reported in the literature, 2MASS~J08354256$-$0819237 and 2MASS~J18212815+1414010, using the SpeX instrument on the Infrared Telescope Facility.
+By simultaneously observing a nearby reference star, we achieve $<$0.15\% per-band sensitivity in relative brightness changes across the 0.9--2.4$\mu$m bandwidth.
 We find that 2MASS~J0835$-$0819 exhibits marginal ($\lesssim$ 0.5\% per band) variability with no clear spectral dependence, while 2MASS~J1821+1414 varies by up to $\pm$1.5\% at 0.9~$\mu$m, with the variability amplitude declining toward longer wavelengths.
 The latter result extends the variability trend observed in prior $HST$/WFC3 spectral monitoring of 2MASS~J1821+1414, and we show that the full 0.9--2.4~$\mu$m variability amplitude spectrum can be reproduced by Mie extinction from dust particles with a log-normal particle size distribution with a median radius of 0.24 $\mu$m.
-\textbf{We do not detect} statistically significant phase variations with wavelength.
-The different variability \textbf{behavior} of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
+We do not detect statistically significant phase variations with wavelength.
+The different variability behavior of 2MASS~J0835$-$0819 and  2MASS~J1821+1414 suggests dependencies on viewing angle and/or overall cloud content, underlying factors that can be examined through a broader survey.
 \end{abstract}
@@
 In addition to influencing spectral energy distributions (e.g., \citealt{2001ApJ...556..357A,2008ApJ...674..451B}) and photospheric chemistry (e.g., \citealt{2000ApJ...531..438B}), condensates can coalesce into large-scale cloud and haze structures \citep{1989ApJ...338..314L,2001ApJ...556..872A,2014Natur.505..654C}.
-\textbf{These structures} may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) \textbf{and} long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
+These structures may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
 Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
@@
 
-Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows \textbf{for} the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
-The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} \textbf{and} amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) \textbf{and} surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
+Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows for the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
+The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} and amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
 Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
 Since different wavelengths sample different photospheric depths in the highly structured spectra of L and T dwarfs, these phase variations have been interpreted as arising from the relative motion of distinct cloud layers or deep thermal pulsations.
-Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact \textbf{with} clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.
+Deep thermal pulsations occur on longer timescales ($\sim$ 100 hr for an example T-dwarf model) but may interact with clouds to produce shorter timescale variability \citep{2014ApJ...785..158R}.
 
 Broad-band variability amplitudes are typically $<$1\% in L and T dwarfs, with some dramatic exceptions \citep{2009ApJ...701.1534A,2012ApJ...750..105R,2013A&A...555L...5G,2016ApJ...829L..32L}. 
-Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient \textbf{numbers of nearby reference stars which can be used to correct time-variable telluric absorption} \citep{2003MNRAS.339..477B}.
-In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision \textbf{and} have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
-However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity \textbf{or} evolution in variability modes.
+Ground-based spectral (e.g., CLOUDS; \citealt{2008A&A...487..277G}) and broad-band photometric monitoring surveys (e.g., \citealt{1999A&A...348..800B,2003MNRAS.346..473K,2014ApJ...793...75R,2014A&A...566A.111W}) are generally limited to $>$1-3\% relative precision due to telluric atmospheric instabilities (i.e., ``red noise'') and insufficient numbers of nearby reference stars which can be used to correct time-variable telluric absorption \citep{2003MNRAS.339..477B}.
+In contrast, the stability of space-based platforms such as $Hubble$ $Space$ $Telescope$ ($HST$), $Spitzer$ and $Kepler$ provide order-of-magnitude improvements in relative photometric and spectro-photometric precision and have been responsible for the discovery of the majority of known L and T dwarf variables \citep{2013ApJ...768..121A,2013ApJ...779..172G,2015ApJ...799..154M}.
+However, these facilities are poorly suited for building up robust statistical samples to assess the physical origins of surface heterogeneity or evolution in variability modes.
 
-Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which \textbf{reference stars} are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
-\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby \textbf{reference star} in a wide \textbf{and long (3$\arcsec \times 60 \arcsec$) slit.}
-This was sufficient to infer the presence of a cloud/haze layer \textbf{or disfavor TiO/VO absorption} in CoRoT-1b via transmission spectroscopy.
+Ground-based Multi-Object Spectroscopy (MOS) with a multi-object or long slit spectrograph, in which reference stars are simultaneously observed to correct for telluric effects can significantly improve the precision of ground-based spectro-photometry (e.g., \citealt{bean10,bean2013,gibson13clouds,stevenson2016hatp26}).
+\citet{2014ApJ...783....5S} achieved $<$0.1\% per band variability precision for the planet-host star CoRoT-1 using the NASA Infrared Telescope Facility (IRTF) SpeX spectrograph \citep{2003PASP..115..362R}, by simultaneously monitoring the star and a nearby reference star in a wide and long (3$\arcsec \times 60 \arcsec$) slit.
+This was sufficient to infer the presence of a cloud/haze layer or disfavor TiO/VO absorption in CoRoT-1b via transmission spectroscopy.
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
@@
 	from the IRSA Finderchart service (\url{http://irsa.ipac.caltech.edu/applications/finderchart/}).
-Each image is centered on the target \textbf{and spans} a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
-	The \textbf{reference stars labeled in each image are observed simultaneously in the 3$\arcsec \times 60 \arcsec$ SpeX slit to remove telluric variability.}}
+Each image is centered on the target and spans a 1$\arcmin\times$1$\arcmin$ field of view oriented with North up and East the left.
+	The reference stars labeled in each image are observed simultaneously in the 3$\arcsec \times 60 \arcsec$ SpeX slit to remove telluric variability.}
 	\label{fig:images}
@@
 The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree}.
-\textbf{We downselected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) \textbf{reference stars} at apparent separations of 5$\arcsec$--30$\arcsec$.
-We identified 30 potential targets \textbf{and} prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
+We \textbf{down-selected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) reference stars at apparent separations of 5$\arcsec$--30$\arcsec$.
+We identified 30 potential targets and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
 Two sources were identified as ideal initial targets (Table~\ref{tab:bdProp}).
 
-2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of \textbf{low surface gravity \citep[][however, see \citet{2015ApJS..219...33G}]{2016ApJ...833...96L}.
-There is no Li I absorption reported for this source \citep{2003AJ....126.2421C,2015ApJS..220...18B}; however its low temperature \citep[T$_{eff}$=1800~K][]{2015ApJS..219...33G} and likely youth ($<$1 Gyr) is consistent with a mass below the hydrogen-burning mass limit \citep{2003A&A...402..701B,2000ApJ...531..438B}.}
+2MASS~J08354256$-$0819237 (hereafter {\sha}; \citealt{2003AJ....126.2421C}) is a bright, nearby ($d$ = 7.27$\pm$0.02~pc; \citealt{2016AJ....152...24W}) L5 dwarf that shows signatures of low surface gravity \citep[][however, see \citet{2015ApJS..219...33G}]{2016ApJ...833...96L}.
+There is no Li I absorption reported for this source \citep{2003AJ....126.2421C,2015ApJS..220...18B}; however its low temperature \citep[T$_{eff}$=1800~K][]{2015ApJS..219...33G} and likely youth ($<$1 Gyr) is consistent with a mass below the hydrogen-burning mass limit \citep{2003A&A...402..701B,2000ApJ...531..438B}.
 This source has been reported to vary in both optical and near-infrared bands with a period of 3.1~hr and an amplitude of $\sim$1\%  \citep{2004MNRAS.354..378K,2014A&A...566A.111W}.
 Its $v\sin{i}$ = 14.2$\pm$0.4~{\kms} \citep{2010ApJ...723..684B} suggests a near pole-on viewing angle assuming a radius\footnote{We adopt the equatorial radius of Jupiter, {\rjup} = 7.15$\times$10$^9$~cm.} R = 1~{\rjup}.
-There is an $H$ = 12.3 \textbf{reference star} (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
+There is an $H$ = 12.3 reference star (2MASS~J08354383$-$0819212) at a separation of 28$\arcsec$ suitable for relative flux calibration (Figure~\ref{fig:images}).
 
-2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} \textbf{and Li absorption \citep{2008ApJ...686..528L}.}
+2MASS J18212815+1414010 (hereafter {\shb}; \citealt{2008ApJ...686..528L}) is a similarly bright and nearby ($d$ = 9.38$\pm$0.03; \citealt{2016MNRAS.455..357S}) L4.5 dwarf, which exhibits a peculiar near-infrared spectrum attributed to youth and/or thick clouds \citep{2008ApJ...686..528L,2015ApJS..219...33G,2016ApJ...833...96L} and Li absorption \citep{2008ApJ...686..528L}.
 This source is a photometric variable with a period of 4.2$\pm$0.1~hr \citep{2015ApJ...799..154M} and $v\sin{i}$ = 28.85$\pm$0.16~{\kms}  \citep{2010ApJ...723..684B}, suggesting a near equator-on orientation.
 \citet{2015ApJ...798L..13Y} measured 1--3\% spectral variability with $HST$/WFC3 over 1.1--1.6~$\micron$, with greater variabilty at shorter wavelengths.
-There are three suitably bright \textbf{reference} stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
-We chose 2MASS~J18212622+1414064 \textbf{(visible in Figure~\ref{fig:images})} with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
+There are three suitably bright reference stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
+We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
 
@@
 obtained IRTF/SpeX data for these sources \citep{2008ApJ...686..528L,2010ApJ...710.1142B}.
-Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} \textbf{indicates} near-infrared
+Direct comparison to spectral standards following the convention of \citet{2010ApJS..190..100K} indicates near-infrared
 classifications of L7 for {\sha} and L5 for {\shb} (Figure~\ref{fig:tbright}).
@@
 \end{equation}
-$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ \textbf{is} the source distance and $R$ \textbf{is} the source radius.
-\textbf{We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
-Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.}
+$F_{\lambda,obs}$ and $F_{\lambda,abs}$ are the observed and absolute flux densities, $B_\lambda$ is the Planck function, $d$ is the source distance and $R$ is the source radius.
+We have ignored limb darkening in our calculations, which affects the surface intensity of brown dwarf surfaces \citep[e.g.][]{2011A&A...529A..75C}.
+Since there are few empirical constraints on limb darkening for L-dwarfs, we assume a uniform brightness temperature surface, which gives an average brightness temperature of a non-homogeneous surface.
 
@@
 For {\sha} we considered two cases: radii of 0.114--0.137~R$_{\odot}$ for ages of 50--200~Myr, the age range estimated for INT-G sources by \citet{2013ApJ...772...79A}; and radii of 0.088--0.101~R$_{\odot}$ for ages of 0.5--3~Gyr; i.e., a field dwarf age.
-For {\shb}, we assumed \textbf{a} lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}.
-The \textbf{\citet{2003A&A...402..701B}} evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.
+For {\shb}, we assumed a lower age limit of 200~Myr based on its field gravity classification, and an upper limit of 700~Myr based on the analysis of \citet{2016MNRAS.455..357S}.
+The \citet{2003A&A...402..701B} evolutionary models predict radii of 0.097--0.114~R$_{\odot}$ for these ages and the luminosity of {\shb}.
 
@@
 We compared these two cases to solar-metallicity BT-Settl spectral models from \citet{2012RSPTA.370.2765A}, with {\teff} and {\logg} parameters consistent with the bolometric luminosity of {\sha} and the adopted ages (again based on the \citealt{2003A&A...402..701B} evolutionary models).
-\textbf{To achieve temperatures and gravities between the pre-computed spectra in the BT-Settl atmospheric grid, we interpolated the spectra.}
+To achieve temperatures and gravities between the pre-computed spectra in the BT-Settl atmospheric grid, we interpolated the spectra.
 Both models overlap the data to some degree, although the young model shows an increasing brightness temperature with wavelength rather than a decreasing temperature.
@@
 The duration is the total time from start to end of the observations including array sampling and overheads.
-The FWHM is the measured full width \textbf{at} half maximum of the spatial point spread function around \textbf{H band (1.7$\mu$m)}, taken as the median value over the entire time series.}
+The FWHM is the measured full width at half maximum of the spatial point spread function around H band (1.7$\mu$m), taken as the median value over the entire time series.}
 \end{deluxetable*}
@@
 Both target and reference star were observed simultaneously by orienting the 3$\arcsec$$\times$60$\arcsec$ slit to align with the visual binary axis.
-This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes \textbf{differential} color refraction.
-The effective resolution of the spectral data, set by seeing and pointing errors, \textbf{was} $\lambda$/$\Delta\lambda$ $\approx$ 50.
+This orientation is generally misaligned with the parallactic angle, but the good seeing (0$\farcs$5 at $H$-band) and wide slit minimizes differential color refraction.
+The effective resolution of the spectral data, set by seeing and pointing errors, was $\lambda$/$\Delta\lambda$ $\approx$ 50.
 Integration times were 45~s and 60~s for {\sha} and {\shb}, respectively.
@@
 
-\textbf{The 2D images were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
+The 2D images were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
 This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
@@
 Once the 2D spectral images were rectified, the background is subtracted along the Y (spatial) direction with a 4th order polynomial.
-The reduction software is available online\footnote{https://github.com/eas342/spectral\_pipeline\_and\_scripts}.}
+The reduction software is available online\footnote{https://github.com/eas342/spectral\_pipeline\_and\_scripts}.
 
-\textbf{We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
+We obtained ThAr arc lamp spectra, dark frames and flat field data for calibration.
 The ThAr data is taken for wavelength calibration with the 0.3$\arcsec\times60\arcsec$ slit since it has a resolving power high enough to separate the ThAr lines and identify them.
@@
 For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum.
-To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.}
+To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
 These shifts were used to apply a custom flat field for every image.
@@
 Typical signal-to-noise of the extracted spectra were 40 - 100 per spectral pixel (unbinned).
-Relative spectra (source \textbf{divided by} reference) were then computed for each exposure.
+Relative spectra (source divided by reference) were then computed for each exposure.
 Our image rectification process described above ensures that the wavelength solution is the same for each row of the image.
-However, there are small additional shifts of the sources within the \textbf{slit, so} another shift was performed between the sources to ensure that telluric features were removed when dividing the two spectra.
+However, there are small additional shifts of the sources within the slit, so another shift was performed between the sources to ensure that telluric features were removed when dividing the two spectra.
 
@@
 \shb\ has significant variability over wavelengths $<$1.7$\micron$ with a strong spectral slope.
-	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained \textbf{at} a different epoch, but show a similar slope.
-	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle \textbf{radius} of 0.28 $\mu$m.
+	 Also shown is the WFC3 amplitude spectrum of \shb\ from \citet{2015ApJ...798L..13Y}. The WFC3 observations were obtained at a different epoch, but show a similar slope.
+	 The amplitude spectrum for \shb\ is fit to a simple Mie scattering model with a log-normal particle size distribution of spherical forsterite grains; the best fit has a median particle radius of 0.28 $\mu$m.
 	 In all plots the regions potentially contaminated by telluric absorption are shaded in light green.
@@
 Figure \ref{fig:specphot} shows the raw spectra of the two brown dwarfs, their reference spectra and the background spectra.
-Neither the reference spectra nor the brown dwarf spectra have \textbf{had} any corrections applied for telluric absorption or instrumental spectral response.
+Neither the reference spectra nor the brown dwarf spectra have had any corrections applied for telluric absorption or instrumental spectral response.
 The reference stars have significantly bluer spectra than the brown dwarfs, but nonetheless contain the same telluric water absorption signatures
@@
 The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
-We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period \textbf{for each brown dwarf} and compare it to the expected photon and read noise.
+We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period for each brown dwarf and compare it to the expected photon and read noise.
 In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
@@
 
-We find minimal variation in the lightcurves of {\sha} \textbf{but} pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
+We find minimal variation in the lightcurves of {\sha} but pronounced variation in {\shb}, particularly in bands $<$1.8~$\mu$m. 
 These variations are periodic with ``double-hump'' structures at peak amplitudes around -2.7~hr and +1.3~hr relative to JD 2457565.00.
@@
 \end{equation}
-where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is \textbf{the} period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
+where $F(t)$ is the relative flux as a function of time $t$, $A_1$ and $A_2$ are the amplitudes of the two sinusoid terms, $t_1$ and $t_2$ are the time of maximum periodic flux for each sinusoid term, $\tau$ is the period of the variations, $a(t)$ is the airmass as a function of time and $B$, $C$ and $D$ are constants quantifying baseline (i.e., non-astrophysical) trends.
 Since some wavelengths are affected by telluric contamination and we wish to avoid fitting harmonics, we impose a prior on the rotational period $\tau$.
-\textbf{We impose} 2.6 $< \tau <$ 3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
+We impose 2.6 $< \tau <$ 3.6 hr for \sha\ and 3.7 $< \tau <$ 4.7 hr for {\shb}, $\pm$0.5 hr around the literature values.
 These priors are wide enough they don't drive the constraints on $\tau$ at short wavelengths for {\shb}, but narrow enough to ensure that the sinusoidal fits do not just fit the airmass trends with time.
@@
 We do not put any constraints on A$_1$ relative to A$_2$.
-\textbf{The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.}
+The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.
 
@@
 For {\sha} (Figure \ref{fig:ampspec0835}) we find at most small amplitude variability ($\lesssim 0.5\%$), marginally significant at 1.7~$\mu$m and 2.1--2.35~$\mu$m, with a flat trend as a function of wavelength.
-\textbf{If one were to average all of the K-band points together, they are consistent with a 3.4 $\pm$ 0.1 hr rotation period, though this is somewhat driven by the prior 2.6 $< \tau < $3.6 hr.}
+If one were to average all of the K-band points together, they are consistent with a 3.4 $\pm$ 0.1 hr rotation period, though this is somewhat driven by the prior 2.6 $< \tau < $3.6 hr.
 
@@
 In both cases, we find no statistically significant wavelength dependence on the time of maximum variation $t_1$, and hence no phase variation.
-The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}, \textbf{4.2$\pm$0.1 hr}.
+The period of \shb\ is found to be consistent with that of \citet{2015ApJ...799..154M}, 4.2$\pm$0.1 hr.
 If we optimistically assume all wavelengths are statistically independent, the weighted average rotation period is 4.10 $\pm$ 0.03 hours.
@@
 \end{equation}
-There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum that may be due to different spatial cloud and temperature distributions \textbf{at} different epochs.
-\citet{2015ApJ...798L..13Y} \textbf{found} that the WFC3 amplitude spectrum has no significant water vapor \textbf{absorption, which} indicates a high haze layer in {\shb}.
+There is a multiplicative offset of 25\% between the IRTF and WFC3 spectrum that may be due to different spatial cloud and temperature distributions at different epochs.
+\citet{2015ApJ...798L..13Y} found that the WFC3 amplitude spectrum has no significant water vapor absorption, which indicates a high haze layer in {\shb}.
 This is consistent with our gradually decreasing slope from 1.1 to 1.7~$\mu$m.
@@
 
-We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an \textbf{optically thin grouping of clouds} consisting of a log-normal distribution of particle sizes.
-\textbf{
+We model the wavelength dependence of variability amplitudes for \shb\ with a simple cloud model: an optically thin grouping of clouds consisting of a log-normal distribution of particle sizes.
 Let $\alpha_{min}$ and $\alpha_{max}$ be the minimum and maximum cloud coverages corresponding to the maximum and minimum flux levels, respectively.
@@
 \end{equation}
-where $A_{Clouds}$ is the variability amplitude, $K$ is a constant encapsulating the area and column density and $Q_{avg}(r,\sigma_s)$ is the extinction coefficient averaged over all particles.}
+where $A_{Clouds}$ is the variability amplitude, $K$ is a constant encapsulating the area and column density and $Q_{avg}(r,\sigma_s)$ is the extinction coefficient averaged over all particles.
 
-We model the single particle extinction coefficient, $Q_{ext}$ \textbf{with} the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
+We model the single particle extinction coefficient, $Q_{ext}$ with the \texttt{Python} Mie theory code \texttt{miescatter} \citep{bohren1983mie} to calculate the opacity as a function of wavelength.
 We assume that the particles are spherical forsterite grains (Mg$_2$SiO$_4$).
-We use a constant n=1.67 \textbf{and k=0.006 complex} index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.
+We use a constant n=1.67 and k=0.006 complex index of refraction because the real and imaginary parts of the index of refraction are relatively constant across the optical and near infrared \citep{scott1996forsterite}.
 When fitting the amplitude spectra to our Mie model, we imposed a prior of $r < 5 \mu m$; beyond this scale, the models are essentially unchanged with median particle radius.
@@
 We show the maximum likelihood model which has a near-zero amplitude.
-For \shb, we find that the amplitude spectrum is well-fit by a Mie scattering model and \textbf{that} the median particle radius is reasonably constrained.
-Figure \ref{fig:ampspec1821} shows the best-fit model\textbf{, which} has a median particle radius of 0.28~$\mu$m and $\sigma_s$ = 0.3.
+For \shb, we find that the amplitude spectrum is well-fit by a Mie scattering model and that the median particle radius is reasonably constrained.
+Figure \ref{fig:ampspec1821} shows the best-fit model, which has a median particle radius of 0.28~$\mu$m and $\sigma_s$ = 0.3.
 This model has a reduced $\chi^2$ of 1.08 and is thus consistent with the measured amplitude spectrum.
@@
 
-A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has \textbf{a redder than average} ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
+A similar amplitude versus wavelength trend was recently observed for WISEP J004701.06+680352.1 \citep{2016ApJ...829L..32L}, which has a redder than average ($J-K$ = 2.55) spectral energy distribution thought to be caused by a high altitude haze layer.
 In WISEP J0047+6803, the wavelength trend could be fit by $\sim0.4~\mu$m forsterite grains, which is close to our characteristic particle size.
@@
 
-We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral \textbf{types} L4-L5: {\sha} and {\shb}.
+We obtained high precision ground-based spectrophotometry of two brown dwarfs of spectral types L4-L5: {\sha} and {\shb}.
 These brown dwarfs have temperatures near the condensation temperature of forsterite (Mg$_2$SiO$_4$).
 We find that {\sha} has marginal variability and no significant wavelength dependence; while
-{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m), which declines \textbf{toward} the near infrared (2.4$~\mu$m).
+{\shb} shows significant variability up to the 1.5\% amplitude (3.0\% peak-to-valley) at short wavelengths (0.9~$\mu$m), which declines toward the near infrared (2.4$~\mu$m).
 A possible difference between the two brown dwarfs is the viewing geometry with \sha\ closer to pole-on and \shb\ closer to equator-on as shown in Table \ref{tab:bdProp}.
 Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
-\textbf{\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.}
+\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.
 
@@
 Using ground-based facilities such as SpeX on IRTF allows us to expand our monitoring of cloud-bearing ultracool dwarfs, both in sample size and long-term tracking.
-The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations \textbf{while} the latter allows us to study weather-related changes to cloud structures over multiple rotation periods.
+The former can provide powerful constraints on how dust particle sizes may depend on differing pressure-temperature profiles, rotation rates, composition and viewing orientations while the latter allows us to study weather-related changes to cloud structures over multiple rotation periods.
 We are currently pursuing a larger monitoring sample that will be reported in future publications.
@@
 \section{Acknowledgements}
-\textbf{Thanks to the anonymous referee for useful improvements and corrections to this work.}
+Thanks to the anonymous referee for useful improvements and corrections to this work.
 Thanks to Vivien Parmentier for useful discussions on cloud versus a spotted temperature models.
@@
 
-\textbf{\software{
+\software{
 \texttt{emcee} \citep{foreman-mackey2013emcee},
@@
 \texttt{IRAF} \citep{tody86} and
-\texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}}
+\texttt{IDL} version 8.5 (Exelis Visual Information Solutions, Boulder, Colorado)}
 

### 2017-09-08 ms.tex
made edits requested by referee through section 4.

@@
 These structures may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
-Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}), virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
+Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M})\textbf{; virtually} all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
 Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
@@
 Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows for the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
-The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A} and amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
+The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}\textbf{, and} amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
 Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
@@
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
-In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing it and its L dwarf companion.
+In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing \textbf{Luhman 16A, a physically associated L dwarf companion nearby on the sky}.
 These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
@@
 There are three suitably bright reference stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
-We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations.
+We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations \textbf{because this configuration minimized the amount of light entering the slit from the nearby visual companion to the north of our target.
+However, we expect that another configuration with the reference star to the southwest could achieve similar spectro-photometric precision.}
 
@@
 
-The 2D images were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
+The 2D \textbf{prism} images\textbf{, which have a dispersion direction approximately along the X direction and spatial direction approximately along the Y direction,} were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
 This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
@@
 Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
-We take flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
+We \textbf{took} flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
 For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum.
 To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
-These shifts were used to apply a custom flat field for every image.
+These shifts were used to apply a custom flat field for every image\textbf{, while shifting the sky flat (with pixel-to-pixel response removed) and maintaining the position of the pixel-to-pixel flat}.
 For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.

### 2017-09-09 ms.tex
nearly finished all changes from referee.

@@
 To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
-These shifts were used to apply a custom flat field for every image\textbf{, while shifting the sky flat (with pixel-to-pixel response removed) and maintaining the position of the pixel-to-pixel flat}.
+These shifts were used to apply a custom flat field for every image\textbf{: the illumination flat (with pixel-to-pixel flat removed) is shifted to the cross correlation peaks and multiplied by the pixel-to-pixel flat structure, which is maintained at the same position}.
 For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.
@@
 The uncertainties in these curves due to photon and read noise range from 0.2\% to 0.6\% per exposure.
-We measure the standard deviations of the time series for wavelength regions that have no significant variations near the rotation period for each brown dwarf and compare it to the expected photon and read noise.
+We measure the standard deviation of the time series for wavelength regions that have no significant variations near the rotation period for each brown dwarf and compare it to the expected photon and read noise.
 In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
@@
 
-Each of the raw light curves were fit to a double sinusoidal model:
+Each of the raw light curves \textbf{was} fit to a double sinusoidal model:
 \begin{equation}\label{eq:cosfit}
@@
 Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
-\sha\ shows less variability than reported in the literature which shows at a tentative period of 3.1 hours \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.
+\sha\ shows less variability \textbf{than reported in the literature} \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.
 

### 2017-09-12 ms.tex
finally calculated the co-variance to address the referee's question to quantify it.

@@
 We do not put any constraints on A$_1$ relative to A$_2$.
-The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.
+The co-variance between A$_1$ and A$_2$ \textbf{is small ($\lesssim 10^{-2}$ of variance of A$_2$ in absolute magnitude)} resulting in ``round'' MCMC 2D posterior distributions between the two parameters since they are essentially different Fourier parameters for the time series.
 

### 2017-09-15 ms.tex
fixed subject verb agreement on standard deviations.
removed the \textbf commands that highlighted the changes.

--- 2017-09-09 ms.tex
@@
 These structures may produce rotationally-modulated brightness variations (e.g., \citealt{2012ApJ...750..105R}) and long-term variations from differential rotation and/or cloud structure evolution (e.g., \citealt{2009ApJ...701.1534A,2013A&A...555L...5G,2016ApJ...826....8Y}).
-Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M})\textbf{; virtually} all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
+Evidence of cloud-driven variability extends to the cooler T dwarfs (e.g., \citealt{2009ApJ...701.1534A,2012ApJ...760L..31B,2015ApJ...799..154M}); virtually all L dwarfs and most T dwarfs likely have cloud deck heterogeneities leading to infrared flux variations $\gtrsim$0.2\% in amplitude \citep{2015ApJ...799..154M}.
 Clouds and hazes are important constituents of exoplanetary atmospheres as well (e.g., \citealt{2011ApJ...733...65B,2014Natur.505...69K,2016Natur.529...59S}).
@@
 Multi-wavelength monitoring of low-temperature stars and brown dwarfs allows for the measurement of cloud vertical structure and composition, as gray grain scattering opacity competes with strongly wavelength-dependent molecular gas opacity.
-The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}\textbf{, and} amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
+The amplitude of variability as a function of wavelength samples the vertical depths of cloud layers \citep{2013ApJ...768..121A}, and amplitude spectra have been shown to vary with effective temperature ({\teff}; e.g., \citealt{2015ApJ...798L..13Y}) and surface gravity (e.g., \citealt{2016ApJ...829L..32L}).
 Wavelength-dependent phase variations in lightcurves have also been observed \citep{2012ApJ...760L..31B,2013ApJ...778L..10B,2016ApJ...826....8Y}.
@@
 A similar investigation of the disintegrating rocky exoplanet KIC 12557548b  enabled the characterization of the grain properties of its tidal debris tail \citep{2016ApJ...826..156S}.
-In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing \textbf{Luhman 16A, a physically associated L dwarf companion nearby on the sky}.
+In a parallel effort, \citet{2014ApJ...785...48B} obtained $<$0.5\% per-band relative precision across the 1--2.5~$\mu$m band with IRTF/SpeX for the variable T dwarf Luhman 16B, by simultaneously observing Luhman 16A, a physically associated L dwarf companion nearby on the sky.
 These studies demonstrate that high-precision, near-infrared spectral monitoring observations can be achieved from the ground.
@@
 The declination range corresponds to the visibility region of IRTF.} with $H$ $<$ 14 and $-$30{\degree}  $<$ $\delta$ $<$ +67{\degree}.
-We \textbf{down-selected} those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) reference stars at apparent separations of 5$\arcsec$--30$\arcsec$.
+We down-selected those sources that have comparable-brightness ($\Delta{H}$ $<$ 1) reference stars at apparent separations of 5$\arcsec$--30$\arcsec$.
 We identified 30 potential targets and prioritized those with previously detected photometric variability or rotational $v\sin{i}$ measurements indicating periods $\leq$10~hr.
@@
 There are three suitably bright reference stars within 40$\arcsec$ for relative calibration visible in Figure \ref{fig:images}.
-We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations \textbf{because this configuration minimized the amount of light entering the slit from the nearby visual companion to the north of our target.
-However, we expect that another configuration with the reference star to the southwest could achieve similar spectro-photometric precision.}
+We chose 2MASS~J18212622+1414064 (visible in Figure~\ref{fig:images}) with $H$=12.0 at 32$\arcsec$ separation for our monitoring observations because this configuration minimized the amount of light entering the slit from the nearby visual companion to the north of our target.
+However, we expect that another configuration with the reference star to the southwest could achieve similar spectro-photometric precision.
 
@@
 
-The 2D \textbf{prism} images\textbf{, which have a dispersion direction approximately along the X direction and spatial direction approximately along the Y direction,} were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
+The 2D prism images, which have a dispersion direction approximately along the X direction and spatial direction approximately along the Y direction, were rectified so that the X coordinates of all background spectra corresponded to the same wavelength.
 This was achieved by selecting a reference row between the sources and then cross-correlating this reference spectrum with all other illuminated detector rows.
@@
 Dark frames are taken with the same exposure time as the science images and with the order sorting filter set to the closed position.
-We \textbf{took} flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
+We took flat field field data with an incandescent lamp to correct for high frequency, pixel-to-pixel variations.
 For {\sha}, we used a combination of the flat-field lamp and a sky frame to construct a pixel response map, removing large-scale ($\gtrsim$ 30 pixels) structure with low order polynomial fits along spatial and spectral axes, and normalizing to the median response spectrum.
 To correct for instrument flexure, we cross-correlated the sky frame with each science image to measure linear spatial shifts, which were $\pm$5~pixels or 0.5\arcsec\ for \sha\ and $\pm$1.5~pixels or 0.15\arcsec\ for \shb.
-These shifts were used to apply a custom flat field for every image\textbf{: the illumination flat (with pixel-to-pixel flat removed) is shifted to the cross correlation peaks and multiplied by the pixel-to-pixel flat structure, which is maintained at the same position}.
+These shifts were used to apply a custom flat field for every image: the illumination flat (with pixel-to-pixel flat removed) is shifted to the cross correlation peaks and multiplied by the pixel-to-pixel flat structure, which is maintained at the same position.
 For {\shb}, we did not have sufficient sky frames so we used our incandescent lamp image for both flat fielding and flexure analysis.
@@
 We measure the standard deviation of the time series for wavelength regions that have no significant variations near the rotation period for each brown dwarf and compare it to the expected photon and read noise.
-In these wavelength bins, the standard deviations of the points is about 4$\times$ the expected read noise and photon noise.
+In these wavelength bins, the standard deviations of the points are about 4$\times$ the expected read noise and photon noise.
 We attribute this to correlated errors between wavelengths and as a simple approximation multiply all error bars by a factor of 4 to account for these systematics.
@@
 
-Each of the raw light curves \textbf{was} fit to a double sinusoidal model:
+Each of the raw light curves was fit to a double sinusoidal model:
 \begin{equation}\label{eq:cosfit}
@@
 We do not put any constraints on A$_1$ relative to A$_2$.
-The co-variance between A$_1$ and A$_2$ is very small (resulting in ``round'' MCMC 2D posterior distributions between the two parameters) since they are essentially different Fourier parameters for the time series.
+The co-variance between A$_1$ and A$_2$ is small ($\lesssim 10^{-2}$ of variance of A$_2$ in absolute magnitude) resulting in ``round'' MCMC 2D posterior distributions between the two parameters since they are essentially different Fourier parameters for the time series.
 
@@
 Recently, \citet{vos2017viewingGeom} find that there are correlations between variability and color properties as a function of viewing geometry and that equator-on dwarfs show, on average, larger variability amplitudes.
-\sha\ shows less variability \textbf{than reported in the literature} \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.
+\sha\ shows less variability than reported in the literature \citep{2004MNRAS.354..378K,2014A&A...566A.111W}, so it likely exhibited a more homogeneous cloud distribution at our observed epoch.
 
